---
title: "EDA Report"
author: "Provided by AutoQuant"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  prettydoc::html_pretty:
    theme: cayman
    toc: yes
    toc_depth: 2
    fig_caption: yes
    number_sections: no
classoption: landscape
params:
  artifacts: NULL
  DataName: "EDA Data"
  Theme: "dark"
---

```{css, echo=FALSE}
@import url('https://fonts.googleapis.com/css2?family=Yusei+Magic&display=swap');

:root{
  /* Core dark palette */
  --bg0: #070A14;
  --bg1: #0B1030;
  --bg2: #10183D;

  --panel: rgba(16, 24, 61, 0.72);
  --panel2: rgba(10, 14, 32, 0.72);

  --text: #E7ECFF;
  --muted: rgba(231, 236, 255, 0.72);

  --link: #9EC5FF;
  --linkHover: #CFE3FF;

  /* Neon glow */
  --glow: rgba(72, 145, 255, 0.40);
  --glowStrong: rgba(72, 145, 255, 0.70);
  --border: rgba(140, 170, 255, 0.30);

  --codeBg: rgba(255,255,255,0.06);
  --codeBorder: rgba(140, 170, 255, 0.22);

  --preBg: rgba(0,0,0,0.25);
  --preBorder: rgba(140, 170, 255, 0.28);

  --tableHeadBg: rgba(72, 145, 255, 0.22);
  --tableOdd: rgba(255,255,255,0.04);
  --tableEven: rgba(255,255,255,0.02);
  --tableGrid: rgba(231, 236, 255, 0.12);
}

* { box-sizing: border-box; }

html, body { height: 100%; }

body {
  padding: 0;
  margin: 0;
  font-family: "Open Sans", "Helvetica Neue", Helvetica, Arial, sans-serif;
  font-size: 16px;
  line-height: 1.55;
  color: #E7ECFF;

  background:
    radial-gradient(1200px 600px at 20% -10%, rgba(72,145,255,0.20), transparent 60%),
    radial-gradient(900px 500px at 90% 10%, rgba(168,80,255,0.14), transparent 55%),
    linear-gradient(180deg, #0B1030, #070A14);

  background-repeat: no-repeat;
  background-attachment: fixed;
  background-size: cover;
}

a {
  color: var(--link);
  text-decoration: none;
}
a:hover {
  color: var(--linkHover);
  text-decoration: underline;
}

/* Header */
.page-header {
  color: var(--text);
  text-align: center;
  background-color: #05071A;
  background-image: radial-gradient(900px 400px at 50% 0%, rgba(72,145,255,0.18), transparent 70%),
                    linear-gradient(120deg, #05071A, #0E1B4E);
  padding: 1.5rem 2rem;
  border-bottom: 1px solid rgba(140,170,255,0.15);
}
.page-header :last-child { margin-bottom: 0.5rem; }
@media screen and (max-width: 42em) {
  .page-header { padding: 1rem 1rem; }
}

.project-name {
  margin-top: 0;
  margin-bottom: 0.1rem;
  font-size: 2rem;
}
@media screen and (max-width: 42em) {
  .project-name { font-size: 1.75rem; }
}

.project-tagline {
  margin-bottom: 2rem;
  font-weight: normal;
  opacity: 0.8;
  font-size: 1.5rem;
  color: var(--muted);
}
@media screen and (max-width: 42em) {
  .project-tagline { font-size: 1.2rem; }
}

.project-author, .project-date {
  font-weight: normal;
  opacity: 0.85;
  font-size: 1.2rem;
  color: var(--muted);
}
@media screen and (max-width: 42em) {
  .project-author, .project-date { font-size: 1rem; }
}

/* Main layout */
.main-content, .toc {
  max-width: 95%;
  padding: 2rem 4rem;
  margin: 0 auto;
  font-size: 1.06rem;
}

@media screen and (min-width: 42em) and (max-width: 64em) {
  .main-content, .toc { padding: 2rem; }
}
@media screen and (max-width: 42em) {
  .main-content, .toc {
    padding: 2rem 1rem;
    font-size: 1rem;
  }
}

.main-content :first-child { margin-top: 0; }
.main-content img { max-width: 100%; }

/* TOC */
.toc { padding-bottom: 0; }

.toc .toc-box {
  padding: 48px;
  background: linear-gradient(90deg, rgba(5,7,26,0.90), rgba(16,24,61,0.70));
  border: 1px solid rgba(140,170,255,0.20);
  border-radius: 44px;
  color: var(--text);
  box-shadow:
    0 10px 30px rgba(0,0,0,0.35),
    0 0 24px var(--glow);
  backdrop-filter: blur(10px);
}
.toc .toc-box .toc-title {
  margin: 0 0 0.5rem;
  text-align: center;
}
.toc .toc-box > ul { margin: 0; padding-left: 1.5rem; }

/* Headings */
.main-content h1,
.main-content h2,
.main-content h3,
.main-content h4,
.main-content h5,
.main-content h6 {
  margin-top: 2rem;
  margin-bottom: 1rem;
  font-weight: 700;
  letter-spacing: 0.2px;
  color: var(--text);
}

.main-content h1 { font-size: 2.0rem; }
.main-content h2 { font-size: 1.6rem; opacity: 0.95; }
.main-content h3 { font-size: 1.35rem; opacity: 0.92; }
.main-content h4 { font-size: 1.15rem; opacity: 0.90; }
.main-content h5 { font-size: 1.05rem; opacity: 0.88; }
.main-content h6 { font-size: 1.0rem; opacity: 0.86; }

/* Paragraphs */
.main-content p { margin-bottom: 1em; color: var(--text); }

/* Inline code */
.main-content code {
  padding: 2px 6px;
  font-family: Consolas, "Liberation Mono", Menlo, Courier, monospace;
  color: var(--text);
  background-color: var(--codeBg);
  border: 1px solid var(--codeBorder);
  border-radius: 0.45rem;
}

/* Code blocks */
.main-content pre {
  padding: 0.9rem 1rem;
  margin-top: 0;
  margin-bottom: 1rem;

  font: 0.98rem Consolas, "Liberation Mono", Menlo, Courier, monospace;
  color: var(--text);

  background-color: var(--preBg);
  border: 1px solid var(--preBorder);
  border-radius: 0.75rem;
  line-height: 1.45;
  overflow: auto;

  box-shadow:
    0 10px 24px rgba(0,0,0,0.35),
    0 0 18px rgba(72,145,255,0.16);
}
@media screen and (max-width: 42em) {
  .main-content pre { font-size: 0.9rem; }
}

.main-content pre > code {
  padding: 0;
  margin: 0;
  color: var(--text);
  word-break: normal;
  white-space: pre;
  background: transparent;
  border: 0;
}

/* Lists */
.main-content ul, .main-content ol { margin-top: 0; }

/* Blockquotes */
.main-content blockquote {
  padding: 0.25rem 1rem;
  margin-left: 0;
  color: var(--muted);
  border-left: 0.3rem solid rgba(72,145,255,0.45);
  background: rgba(255,255,255,0.03);
  border-radius: 0.6rem;
}
@media screen and (max-width: 42em) {
  .main-content blockquote { font-size: 1.05rem; }
}

/* HR */
.main-content hr {
  height: 1px;
  padding: 0;
  margin: 1.25rem 0;
  background-color: rgba(231,236,255,0.12);
  border: 0;
}

/* ============================
   DETAILS: glow box + hover glow
   ============================ */
.main-content details {
  margin: 1rem 0;
  padding: 0.85rem 1rem;
  border-radius: 0.95rem;

  background: linear-gradient(180deg, var(--panel), var(--panel2));
  border: 1px solid var(--border);

  box-shadow:
    0 10px 26px rgba(0,0,0,0.35),
    0 0 18px var(--glow);

  transition: transform 140ms ease, box-shadow 140ms ease, border-color 140ms ease;
  backdrop-filter: blur(10px);
}

.main-content details:hover {
  transform: translateY(-1px);
  border-color: rgba(140,170,255,0.55);
  box-shadow:
    0 14px 34px rgba(0,0,0,0.45),
    0 0 26px var(--glowStrong);
}

.main-content details[open] {
  border-color: rgba(140,170,255,0.60);
  box-shadow:
    0 14px 34px rgba(0,0,0,0.45),
    0 0 28px var(--glowStrong);
}

.main-content details > summary {
  cursor: pointer;
  user-select: none;
  font-weight: 700;
  color: var(--text);
  list-style: none;
  display: flex;
  align-items: center;
  gap: 10px;
}

.main-content details > summary::-webkit-details-marker { display: none; }

.main-content details > summary::before {
  content: "▸";
  display: inline-block;
  transform: translateY(-1px);
  opacity: 0.85;
  transition: transform 140ms ease;
}

.main-content details[open] > summary::before {
  transform: rotate(90deg) translateY(-1px);
}

/* Inner content spacing inside details */
.main-content details > *:not(summary) {
  margin-top: 0.85rem;
}

/* ============================
   TABLES (dark) + wrapper hooks
   ============================ */
.main-content table {
  width: 100%;
  overflow: auto;
  word-break: normal;
  word-break: keep-all;
  -webkit-overflow-scrolling: touch;
  border-collapse: collapse;
  border-spacing: 0;
  margin: 0.75rem 0;
  color: var(--text);
}

.main-content table th {
  font-weight: 800;
  background-color: var(--tableHeadBg);
  color: var(--text);
  border-bottom: 1px solid var(--tableGrid);
}

.main-content table th,
.main-content table td {
  padding: 0.55rem 0.85rem;
  border-bottom: 1px solid var(--tableGrid);
  text-align: left;
}

.main-content table tr:nth-child(odd) { background-color: var(--tableOdd); }
.main-content table tr:nth-child(even) { background-color: var(--tableEven); }

/* Wrapper that JS will create around tables */
.table-wrap {
  margin: 1rem 0 1.25rem;
  padding: 0.75rem 0.9rem;
  border-radius: 0.95rem;
  background: linear-gradient(180deg, var(--panel), var(--panel2));
  border: 1px solid rgba(140,170,255,0.22);
  box-shadow:
    0 10px 26px rgba(0,0,0,0.30),
    0 0 18px rgba(72,145,255,0.18);
}

.table-toolbar {
  display: flex;
  justify-content: flex-end;
  gap: 10px;
  margin-bottom: 0.6rem;
}

.table-btn {
  appearance: none;
  border: 1px solid rgba(140,170,255,0.40);
  background: rgba(72,145,255,0.14);
  color: var(--text);
  padding: 7px 10px;
  border-radius: 0.7rem;
  cursor: pointer;
  font-weight: 700;
  letter-spacing: 0.2px;
  transition: transform 120ms ease, box-shadow 120ms ease, border-color 120ms ease, background 120ms ease;
}

.table-btn:hover {
  transform: translateY(-1px);
  border-color: rgba(140,170,255,0.70);
  background: rgba(72,145,255,0.22);
  box-shadow: 0 0 18px rgba(72,145,255,0.35);
}

.table-btn:active {
  transform: translateY(0px);
}

/* Definition lists */
.main-content dl { padding: 0; }
.main-content dl dt {
  padding: 0;
  margin-top: 1rem;
  font-size: 1rem;
  font-weight: 800;
  color: var(--text);
}
.main-content dl dd {
  padding: 0;
  margin-bottom: 1rem;
  color: var(--muted);
}

/* Reactable: focus glow + small polish */
.reactable .rt-search input:focus,
.reactable .rt-filter input:focus,
.reactable select:focus {
  border-color: rgba(140,170,255,0.70) !important;
  box-shadow: 0 0 0 3px rgba(72,145,255,0.18), 0 0 18px rgba(72,145,255,0.30) !important;
}

/* Reactable: soften grid + round the whole widget */
.reactable {
  border-radius: 14px;
  overflow: hidden; /* keeps rounded corners clean */
}

/* Scrollbar polish (Chrome/Edge) */
.reactable ::-webkit-scrollbar { height: 10px; width: 10px; }
.reactable ::-webkit-scrollbar-track { background: rgba(0,0,0,0.15); border-radius: 999px; }
.reactable ::-webkit-scrollbar-thumb { background: rgba(140,170,255,0.25); border-radius: 999px; }
.reactable ::-webkit-scrollbar-thumb:hover { background: rgba(140,170,255,0.40); }

.reactable {
  position: relative;
  border-radius: 16px;
  overflow: hidden;
}

.reactable::before {
  content: "";
  position: absolute;
  inset: 0;
  border-radius: 16px;
  padding: 1px;
  background: linear-gradient(
    135deg,
    rgba(72,145,255,0.7),
    rgba(168,80,255,0.5),
    rgba(72,145,255,0.7)
  );
  -webkit-mask:
    linear-gradient(#000 0 0) content-box,
    linear-gradient(#000 0 0);
  -webkit-mask-composite: xor;
  mask-composite: exclude;
  pointer-events: none;
}
.reactable .rt-tbody .rt-tr:hover {
  background: rgba(72,145,255,0.12) !important;
  box-shadow: inset 0 0 18px rgba(72,145,255,0.18);
}
.reactable .rt-tr {
  transition: background 120ms ease, box-shadow 120ms ease;
}

.reactable .rt-pagination button {
  transition: all 120ms ease;
}

```


## <font size="5">EDA Report Descriptions</font>

<details><summary>Expand</summary>
<p>

This report is designed to provide a broad, structured, and user-friendly exploratory data analysis workflow for investigating datasets before modeling, reporting, or deeper analysis. The goal is to surface meaningful patterns, data quality issues, distribution characteristics, relationships between variables, temporal movement, target-variable behavior, drift signals, and potential modeling risks in a clear and navigable format.

The outputs are intended to be semi-comprehensive rather than exhaustive. They provide enough evidence to help users form reasonable conclusions about the data, identify variables or relationships worth further investigation, and recognize areas where additional domain review, validation, or modeling decisions may be needed. The report is organized into higher-level sections so users can quickly navigate from broad diagnostics to more detailed artifacts as needed.

While the report provides a wide range of tables, plots, diagnostics, and heuristic flags, it should be treated as an analytical starting point rather than a final judgment. Some findings, especially target leakage, collider risk, post-treatment risk, feature drift, and concept drift indicators, are intended to highlight areas for review rather than prove causality or modeling suitability on their own.


### Data Description

This section provides a column-level audit of the input dataset. The table summarizes each variable’s data type, inferred role, row count, missingness indicators, NULL counts, NA counts, NaN counts, infinite-value counts, empty-value counts, unique-value counts, dominant value statistics, constant-field flags, and a preview of the first five values. This overview is intended to help identify data quality issues, suspicious fields, high-cardinality variables, incorrectly typed columns, and other attributes that may affect downstream analysis.

### Univariate Statistics

This section provides a variable-level statistical audit for the numeric fields selected for univariate analysis. The summary table includes row counts, valid-value counts, missingness indicators, zero-value counts, positive and negative value counts, unique-value counts, central tendency statistics, spread statistics, percentile values, skewness, kurtosis, coefficient of variation, IQR-based outlier counts, and diagnostic flags for constant fields, missing values, and infinite values. This table is intended to help identify distribution shape, scale, sparsity, outliers, skew, abnormal values, and other characteristics that may affect downstream analysis.

### Univariate Plots

This section provides visual summaries of the variables selected for univariate analysis. Numeric variables are displayed with histograms to show distribution shape and box plots to highlight spread, central tendency, and potential outliers. When a valid grouping variable is supplied, grouped box plots are also generated to compare numeric distributions across groups. Low-cardinality numeric variables may be shown as discrete bar plots, while categorical variables are summarized with count-based bar plots using a Top-N view when needed to keep high-cardinality fields readable.

### Correlation Analysis

This section provides a relationship-level audit for the numeric variables selected for correlation analysis. The report validates the selected correlation inputs, identifies missing, non-numeric, and constant variables, and summarizes pairwise relationships using Spearman correlation. Outputs include a correlation matrix plot, pairwise correlation statistics, pairwise sample sizes, missing-pair counts, correlation direction, correlation strength, p-values, high-correlation flags, and ranked summaries of the strongest absolute, positive, and negative relationships. This section is intended to help identify redundant variables, potential multicollinearity, inverse relationships, weak relationships, and numeric fields that may require further investigation before modeling or downstream analysis.

### Trend Analysis

This section provides time-series summaries for the numeric variables selected for trend analysis. Overall trends are aggregated over the supplied date field and displayed as area plots to show broad movement over time. When a valid grouping variable is supplied, grouped line plots are also generated to compare temporal patterns across segments. The section also includes trend input diagnostics to confirm that the date field, grouping field, and selected trend variables are valid and usable. This section is intended to help identify temporal patterns, seasonality, structural changes, group-level differences, and unusual metric behavior over time.



</details>
</p>

# <font size="5">Describe Data</font>

<details><summary>Expand</summary>
<p>

```{r Describe_Data_Table, echo=FALSE}
if (!is.null(artifacts$widgets$describe_data)) {
  artifacts$widgets$describe_data
}
```

</details>
</p>





# <font size="5">Univariate Statistics</font>
<p>

<details><summary>Expand</summary>
<p>

```{r Univariate_Stats, echo=FALSE}
if (!is.null(artifacts$widgets$univariate_stats)) {
  artifacts$widgets$univariate_stats
} else {
  cat("No univariate variables were selected.")
}
```

</details>
</p>

# <font size="5">Univariate Distribution Plots</font>

<details><summary>Expand</summary>
<p>

```{r UnivariateHistogramPlotList, echo=FALSE}
UnivariateHistogramPlotList <- artifacts$plots$univariate$Histograms
HistogramPlotCols <- artifacts$layout$HistogramPlotCols

if (is.null(HistogramPlotCols)) {
  HistogramPlotCols <- 2L
}

if (!is.null(UnivariateHistogramPlotList) && length(UnivariateHistogramPlotList) > 0L) {
  AutoPlots::display_plots_grid(
    UnivariateHistogramPlotList,
    cols = HistogramPlotCols
  )
} else {
  cat("No numeric univariate variables were available for histogram plots.")
}
```

</p>
</details>


# <font size="5">Univariate Box Plots</font>

<details><summary>Expand</summary>
<p>

```{r UnivariateBoxPlotList, echo=FALSE}
UnivariateBoxPlotList <- artifacts$plots$univariate$BoxPlots
BoxPlotCols <- artifacts$layout$BoxPlotCols

if (is.null(BoxPlotCols)) {
  BoxPlotCols <- 2L
}

if (!is.null(UnivariateBoxPlotList) && length(UnivariateBoxPlotList) > 0L) {
  AutoPlots::display_plots_grid(
    UnivariateBoxPlotList,
    cols = BoxPlotCols
  )
} else {
  cat("No numeric univariate variables were available for box plots.")
}
```

</p>
</details>


# <font size="5">Grouped Univariate Box Plots</font>

<details><summary>Expand</summary>
<p>

```{r UnivariateGroupedBoxPlotList, echo=FALSE}
UnivariateGroupedBoxPlotList <- artifacts$plots$univariate$GroupedBoxPlots
GroupedBoxPlotCols <- artifacts$layout$GroupedBoxPlotCols

if (is.null(GroupedBoxPlotCols)) {
  GroupedBoxPlotCols <- 2L
}

if (!is.null(UnivariateGroupedBoxPlotList) && length(UnivariateGroupedBoxPlotList) > 0L) {
  AutoPlots::display_plots_grid(
    UnivariateGroupedBoxPlotList,
    cols = GroupedBoxPlotCols
  )
} else {
  cat("No grouped univariate box plots were generated. Provide a valid TrendGroupVar to enable this section.")
}
```

</p>
</details>


# <font size="5">Discrete Numeric Bar Plots</font>

<details><summary>Expand</summary>
<p>

```{r UnivariateDiscreteNumericPlotList, echo=FALSE}
UnivariateDiscreteNumericPlotList <- artifacts$plots$univariate$DiscreteNumericBarPlots
DiscreteNumericBarPlotCols <- artifacts$layout$DiscreteNumericBarPlotCols

if (is.null(DiscreteNumericBarPlotCols)) {
  DiscreteNumericBarPlotCols <- 2L
}

if (!is.null(UnivariateDiscreteNumericPlotList) && length(UnivariateDiscreteNumericPlotList) > 0L) {
  AutoPlots::display_plots_grid(
    UnivariateDiscreteNumericPlotList,
    cols = DiscreteNumericBarPlotCols
  )
} else {
  cat("No low-cardinality numeric variables were available for discrete numeric bar plots.")
}
```

</p>
</details>


# <font size="5">Categorical Bar Plots</font>

<details><summary>Expand</summary>
<p>

```{r UnivariateCategoricalTopNPlotList, echo=FALSE}
UnivariateCategoricalTopNPlotList <- artifacts$plots$univariate$CategoricalTopNBarPlots
CategoricalBarPlotCols <- artifacts$layout$CategoricalBarPlotCols

if (is.null(CategoricalBarPlotCols)) {
  CategoricalBarPlotCols <- 1L
}

if (!is.null(UnivariateCategoricalTopNPlotList) && length(UnivariateCategoricalTopNPlotList) > 0L) {
  AutoPlots::display_plots_grid(
    UnivariateCategoricalTopNPlotList,
    cols = CategoricalBarPlotCols
  )
} else {
  cat("No categorical univariate variables were available for bar plots.")
}
```

</p>
</details>


# <font size="5">Correlation Variable Diagnostics</font>

<details><summary>Expand</summary>
<p>

```{r Correlation_Variable_Diagnostics, echo=FALSE}
if (!is.null(artifacts$widgets$correlation_variable_diagnostics)) {
  artifacts$widgets$correlation_variable_diagnostics
} else {
  cat("Correlation variable diagnostics were not created.")
}
```

</p>
</details>


# <font size="5">Correlation Matrix</font>

<details><summary>Expand</summary>
<p>

```{r CorrelogramPlot, echo=FALSE}
if (!is.null(artifacts$plots$correlogram)) {
  artifacts$plots$correlogram
} else {
  cat("No correlation matrix was generated. At least two usable numeric correlation variables are required.")
}
```

</p>
</details>


# <font size="5">Pairwise Correlation Statistics</font>

<details><summary>Expand</summary>
<p>

```{r Correlation_Stats, echo=FALSE}
if (!is.null(artifacts$widgets$correlation_stats)) {
  artifacts$widgets$correlation_stats
} else {
  cat("Pairwise correlation statistics were not created.")
}
```

</p>
</details>

# <font size="5">Top Correlation Plots</font>

<details><summary>Expand</summary>
<p>

```{r CorrelationPlotList, echo=FALSE}
CorrelationPlotList <- artifacts$plots$correlation_pairs

if (!is.null(CorrelationPlotList) && length(CorrelationPlotList) > 0L) {
  AutoPlots::display_plots_grid(
    CorrelationPlotList,
    cols = 1L
  )
} else {
  cat("No top correlation plots were generated.")
}
```

</p>
</details>

# <font size="5">Overall Trend Area Plots</font>

<details><summary>Expand</summary>
<p>

```{r TrendAreaPlotList, echo=FALSE}
TrendAreaPlotList <- artifacts$plots$trend_area

if (!is.null(TrendAreaPlotList) && length(TrendAreaPlotList) > 0L) {
  AutoPlots::display_plots_grid(
    TrendAreaPlotList,
    cols = 2L
  )
} else {
  cat("No overall trend area plots were generated. Provide a valid TrendDateVar and at least one numeric TrendVars value.")
}
```

</p>
</details>


# <font size="5">Grouped Trend Line Plots</font>

<details><summary>Expand</summary>
<p>

```{r TrendPlotList, echo=FALSE}
TrendPlotList <- artifacts$plots$trend_grouped_lines

if (!is.null(TrendPlotList) && length(TrendPlotList) > 0L) {
  AutoPlots::display_plots_grid(
    TrendPlotList,
    cols = 2L
  )
} else {
  cat("No grouped trend line plots were generated. Provide a valid TrendGroupVar to enable this section.")
}
```

</p>
</details>



```{js, echo=FALSE}
setTimeout(function() {
  var codes = document.querySelectorAll('.dataTables_wrapper');
  var code, i, d, s, p;
  for (i = 0; i < codes.length; i++) {
    code = codes[i];
    p = code.parentNode;
    d = document.createElement('details');
    s = document.createElement('summary');
    s.innerText = 'Details';
    // <details><summary>Details</summary></details>
    d.appendChild(s);
    // move the code into <details>
    p.replaceChild(d, code);
    d.appendChild(code);
  }
});
```
