---
title: "Regression ML Report"
author: "Provided by AutoQuant"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  prettydoc::html_pretty:
    theme: cayman
    toc: yes
    toc_depth: 2
    fig_caption: yes
    number_sections: no
classoption: landscape
---

```{r Environment, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
temp <- globalenv()
TempNames <- names(temp)
for(nam in TempNames) {
  assign(x = nam, value = eval(temp[[nam]]), envir = .GlobalEnv)
}
```

```{css, echo=FALSE}
@import url('https://fonts.googleapis.com/css2?family=Yusei+Magic&display=swap');

* {
  box-sizing: border-box;
}

body {
  padding: 0;
  margin: 0;
  font-family: "Open Sans", "Helvetica Neue", Helvetica, Arial, sans-serif;
  font-size: 16px;
  line-height: 1.5;
  color: #000000;
  background: linear-gradient(180deg, #787989, #b7b8cf);
}

a {
  color: #b1c5d8;
  text-decoration: none;
}
a:hover {
  text-decoration: underline;
}

.page-header {
  color: #fff;
  text-align: center;
  background-color: #152399;
  background-image: linear-gradient(120deg,#000121,#152399);
  padding: 1.5rem 2rem;
}
.page-header :last-child {
  margin-bottom: 0.5rem;
}
@media screen and (max-width: 42em) {
  .page-header {
    padding: 1rem 1rem;
  }
}

.project-name {
  margin-top: 0;
  margin-bottom: 0.1rem;
  font-size: 2rem;
}
@media screen and (max-width: 42em) {
  .project-name {
    font-size: 1.75rem;
  }
}

.project-tagline {
  margin-bottom: 2rem;
  font-weight: normal;
  opacity: 0.7;
  font-size: 1.5rem;
}
@media screen and (max-width: 42em) {
  .project-tagline {
    font-size: 1.2rem;
  }
}

.project-author, .project-date {
  font-weight: normal;
  opacity: 0.7;
  font-size: 1.2rem;
}
@media screen and (max-width: 42em) {
  .project-author, .project-date {
    font-size: 1rem;
  }
}

.main-content, .toc {
  max-width: 64rem;
  padding: 2rem 4rem;
  margin: 0 auto;
  font-size: 1.1rem;
}

.toc {
  padding-bottom: 0;
}
.toc .toc-box {
  padding: 55px;
  background: linear-gradient(90deg, #00052b, #00198a);
  border: solid 3px #000000;
  border-radius: 70px;
  color: white;
  box-shadow: 8px 5px 10px 0px #000000;
}
.toc .toc-box .toc-title {
  margin: 0 0 0.5rem;
  text-align: center;
}
.toc .toc-box > ul {
  margin: 0;
  padding-left: 1.5rem;
}
@media screen and (min-width: 42em) and (max-width: 64em) {
  .toc {
    padding: 2rem 2rem 0;
  }
}
@media screen and (max-width: 42em) {
  .toc {
    padding: 2rem 1rem 0;
    font-size: 1rem;
  }
}

.main-content :first-child {
  margin-top: 0;
}
@media screen and (min-width: 42em) and (max-width: 64em) {
  .main-content {
    padding: 2rem;
  }
}
@media screen and (max-width: 42em) {
  .main-content {
    padding: 2rem 1rem;
    font-size: 1rem;
  }
}
.main-content img {
  max-width: 100%;
}
.main-content h1,
.main-content h2,
.main-content h3,
.main-content h4,
.main-content h5,
.main-content h6 {
  margin-top: 2rem;
  margin-bottom: 1rem;
  font-weight: normal;
  color: #000000;
}
.main-content p {
  margin-bottom: 1em;
}
.main-content code {
  padding: 2px 4px;
  font-family: Consolas, "Liberation Mono", Menlo, Courier, monospace;
  color: #2c2c2d;
  background-color: #f3f6fa;
  border-radius: 0.3rem;
}
.main-content pre {
  padding: 0.8rem;
  margin-top: 0;
  margin-bottom: 1rem;
  font: 1rem Consolas, "Liberation Mono", Menlo, Courier, monospace;
  color: #2c2c2d;
  word-wrap: normal;
  background-color: #e9edf9c9;
  border: solid 1px #001a35;
  border-radius: 0.3rem;
  line-height: 1.45;
  overflow: auto;
}
@media screen and (max-width: 42em) {
  .main-content pre {
    font-size: 0.9rem;
  }
}
.main-content pre > code {
  padding: 0;
  margin: 0;
  color: #2c2c2d;
  word-break: normal;
  white-space: pre;
  background: transparent;
  border: 0;
}
@media screen and (max-width: 42em) {
  .main-content pre > code {
    font-size: 0.9rem;
  }
}
.main-content pre code,
.main-content pre tt {
  display: inline;
  max-width: initial;
  padding: 0;
  margin: 0;
  overflow: initial;
  line-height: inherit;
  word-wrap: normal;
  background-color: transparent;
  border: 0;
}
.main-content pre code:before, .main-content pre code:after,
.main-content pre tt:before,
.main-content pre tt:after {
  content: normal;
}
.main-content ul,
.main-content ol {
  margin-top: 0;
}
.main-content blockquote {
  padding: 0 1rem;
  margin-left: 0;
  color: #2c2c2d;
  border-left: 0.3rem solid #dce6f0;
  font-size: 1.2rem;
}
.main-content blockquote > :first-child {
  margin-top: 0;
}
.main-content blockquote > :last-child {
  margin-bottom: 0;
}
@media screen and (max-width: 42em) {
  .main-content blockquote {
    font-size: 1.1rem;
  }
}
.main-content table {
  width: 100%;
  overflow: auto;
  word-break: normal;
  word-break: keep-all;
  -webkit-overflow-scrolling: touch;
  border-collapse: collapse;
  border-spacing: 0;
  margin: 1rem 0;
}
.main-content table th {
  font-weight: bold;
  background-color: #159957;
  color: #fff;
}
.main-content table th,
.main-content table td {
  padding: 0.5rem 1rem;
  border-bottom: 1px solid #e9ebec;
  text-align: left;
}
.main-content table tr:nth-child(odd) {
  background-color: #f2f2f2;
}
.main-content dl {
  padding: 0;
}
.main-content dl dt {
  padding: 0;
  margin-top: 1rem;
  font-size: 1rem;
  font-weight: bold;
}
.main-content dl dd {
  padding: 0;
  margin-bottom: 1rem;
}
.main-content hr {
  height: 2px;
  padding: 0;
  margin: 1rem 0;
  background-color: #eff0f1;
  border: 0;
}
```

```{r ModelObject_DataSets_And_MetaData, echo = FALSE}
if(!is.null(ModelObject)) {
  
  # DataSets
  TestData <- ModelObject[['TestData']]
  TrainData <- ModelObject[['TrainData']]
  
  # Meta info
  TargetColumnName <- ModelObject[['ArgsList']][['TargetColumnName']]
  PredictionColumnName <- 'Predict'
  if(is.null(FeatureColumnNames)) {
    FeatureColumnNames <- ModelObject[['ColNames']][[1L]]
  }
  if(is.null(DateColumnName) && !is.null(ModelObject[['ArgsList']][['PrimaryDateColumn']])) {
    DateColumnName <- ModelObject[['ArgsList']][['PrimaryDateColumn']]
  } else {
    DateColumnName <- NULL
  }
}
```

```{r ModelObject_Model_MetaData, echo = FALSE}
if(!is.null(ModelObject)) {
  
  # Model MetaData ----

  ## Model_MetaData_Parameters ----
  ArgsList <- ModelObject[['ArgsList']]
  
  ## Model_MetaData_GridMetrics ----
  GridMetrics <- ModelObject[['GridMetrics']]
  
}
``` 

```{r ModelObject_Evaluation_Metrics, echo = FALSE}
if(!is.null(ModelObject)) {
  
  # Evaluation Metrics ----
  
  ## Model_Evaluation_Metrics (catboost check, h2o check) ----
  Test_EvalMetrics <- ModelObject[['EvaluationMetrics']][['TestData']]
  Train_EvalMetrics <- ModelObject[['EvaluationMetrics']][['TrainData']]
  
  ## Model_VarImportanceTable ----
  if(tolower(Algo) == 'catboost') {
    
    # Store data
    Test_Importance <- ModelObject[['VariableImportance']][['Test_Importance']]
    Validation_Importance <- ModelObject[['VariableImportance']][['Validation_Importance']]
    Train_Importance <- ModelObject[['VariableImportance']][['Train_Importance']]

    # Update Colnames
    if(!is.null(Test_Importance)) data.table::setnames(Test_Importance, old = 'Importance', new = 'Test_Importance', skip_absent = TRUE)
    if(!is.null(Validation_Importance)) data.table::setnames(Validation_Importance, old = 'Importance', new = 'Validation_Importance', skip_absent = TRUE)
    if(!is.null(Train_Importance)) data.table::setnames(Train_Importance, old = 'Importance', new = 'Train_Importance', skip_absent = TRUE)

    # CatBoost only
    if(is.null(Test_Importance) && is.null(Validation_Importance) && is.null(Train_Importance)) {
      All_Importance <- NULL
    } else if(!is.null(Test_Importance) && !is.null(Validation_Importance) && !is.null(Train_Importance)) {
      All_Importance <- merge(Test_Importance, Validation_Importance, by = 'Variable', all = TRUE)
      All_Importance <- merge(All_Importance, Train_Importance, by = 'Variable', all = TRUE)
    } else if(!is.null(Test_Importance) && !is.null(Validation_Importance) && is.null(Train_Importance)) {
      All_Importance <- merge(Test_Importance, Validation_Importance, by = 'Variable', all = TRUE)
    } else if(!is.null(Test_Importance) && is.null(Validation_Importance) && !is.null(Train_Importance)) {
      All_Importance <- merge(Test_Importance, Train_Importance, by = 'Variable', all = TRUE)
    } else if(is.null(Test_Importance) && !is.null(Validation_Importance) && !is.null(Train_Importance)) {
      All_Importance <- merge(Validation_Importance, Train_Importance, by = 'Variable', all = TRUE)
    } else if(is.null(Test_Importance) && is.null(Validation_Importance) && !is.null(Train_Importance)) {
      All_Importance <- Train_Importance
    } else if(is.null(Test_Importance) && !is.null(Validation_Importance) && is.null(Train_Importance)) {
      All_Importance <- Validation_Importance
    } else if(!is.null(Test_Importance) && is.null(Validation_Importance) && is.null(Train_Importance)) {
      All_Importance <- Test_Importance
    } else {
      All_Importance <- NULL
    }

  } else {

    # Store data (xgb check, )
    Test_Importance <- ModelObject[['VariableImportance']]
    Validation_Importance <- NULL
    Train_Importance <- NULL
    
    # Update Colnames
    if(Algo %in% c("xgboost","lightgbm")) {
      if(!is.null(Test_Importance)) data.table::setnames(Test_Importance, old = names(Test_Importance)[2], new = 'Test_Importance', skip_absent = TRUE)
    } else {
      # h2o col 3 is scaled importance which is preferred
      if(!is.null(Test_Importance)) data.table::setnames(Test_Importance, old = names(Test_Importance)[3], new = 'Test_Importance', skip_absent = TRUE)
    }
    
    # Non CatBoost only
    if(!is.null(Test_Importance)) {
      All_Importance <- Test_Importance
    } else {
      All_Importance <- NULL
    }
    
  }
  
  ## Model_IntImportanceTable ----
  if(tolower(Algo) == 'catboost') {
    Test_Interaction <- ModelObject[['InteractionImportance']][['Test_Interaction']]
    Validation_Interaction <- ModelObject[['InteractionImportance']][['Validation_Interaction']]
    Train_Interaction <- ModelObject[['InteractionImportance']][['Train_Interaction']]
    
    # Update Colnames
    if(!is.null(Test_Interaction)) data.table::setnames(Test_Interaction, old = 'score', new = 'Test_Importance', skip_absent = TRUE)
    if(!is.null(Validation_Interaction)) data.table::setnames(Validation_Interaction, old = 'score', new = 'Validation_Importance', skip_absent = TRUE)
    if(!is.null(Train_Interaction)) data.table::setnames(Train_Interaction, old = 'score', new = 'Train_Importance', skip_absent = TRUE)

    # CatBoost only
    if(is.null(Test_Interaction) && is.null(Validation_Interaction) && is.null(Train_Interaction)) {
      All_Interaction <- NULL
    } else if(!is.null(Test_Interaction) && !is.null(Validation_Interaction) && !is.null(Train_Interaction)) {
      All_Interaction <- merge(Test_Interaction, Validation_Interaction, by = c('Features1','Features2'), all = TRUE)
      All_Interaction <- merge(All_Interaction, Train_Interaction, by = c('Features1','Features2'), all = TRUE)
      data.table::setorderv(x = All_Interaction, cols = names(All_Interaction)[3L], order = -1)
    } else if(!is.null(Test_Interaction) && !is.null(Validation_Interaction) && is.null(Train_Interaction)) {
      All_Interaction <- merge(Test_Interaction, Validation_Interaction, by = c('Features1','Features2'), all = TRUE)
      data.table::setorderv(x = All_Interaction, cols = names(All_Interaction)[3L], order = -1)
    } else if(!is.null(Test_Interaction) && is.null(Validation_Interaction) && !is.null(Train_Interaction)) {
      All_Interaction <- merge(Test_Interaction, Train_Interaction, by = c('Features1','Features2'), all = TRUE)
      data.table::setorderv(x = All_Interaction, cols = names(All_Interaction)[3L], order = -1)
    } else if(is.null(Test_Interaction) && !is.null(Validation_Interaction) && !is.null(Train_Interaction)) {
      All_Interaction <- merge(Validation_Interaction, Train_Interaction, by = c('Features1','Features2'), all = TRUE)
      data.table::setorderv(x = All_Interaction, cols = names(All_Interaction)[3L], order = -1)
    } else if(is.null(Test_Interaction) && is.null(Validation_Interaction) && !is.null(Train_Interaction)) {
      All_Interaction <- Train_Interaction
    } else if(is.null(Test_Interaction) && !is.null(Validation_Interaction) && is.null(Train_Interaction)) {
      All_Interaction <- Validation_Interaction
    } else if(!is.null(Test_Interaction) && is.null(Validation_Interaction) && is.null(Train_Interaction)) {
      All_Interaction <- Test_Interaction
    } else {
      All_Interaction <- NULL
    }
  } else {
    All_Interaction <- NULL
  }
}
``` 

```{r Generic_DataSets_And_MetaData, echo = FALSE}
if(is.null(ModelObject)) {
  
  # DataSets
  if(is.null(TestData) && file.exists(file.path(SourcePath, paste0(ModelID, "_ValidationData.csv")))) {
    TestData <- data.table::fread(file = file.path(SourcePath, paste0(ModelID, "_ValidationData.csv")))
  }
  # Validate
  if(is.null(ValidationData) && file.exists(file.path(SourcePath, paste0(ModelID, "_ValData.csv")))) {
    ValidationDataData <- data.table::fread(file = file.path(SourcePath, paste0(ModelID, "_ValData.csv")))
  }
  # Train
  if(is.null(TrainData) && file.exists(file.path(SourcePath, paste0(ModelID, "_TrainData.csv")))) {
    TrainData <- data.table::fread(file = file.path(SourcePath, paste0(ModelID, "_TrainData.csv")))
  }
  
  # Meta info
  TargetColumnName <- TargetColumnName
  PredictionColumnName <- PredictionColumnName
  if(is.null(FeatureColumnNames) && !is.null(TestData)) {
    FeatureColumnNames <- names(TestData)[!names(TestData) %in% c(TargetColumnName, PredictionColumnName)]
  }
  if(is.null(FeatureColumnNames) && !is.null(ValidationData)) {
    FeatureColumnNames <- names(ValidationData)[!names(ValidationData) %in% c(TargetColumnName, PredictionColumnName)]
  }
  if(is.null(FeatureColumnNames) && !is.null(TrainData)) {
    FeatureColumnNames <- names(TrainData)[!names(TrainData) %in% c(TargetColumnName, PredictionColumnName)]
  }
  if(is.list(FeatureColumnNames) || data.table::is.data.table(FeatureColumnNames)) {
    FeatureColumnNames <- FeatureColumnNames[[1L]]
  }
  if(is.null(DateColumnName) && !is.null(ModelObject[['ArgsList']][['PrimaryDateColumn']])) {
    DateColumnName <- ModelObject[['ArgsList']][['PrimaryDateColumn']]
  } else {
    DateColumnName <- NULL
  }
}
```

```{r Generic_Model_MetaData, echo = FALSE}
if(is.null(ModelObject)) {

  # Model MetaData ----

  ## Model_MetaData_Parameters ----
  if(!is.null(SourcePath) && !is.null(ModelID)) {
    if(file.exists(file.path(SourcePath, paste0(ModelID, "_ArgsList.Rdata")))) {
      load(file.path(SourcePath, paste0(ModelID, "_ArgsList.Rdata")))
    }
  } else {
    ArgsList <- NULL
  }

  ## Model_MetaData_GridMetrics ----
  if(!is.null(SourcePath) && !is.null(ModelID)) {
    if(file.exists(file.path(SourcePath, paste0(ModelID, "_GridMetrics.csv")))) {
      GridMetrics <- data.table::fread(file = file.path(SourcePath, paste0(ModelID, "_GridMetrics.csv")))
    } else {
      GridMetrics <- NULL
    }
  } else {
    GridMetrics <- NULL
  }
}
```
  
```{r Generic_Evaluation_Metrics, echo = FALSE}  
if(is.null(ModelObject)) {
  
  # Evaluation Metrics ----
    
  ## Model_Evaluation_Metrics ----
  
  ### Test
  if(!is.null(TestData) && !is.null(TrainData) && !file.exists(file.path(SourcePath, paste0(ModelID, "_Test_EvaluationMetrics.csv")))) {
    Test_EvalMetrics <- AutoQuant:::RegressionMetrics(
      SaveModelObjects. = FALSE,
      data.           = TrainData,
      ValidationData. = TestData,
      TrainOnFull. = TRUE,
      LossFunction. = 'mse',
      EvalMetric. = 'RMSE',
      TargetColumnName. = TargetColumnName,
      ModelID. = ModelID,
      model_path. = SourcePath,
      metadata_path. = SourcePath)
  } else if(!is.null(TestData) && is.null(TrainData) && !file.exists(file.path(SourcePath, paste0(ModelID, "_Test_EvaluationMetrics.csv")))) {
    Test_EvalMetrics <- AutoQuant:::RegressionMetrics(
      SaveModelObjects. = FALSE,
      data.           = TestData,
      ValidationData. = TestData,
      TrainOnFull. = TRUE,
      LossFunction. = 'mse',
      EvalMetric. = 'RMSE',
      TargetColumnName. = TargetColumnName,
      ModelID. = ModelID,
      model_path. = SourcePath,
      metadata_path. = SourcePath)
  } else if(file.exists(file.path(SourcePath, paste0(ModelID, "_Test_EvaluationMetrics.csv")))) {
    Test_EvalMetrics <- data.table::fread(file = file.path(SourcePath, paste0(ModelID, "_Test_EvaluationMetrics.csv")))
  } else {
    Test_EvalMetrics <- NULL
  }

  ### Train
  if(!is.null(TrainData) && !file.exists(file.path(SourcePath, paste0(ModelID, "_Train_EvaluationMetrics.csv")))) {
    Train_EvalMetrics <- AutoQuant:::RegressionMetrics(
      SaveModelObjects. = FALSE,
      data. = TrainData,
      ValidationData. = TrainData,
      TrainOnFull. = TRUE,
      LossFunction. = 'mse',
      EvalMetric. = 'RMSE',
      TargetColumnName. = TargetColumnName,
      ModelID. = ModelID,
      model_path. = SourcePath,
      metadata_path. = SourcePath)
  } else if(file.exists(file.path(SourcePath, paste0(ModelID, "_Train_EvaluationMetrics.csv")))) {
    Train_EvalMetrics <- data.table::fread(file = file.path(SourcePath, paste0(ModelID, "_Train_EvaluationMetrics.csv")))
  } else {
    Train_EvalMetrics <- NULL
  }
  
  ## Model_VarImportanceTable ----
  if(tolower(Algo) == 'catboost') {
    if(file.exists(file.path(SourcePath, paste0(ModelID, "_Test_Importance_VariableImportance.csv")))) {
      Test_Importance <- data.table::fread(file = file.path(SourcePath, paste0(ModelID, "_Test_Importance_VariableImportance.csv")))
    } else {
      Test_Importance <- NULL
    }
    if(file.exists(file.path(SourcePath, paste0(ModelID, "_Validation_Importance_VariableImportance.csv")))) {
      Validation_Importance <- data.table::fread(file = file.path(SourcePath, paste0(ModelID, "_Validation_Importance_VariableImportance.csv")))
    } else {
      Validation_Importance <- NULL
    }
    if(file.exists(file.path(SourcePath, paste0(ModelID, "_Train_Importance_VariableImportance.csv")))) {
      Train_Importance <- data.table::fread(file = file.path(SourcePath, paste0(ModelID, "_Train_Importance_VariableImportance.csv")))
    } else {
      Train_Importance <- NULL
    }
    
    # Update Colnames
    if(!is.null(Test_Importance)) data.table::setnames(Test_Importance, old = 'Importance', new = 'Test_Importance', skip_absent = TRUE)
    if(!is.null(Validation_Importance)) data.table::setnames(Validation_Importance, old = 'Importance', new = 'Validation_Importance', skip_absent = TRUE)
    if(!is.null(Train_Importance)) data.table::setnames(Train_Importance, old = 'Importance', new = 'Train_Importance', skip_absent = TRUE)

    # CatBoost only
    if(is.null(Test_Importance) && is.null(Validation_Importance) && is.null(Train_Importance)) {
      All_Importance <- NULL
    } else if(!is.null(Test_Importance) && !is.null(Validation_Importance) && !is.null(Train_Importance)) {
      All_Importance <- merge(Test_Importance, Validation_Importance, by = 'Variable', all = TRUE)
      All_Importance <- merge(All_Importance, Train_Importance, by = 'Variable', all = TRUE)
    } else if(!is.null(Test_Importance) && !is.null(Validation_Importance) && is.null(Train_Importance)) {
      All_Importance <- merge(Test_Importance, Validation_Importance, by = 'Variable', all = TRUE)
    } else if(!is.null(Test_Importance) && is.null(Validation_Importance) && !is.null(Train_Importance)) {
      All_Importance <- merge(Test_Importance, Train_Importance, by = 'Variable', all = TRUE)
    } else if(is.null(Test_Importance) && !is.null(Validation_Importance) && !is.null(Train_Importance)) {
      All_Importance <- merge(Validation_Importance, Train_Importance, by = 'Variable', all = TRUE)
    } else if(is.null(Test_Importance) && is.null(Validation_Importance) && !is.null(Train_Importance)) {
      All_Importance <- Train_Importance
    } else if(is.null(Test_Importance) && !is.null(Validation_Importance) && is.null(Train_Importance)) {
      All_Importance <- Validation_Importance
    } else if(!is.null(Test_Importance) && is.null(Validation_Importance) && is.null(Train_Importance)) {
      All_Importance <- Test_Importance
    } else {
      All_Importance <- NULL
    }
    
  } else {
    
    # Encoding-based Models + Generic Connector
    if(is.null(Test_Importance_dt)) {
      Test_Importance <- NULL
    } else {
      Test_Importance <- Test_Importance_dt
    }
    if(is.null(Validation_Importance_dt)) {
      Validation_Importance <- NULL
    } else {
      Validation_Importance <- Validation_Importance_dt
    }
    if(is.null(Train_Importance_dt)) {
      Train_Importance <- NULL
    } else {
      Train_Importance <- Train_Importance_dt
    }
    
    # Update Colnames
    if(!is.null(Test_Importance)) data.table::setnames(Test_Importance, old = 'Importance', new = 'Test_Importance', skip_absent = TRUE)
    if(!is.null(Validation_Importance)) data.table::setnames(Validation_Importance, old = 'Importance', new = 'Validation_Importance', skip_absent = TRUE)
    if(!is.null(Train_Importance)) data.table::setnames(Train_Importance, old = 'Importance', new = 'Train_Importance', skip_absent = TRUE)

  }
  
  ## Model_IntImportanceTable ----
  if(tolower(Algo) == 'catboost') {
    if(file.exists(file.path(SourcePath, paste0(ModelID, "_Test_Interaction_Interaction.csv")))) {
      Test_Interaction <- data.table::fread(file = file.path(SourcePath, paste0(ModelID, "_Test_Interaction_Interaction.csv")))
    } else {
      Test_Interaction <- NULL
    }
    if(file.exists(file.path(SourcePath, paste0(ModelID, "_Validation_Interaction_Interaction.csv")))) {
      Validation_Interaction <- data.table::fread(file = file.path(SourcePath, paste0(ModelID, "_Validation_Interaction_Interaction.csv")))
    } else {
      Validation_Interaction <- NULL
    }
    if(file.exists(file.path(SourcePath, paste0(ModelID, "_Train_Interaction_Interaction.csv")))) {
      Train_Interaction <- data.table::fread(file = file.path(SourcePath, paste0(ModelID, "_Train_Interaction_Interaction.csv")))
    } else {
      Train_Interaction <- NULL
    }
    
    # Update Colnames
    if(!is.null(Test_Interaction)) data.table::setnames(Test_Interaction, old = 'score', new = 'Test_Importance', skip_absent = TRUE)
    if(!is.null(Validation_Interaction)) data.table::setnames(Validation_Interaction, old = 'score', new = 'Validation_Importance', skip_absent = TRUE)
    if(!is.null(Train_Interaction)) data.table::setnames(Train_Interaction, old = 'score', new = 'Train_Importance', skip_absent = TRUE)

    # CatBoost only
    if(is.null(Test_Interaction) && is.null(Validation_Interaction) && is.null(Train_Interaction)) {
      All_Interaction <- NULL
    } else if(!is.null(Test_Interaction) && !is.null(Validation_Interaction) && !is.null(Train_Interaction)) {
      All_Interaction <- merge(Test_Interaction, Validation_Interaction, by = c('Features1','Features2'), all = TRUE)
      All_Interaction <- merge(All_Interaction, Train_Interaction, by = c('Features1','Features2'), all = TRUE)
      data.table::setorderv(x = All_Interaction, cols = names(All_Interaction)[3L], order = -1)
    } else if(!is.null(Test_Interaction) && !is.null(Validation_Interaction) && is.null(Train_Interaction)) {
      All_Interaction <- merge(Test_Interaction, Validation_Interaction, by = c('Features1','Features2'), all = TRUE)
      data.table::setorderv(x = All_Interaction, cols = names(All_Interaction)[3L], order = -1)
    } else if(!is.null(Test_Interaction) && is.null(Validation_Interaction) && !is.null(Train_Interaction)) {
      All_Interaction <- merge(Test_Interaction, Train_Interaction, by = c('Features1','Features2'), all = TRUE)
      data.table::setorderv(x = All_Interaction, cols = names(All_Interaction)[3L], order = -1)
    } else if(is.null(Test_Interaction) && !is.null(Validation_Interaction) && !is.null(Train_Interaction)) {
      All_Interaction <- merge(Validation_Interaction, Train_Interaction, by = c('Features1','Features2'), all = TRUE)
      data.table::setorderv(x = All_Interaction, cols = names(All_Interaction)[3L], order = -1)
    } else if(is.null(Test_Interaction) && is.null(Validation_Interaction) && !is.null(Train_Interaction)) {
      All_Interaction <- Train_Interaction
    } else if(is.null(Test_Interaction) && !is.null(Validation_Interaction) && is.null(Train_Interaction)) {
      All_Interaction <- Validation_Interaction
    } else if(!is.null(Test_Interaction) && is.null(Validation_Interaction) && is.null(Train_Interaction)) {
      All_Interaction <- Test_Interaction
    } else {
      All_Interaction <- NULL
    }
    
  } else {
    All_Interaction <- NULL
  }
}
```

```{r Generic_Evaluation_Plots, echo = FALSE}

# Evaluation Plots ----
  
## EvaluationPlots_ResidualHistogram ----

### Test
Test_ResidualHistogram <- AutoPlots::Plot.Residuals.Histogram(
  dt = TestData,
  AggMethod = "mean",
  SampleSize = 100000,
  XVar = PredictionColumnName,
  YVar = TargetColumnName,
  GroupVar = NULL,
  YVarTrans = "Identity",
  XVarTrans = "Identity",
  FacetRows = 1,
  FacetCols = 1,
  FacetLevels = NULL,
  NumberBins = 20,
  Height = "600px",
  Width = "975px",
  Title = "Residuals Histogram",
  ShowLabels = FALSE,
  Title.YAxis = TargetColumnName,
  Title.XAxis = PredictionColumnName,
  EchartsTheme = "wef",
  TimeLine = FALSE,
  X_Scroll = TRUE,
  Y_Scroll = TRUE,
  TextColor = "white",
  title.fontSize = 22,
  title.fontWeight = "bold",
  title.textShadowColor = "#63aeff",
  title.textShadowBlur = 3,
  title.textShadowOffsetY = 1,
  title.textShadowOffsetX = -1,
  xaxis.fontSize = 14,
  yaxis.fontSize = 14,
  Debug = FALSE)

### Train
if(length(TrainData) > 0L) {
  Train_ResidualHistogram <- AutoPlots::Plot.Residuals.Histogram(
    dt = TrainData,
    AggMethod = "mean",
    SampleSize = 100000,
    XVar = PredictionColumnName,
    YVar = TargetColumnName,
    GroupVar = NULL,
    YVarTrans = "Identity",
    XVarTrans = "Identity",
    FacetRows = 1,
    FacetCols = 1,
    FacetLevels = NULL,
    NumberBins = 20,
    Height = "600px",
    Width = "975px",
    Title = "Residuals Histogram",
    ShowLabels = FALSE,
    Title.YAxis = TargetColumnName,
    Title.XAxis = 'Predict',
    EchartsTheme = "wef",
    TimeLine = FALSE,
    X_Scroll = TRUE,
    Y_Scroll = TRUE,
    TextColor = "white",
    title.fontSize = 22,
    title.fontWeight = "bold",
    title.textShadowColor = "#63aeff",
    title.textShadowBlur = 3,
    title.textShadowOffsetY = 1,
    title.textShadowOffsetX = -1,
    xaxis.fontSize = 14,
    yaxis.fontSize = 14,
    Debug = FALSE)
}


## EvaluationPlots_CalibrationPlot ----

### Test
Test_EvaluationPlot <- AutoPlots::Plot.Calibration.Line(
  dt = TestData,
  AggMethod = "mean",
  XVar = PredictionColumnName,
  YVar = TargetColumnName,
  GroupVar = NULL,
  YVarTrans = "Identity",
  XVarTrans = "Identity",
  FacetRows = 1,
  FacetCols = 1,
  FacetLevels = NULL,
  NumberBins = 21,
  Height = "600px",
  Width = "975px",
  Title = "Calibration Line Plot",
  ShowLabels = FALSE,
  Title.YAxis = TargetColumnName,
  Title.XAxis = "Predict",
  EchartsTheme = "wef",
  
  TimeLine = TRUE,
  X_Scroll = TRUE,
  Y_Scroll = TRUE,
  TextColor = "white",
  Debug = FALSE)

### Train
if(!is.null(TrainData)) {
  Train_EvaluationPlot <- AutoPlots::Plot.Calibration.Line(
    dt = TrainData,
    AggMethod = "mean",
    XVar = PredictionColumnName,
    YVar = TargetColumnName,
    GroupVar = NULL,
    YVarTrans = "Identity",
    XVarTrans = "Identity",
    FacetRows = 1,
    FacetCols = 1,
    FacetLevels = NULL,
    NumberBins = 21,
    Height = "600px",
    Width = "975px",
    Title = "Calibration Line Plot",
    Title.YAxis = TargetColumnName,
    Title.XAxis = "Predict",
    EchartsTheme = "wef",
    
    TimeLine = TRUE,
    X_Scroll = TRUE,
    Y_Scroll = TRUE,
    TextColor = "white",
    Debug = FALSE)
}

## EvaluationPlots_CalibrationBoxPlot ----

### Test
Test_EvaluationBoxPlot <- AutoPlots::Plot.Calibration.Box(
  dt = TestData,
  SampleSize = 100000L,
  AggMethod = "mean",
  XVar = PredictionColumnName,
  YVar = TargetColumnName,
  GroupVar = NULL,
  YVarTrans = "Identity",
  XVarTrans = "Identity",
  FacetRows = 1,
  FacetCols = 1,
  FacetLevels = NULL,
  NumberBins = 21,
  Height = "600px",
  Width = "975px",
  Title = "Calibration Plot",
  ShowLabels = FALSE,
  Title.YAxis = TargetColumnName,
  Title.XAxis = "Predict",
  EchartsTheme = "wef",
  
  TimeLine = TRUE,
  X_Scroll = TRUE,
  Y_Scroll = TRUE,
  TextColor = "white",
  Debug = FALSE)

### Train
if(!is.null(TrainData)) {
  Train_EvaluationBoxPlot <- AutoPlots::Plot.Calibration.Box(
    dt = TrainData,
    SampleSize = 100000L,
    AggMethod = "mean",
    XVar = PredictionColumnName,
    YVar = TargetColumnName,
    GroupVar = NULL,
    YVarTrans = "Identity",
    XVarTrans = "Identity",
    FacetRows = 1,
    FacetCols = 1,
    FacetLevels = NULL,
    NumberBins = 21,
    Height = "600px",
    Width = "975px",
    Title = "Calibration Plot",
    ShowLabels = FALSE,
    Title.YAxis = TargetColumnName,
    Title.XAxis = "Predict",
    EchartsTheme = "wef",
    
    TimeLine = TRUE,
    X_Scroll = TRUE,
    Y_Scroll = TRUE,
    TextColor = "white",
    Debug = FALSE)
}

## EvaluationPlots_ResidualsScatterPlot (depends on ) ----
Test_ScatterPlot <- AutoPlots::Plot.Residuals.Scatter(
  dt = TestData,
  AggMethod = "mean",
  SampleSize = 100000,
  XVar = PredictionColumnName,
  YVar = TargetColumnName,
  GroupVar = NULL,
  YVarTrans = "Identity",
  XVarTrans = "Identity",
  FacetRows = 1,
  FacetCols = 1,
  FacetLevels = NULL,
  Height = "600px",
  Width = "975px",
  Title = "Calibration Plot",
  ShowLabels = FALSE,
  Title.YAxis = TargetColumnName,
  Title.XAxis = g,
  EchartsTheme = "wef",
  
  TimeLine = TRUE,
  X_Scroll = TRUE,
  Y_Scroll = TRUE,
  TextColor = "white",
  Debug = FALSE)

if(length(TrainData) > 0L) {
  Train_ScatterPlot <- AutoPlots::Plot.Residuals.Scatter(
    dt = TrainData,
    AggMethod = "mean",
    SampleSize = 100000,
    XVar = PredictionColumnName,
    YVar = TargetColumnName,
    GroupVar = NULL,
    YVarTrans = "Identity",
    XVarTrans = "Identity",
    FacetRows = 1,
    FacetCols = 1,
    FacetLevels = NULL,
    Height = "600px",
    Width = "975px",
    Title = "Residuals ScatterPlot",
    ShowLabels = FALSE,
    Title.YAxis = TargetColumnName,
    Title.XAxis = g,
    EchartsTheme = "wef",
    
    TimeLine = TRUE,
    X_Scroll = TRUE,
    Y_Scroll = TRUE,
    TextColor = "white",
    Debug = FALSE)
}

```

```{r ModelObject_Model_Interpretation, echo = FALSE}

# Model Interpretation ----

## Model_Evaluation_Metrics_NumericVariables ----

### TestData ----

# Plots to Add and Remove

# Starting batch of plots
Test_ParDepPlots <- list()
  
# Add Plots
if(!is.null(TestData) && !is.null(FeatureColumnNames)) {
  for(g in FeatureColumnNames) {
    if(is.numeric(TestData[[g]])) {
      
      # Add
      Test_ParDepPlots[[g]] <- AutoPlots::Plot.PartialDependence.Line(
        dt = TestData,
        XVar = g,
        YVar = TargetColumnName,
        ZVar = 'Predict',
        YVarTrans = "Identity",
        XVarTrans = "Identity",
        ZVarTrans = "Identity",
        FacetRows = 1,
        FacetCols = 1,
        FacetLevels = NULL,
        GroupVar = NULL,
        NumberBins = 20,
        AggMethod = "mean",
        Height = "600px",
        Width = "975px",
        Title = "Partial Dependence Line",
        ShowLabels = FALSE,
        Title.YAxis = TargetColumnName,
        Title.XAxis = g,
        EchartsTheme = "wef",
        
        TimeLine = TRUE,
        X_Scroll = TRUE,
        Y_Scroll = TRUE,
        TextColor = "white",
        Debug = FALSE)
    }
  }
}

### TrainData ----

# Plots to Add and Remove

# Starting batch of plots
Train_ParDepPlots <- list() # ModelObject[['PlotList']][['Train_ParDepPlots']]

# Add Plots
if(!is.null(TrainData) && !is.null(FeatureColumnNames)) {
  for(g in FeatureColumnNames) {
    if(is.numeric(TrainData[[g]])) {

      # Add
      Train_ParDepPlots[[g]] <- AutoPlots::Plot.PartialDependence.Line(
        dt = TrainData,
        XVar = g,
        YVar = TargetColumnName,
        ZVar = 'Predict',
        YVarTrans = "Identity",
        XVarTrans = "Identity",
        ZVarTrans = "Identity",
        FacetRows = 1,
        FacetCols = 1,
        FacetLevels = NULL,
        GroupVar = NULL,
        NumberBins = 20,
        AggMethod = "mean",
        Height = "600px",
        Width = "975px",
        Title = "Partial Dependence Line",
        ShowLabels = FALSE,
        Title.YAxis = TargetColumnName,
        Title.XAxis = g,
        EchartsTheme = "wef",
        
        TimeLine = TRUE,
        X_Scroll = TRUE,
        Y_Scroll = TRUE,
        TextColor = "white",
        Debug = FALSE)
    }
  }
}

## Model_Evaluation_Metrics_NumericVariables_Box ----
  
### Test Data ----
  
# Starting batch of plots
Test_ParDepBoxPlots <- list()

# Add Plots
if(!is.null(TestData) && !is.null(FeatureColumnNames)) {
  for(g in FeatureColumnNames) {
    if(is.numeric(TestData[[g]])) {

      # Add
      Test_ParDepBoxPlots[[g]] <- AutoPlots::Plot.PartialDependence.Box(
        dt = TestData,
        XVar = g,
        YVar = TargetColumnName,
        ZVar = 'Predict',
        YVarTrans = "Identity",
        XVarTrans = "Identity",
        ZVarTrans = "Identity",
        FacetRows = 1,
        FacetCols = 1,
        FacetLevels = NULL,
        GroupVar = NULL,
        NumberBins = 20,
        AggMethod = "mean",
        Height = "600px",
        Width = "975px",
        Title = "Partial Dependence Line",
        ShowLabels = FALSE,
        Title.YAxis = TargetColumnName,
        Title.XAxis = g,
        EchartsTheme = "wef",
        
        TimeLine = TRUE,
        X_Scroll = TRUE,
        Y_Scroll = TRUE,
        TextColor = "white",
        Debug = FALSE)
    }
  }
}
  
### Train Data ----

# Starting batch of plots
Train_ParDepBoxPlots <- list()

# Add Plots
if(!is.null(TrainData) && !is.null(FeatureColumnNames)) {
  for(g in FeatureColumnNames) {
    if(is.numeric(TrainData[[g]])) {

      # Add
      Train_ParDepBoxPlots[[g]] <- AutoPlots::Plot.PartialDependence.Box(
        dt = TrainData,
        XVar = g,
        YVar = TargetColumnName,
        ZVar = 'Predict',
        YVarTrans = "Identity",
        XVarTrans = "Identity",
        ZVarTrans = "Identity",
        FacetRows = 1,
        FacetCols = 1,
        FacetLevels = NULL,
        GroupVar = NULL,
        NumberBins = 20,
        AggMethod = "mean",
        Height = "600px",
        Width = "975px",
        Title = "Partial Dependence Line",
        ShowLabels = FALSE,
        Title.YAxis = TargetColumnName,
        Title.XAxis = g,
        EchartsTheme = "wef",
        
        TimeLine = TRUE,
        X_Scroll = TRUE,
        Y_Scroll = TRUE,
        TextColor = "white",
        Debug = FALSE)
    }
  }
}
  
## Model_Evaluation_Metrics_CategoricalVariables ---- 

### Test Data ----

# Starting batch of plots
Test_ParDepCatPlots <- list()
  
# Add Plots
if(!is.null(TestData) && !is.null(FeatureColumnNames)) {
  for(g in FeatureColumnNames) {
    if(!is.numeric(TestData[[g]])) {
      
      Test_ParDepCatPlots[[g]] <- AutoPlots::Plot.PartialDependence.HeatMap(
        dt = TestData,
        XVar = g,
        YVar = TargetColumnName,
        ZVar = 'Predict',
        YVarTrans = "Identity",
        XVarTrans = "Identity",
        ZVarTrans = "Identity",
        FacetRows = 1,
        FacetCols = 1,
        FacetLevels = NULL,
        GroupVar = NULL,
        NumberBins = 20,
        AggMethod = "mean",
        Height = "600px",
        Width = "975px",
        Title = "Partial Dependence Line",
        ShowLabels = FALSE,
        Title.YAxis = TargetColumnName,
        Title.XAxis = g,
        EchartsTheme = "wef",
        
        TimeLine = TRUE,
        X_Scroll = TRUE,
        Y_Scroll = TRUE,
        TextColor = "white",
        Debug = FALSE)
    }
  }
}
  
### Train Data ----

# Starting batch of plots
Train_ParDepCatPlots <- list()

# Add Plots
if(!is.null(TrainData) && !is.null(FeatureColumnNames)) {
  for(g in FeatureColumnNames) {
    if(!is.numeric(TrainData[[g]])) {
      
      Train_ParDepCatPlots[[g]] <- AutoPlots::Plot.PartialDependence.HeatMap(
        dt = TrainData,
        XVar = g,
        YVar = TargetColumnName,
        ZVar = 'Predict',
        YVarTrans = "Identity",
        XVarTrans = "Identity",
        ZVarTrans = "Identity",
        FacetRows = 1,
        FacetCols = 1,
        FacetLevels = NULL,
        GroupVar = NULL,
        NumberBins = 20,
        AggMethod = "mean",
        Height = "600px",
        Width = "975px",
        Title = "Partial Dependence Line",
        ShowLabels = FALSE,
        Title.YAxis = TargetColumnName,
        Title.XAxis = g,
        EchartsTheme = "wef",
        
        TimeLine = TRUE,
        X_Scroll = TRUE,
        Y_Scroll = TRUE,
        TextColor = "white",
        Debug = FALSE)
    }
  }
}

```

# <font size="6">Model Evaluation and Insights:</font>

The two main goals with this document are to provide a wide range of output to investigate high level performance and insights and to deliver a high quality report design layout to increase user experience. The metrics provided are intended to be semi-comprehensive. One can always dig deeper into results to gain further insights. In light of that, the results are intended to provide one what they need to come to a reasonable conclusion about their model or to find the area where they need to dig a deeper. 

## Evaluation Metrics
This section contains statistics and variable importance measures to help the user understand model performance at a high level. If the user chose to include Train Data results then these can be used to compare against the Test Data results to identify over / under fitting of models.

## Evaluation Plots 
This section contains visualizations that span the range of predicted values and the associated accuracies across that range. The predicted values range are broken up into every 5th percentile to provide a solid range for evaluation.

## Model Interpretation sections 
These contains visualizations intended to open up the black box of your algorithm. When one inspects coefficients from a regression model, the insights they gain are two-fold: they get an understanding about statistics significance, and they gain an understanding of the variable's effect on the target variable. However, not all relationships are linear and sometimes the user doesn't specifiy an appropriate model structure to fully capture the nature of the relationship, which can lead to incorrect conclusions about statistical signifance along with incorrect conclusions about the nature of the relationship. These visualizations provide a way to understand what the exact nature of those relationships are and if the user chooses, they can attempt to fit the relationship better with an appropriate statistical model to gain a better understanding of statistical significance.


# <font size="6">Evaluation Metrics</font>
<p>

<details><summary>Expand</summary>
<p>



##  <font size="5">Evaluation Metrics Tables</font>

<details><summary>Model Metrics Tables</summary>
<p>


### **TestData**
<p>

<details><summary>Performance Metrics</summary>
<p>

```{r Model_Evaluation_Metrics, echo=FALSE}
if(!is.null(Test_EvalMetrics)) {
  reactable::reactable(
    width = 1075,
    data = Test_EvalMetrics,
    compact = TRUE,
    defaultPageSize = 10,
    wrap = FALSE,
    filterable = TRUE,
    fullWidth = FALSE,
    highlight = TRUE,
    pagination = TRUE,
    resizable = TRUE,
    searchable = TRUE,
    selection = "multiple",
    showPagination = TRUE,
    showSortable = TRUE,
    showSortIcon = TRUE,
    sortable = TRUE,
    striped = TRUE,
    theme = reactable::reactableTheme(
      color = 'black',
      backgroundColor = "#4f4f4f26",
      borderColor = "#dfe2e5",
      stripedColor = "#4f4f4f8f",
      highlightColor = "#8989898f",
      cellPadding = "8px 12px",
      style = list(
        fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif"
      ),
      searchInputStyle = list(width = "100%")
    )
  )
} else {
  print('Test_EvalMetrics is NULL')
}
```

</details>
</p>


### **TrainData + ValidationData**
<p>

<details><summary>Performance Metrics</summary>
<p>

```{r Model_Evaluation_Metrics_Train, echo=FALSE}
if(!is.null(Train_EvalMetrics)) {
  reactable::reactable(
    width = 1075,
    data = Train_EvalMetrics,
    compact = TRUE,
    defaultPageSize = 10,
    wrap = FALSE,
    filterable = TRUE,
    fullWidth = FALSE,
    highlight = TRUE,
    pagination = TRUE,
    resizable = TRUE,
    searchable = TRUE,
    selection = "multiple",
    showPagination = TRUE,
    showSortable = TRUE,
    showSortIcon = TRUE,
    sortable = TRUE,
    striped = TRUE,
    theme = reactable::reactableTheme(
      color = 'black',
      backgroundColor = "#4f4f4f26",
      borderColor = "#dfe2e5",
      stripedColor = "#4f4f4f8f",
      highlightColor = "#8989898f",
      cellPadding = "8px 12px",
      style = list(
        fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif"
      ),
      searchInputStyle = list(width = "100%")
    )
  )
} else {
  print('Train_EvalMetrics is NULL')
}
```

</details>
</p>



##  <font size="5">Variable Importance Tables</font>
<p>

<details><summary>Variable Importance Table</summary>
<p>

```{r Model_VarImportanceTable, echo=FALSE}
if(!is.null(All_Importance)) {
  data.table::setorderv(x = All_Importance, cols = names(All_Importance)[2L], order = -1L, na.last = TRUE)
  reactable::reactable(
    width = 1075,
    data = All_Importance,
    compact = TRUE,
    defaultPageSize = 10,
    wrap = FALSE,
    filterable = TRUE,
    fullWidth = TRUE,
    highlight = TRUE,
    pagination = TRUE,
    resizable = TRUE,
    searchable = TRUE,
    selection = "multiple",
    showPagination = TRUE,
    showSortable = TRUE,
    showSortIcon = TRUE,
    sortable = TRUE,
    striped = TRUE,
    theme = reactable::reactableTheme(
      color = 'black',
      backgroundColor = "#4f4f4f26",
      borderColor = "#dfe2e5",
      stripedColor = "#4f4f4f8f",
      highlightColor = "#8989898f",
      cellPadding = "8px 12px",
      style = list(
        fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif"
      ),
      searchInputStyle = list(width = "100%")
    )
  )
} else {
  print("No importance data was provided")
}
```

</details>
</p>




##  <font size="5">Interaction Importance Tables</font>

<details><summary>Interaction Importance Tables</summary>
<p>


```{r Model_IntImportanceTable, echo=FALSE}
if(exists("All_Interaction") && !is.null(All_Interaction)) {
  data.table::setorderv(x = All_Interaction, cols = names(All_Importance)[3L], order = -1L, na.last = TRUE)
  reactable::reactable(
    width = 1075,
    data = All_Interaction,
    compact = TRUE,
    defaultPageSize = 10,
    wrap = FALSE,
    filterable = TRUE,
    fullWidth = TRUE,
    highlight = TRUE,
    pagination = TRUE,
    resizable = TRUE,
    searchable = TRUE,
    selection = "multiple",
    showPagination = TRUE,
    showSortable = TRUE,
    showSortIcon = TRUE,
    sortable = TRUE,
    striped = TRUE,
    theme = reactable::reactableTheme(
      color = 'black',
      backgroundColor = "#4f4f4f26",
      borderColor = "#dfe2e5",
      stripedColor = "#4f4f4f8f",
      highlightColor = "#8989898f",
      cellPadding = "8px 12px",
      style = list(
        fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif"
      ),
      searchInputStyle = list(width = "100%")
    )
  )
} else {
  print('Interaction importance is only available with CatBoost')
}
```



</details>
</p>



</details>
</p>





# <font size="6">Evaluation Plots</font>
<p>

<details><summary>Expand</summary>
<p>



## <font size="5">Variable Importance Plots</font>
<p>

<details><summary>Expand</summary>
<p>


```{r EvaluationPlots_VIPlot, echo=FALSE}
if(!is.null(Test_Importance)) {
  if("Train_Importance" %in% names(Test_Importance)) data.table::setnames(Test_Importance, 'Train_Importance', 'Importance', skip_absent = TRUE)
  if("Test_Importance" %in% names(Test_Importance)) data.table::setnames(Test_Importance, "Test_Importance", "Importance", skip_absent = TRUE)
  AutoPlots::Plot.VariableImportance(
    dt = Test_Importance,
    XVar = "Importance",
    YVar = "Variable",
    GroupVar = NULL,
    YVarTrans = "Identity",
    XVarTrans = "Identity",
    FacetRows = 1,
    FacetCols = 1,
    FacetLevels = NULL,
    AggMethod = "mean",
    Height = "600px",
    Width = "975px",
    Title = "Variable Importance Plot",
    ShowLabels = FALSE,
    Title.YAxis = NULL,
    Title.XAxis = NULL,
    EchartsTheme = "wef",
    TimeLine = FALSE,
    X_Scroll = TRUE,
    Y_Scroll = TRUE,
    TextColor = "white",
    title.fontSize = 22,
    title.fontWeight = "bold",
    title.textShadowColor = "#63aeff",
    title.textShadowBlur = 3,
    title.textShadowOffsetY = 1,
    title.textShadowOffsetX = -1,
    xaxis.fontSize = 14,
    yaxis.fontSize = 14,
    Debug = FALSE)
} else {
  print("Test_Importance is NULL")
}
if(!is.null(Validation_Importance)) {
  if("Validation_Importance" %in% names(Validation_Importance)) data.table::setnames(Validation_Importance, 'Validation_Importance', 'Importance', skip_absent = TRUE)
  if("Test_Importance" %in% names(Validation_Importance)) data.table::setnames(Validation_Importance, "Test_Importance", "Importance", skip_absent = TRUE)
  AutoPlots::Plot.VariableImportance(
    dt = Validation_Importance,
    XVar = "Importance",
    YVar = "Variable",
    GroupVar = NULL,
    YVarTrans = "Identity",
    XVarTrans = "Identity",
    FacetRows = 1,
    FacetCols = 1,
    FacetLevels = NULL,
    AggMethod = "mean",
    Height = "600px",
    Width = "975px",
    Title = "Variable Importance Plot",
    ShowLabels = FALSE,
    Title.YAxis = NULL,
    Title.XAxis = NULL,
    EchartsTheme = "wef",
    TimeLine = FALSE,
    X_Scroll = TRUE,
    Y_Scroll = TRUE,
    TextColor = "white",
    title.fontSize = 22,
    title.fontWeight = "bold",
    title.textShadowColor = "#63aeff",
    title.textShadowBlur = 3,
    title.textShadowOffsetY = 1,
    title.textShadowOffsetX = -1,
    xaxis.fontSize = 14,
    yaxis.fontSize = 14,
    Debug = FALSE)
} else {
  print("Validation_Importance is only provided for with CatBoost")
}
if(!is.null(Train_Importance)) {
  if("Train_Importance" %in% names(Train_Importance)) data.table::setnames(Train_Importance, 'Train_Importance', 'Importance', skip_absent = TRUE)
  if("Test_Importance" %in% names(Train_Importance)) data.table::setnames(Train_Importance, "Test_Importance", "Importance", skip_absent = TRUE)
  AutoPlots::Plot.VariableImportance(
    dt = Train_Importance,
    XVar = "Importance",
    YVar = "Variable",
    GroupVar = NULL,
    YVarTrans = "Identity",
    XVarTrans = "Identity",
    FacetRows = 1,
    FacetCols = 1,
    FacetLevels = NULL,
    AggMethod = "mean",
    Height = "600px",
    Width = "975px",
    Title = "Variable Importance Plot",
    ShowLabels = FALSE,
    Title.YAxis = NULL,
    Title.XAxis = NULL,
    EchartsTheme = "wef",
    TimeLine = FALSE,
    X_Scroll = TRUE,
    Y_Scroll = TRUE,
    TextColor = "white",
    title.fontSize = 22,
    title.fontWeight = "bold",
    title.textShadowColor = "#63aeff",
    title.textShadowBlur = 3,
    title.textShadowOffsetY = 1,
    title.textShadowOffsetX = -1,
    xaxis.fontSize = 14,
    yaxis.fontSize = 14,
    Debug = FALSE)
  
} else {
  print("Train_Importance is only provided for with CatBoost")
}
```

</details>
</p>



## <font size="5">Residual Histograms</font>
<p>

<details><summary>Expand</summary>
<p>

```{r EvaluationPlots_ResidualHistogram, echo=FALSE}
if(!is.null(Test_ResidualHistogram)) {
  eval(Test_ResidualHistogram)
} else {
  print('Test_ResidualHistogram is NULL or TestData is NULL')
}
if(!is.null(Train_ResidualHistogram)) {
  eval(Train_ResidualHistogram)
} else {
  print('Train_ResidualHistogram is NULL or TrainData is NULL')
}
```

</details>
</p>




## <font size="5">Calibration Plots</font>
<p>

<details><summary>Expand</summary>
<p>

```{r EvaluationPlots_CalibrationPlot, echo=FALSE}
if(!is.null(Test_EvaluationPlot)) {
  eval(Test_EvaluationPlot)
} else {
  print('Test_EvaluationPlot is NULL or TestData is NULL')
}
if(!is.null(Train_EvaluationPlot)) {
  eval(Train_EvaluationPlot)
} else {
  print('Test_EvaluationPlot is NULL or TrainData is NULL')
}
```

</details>
</p>



## <font size="5">Calibration BoxPlots</font>
<p>


<details><summary>Expand</summary>
<p>


```{r EvaluationPlots_CalibrationBoxPlot, echo=FALSE}
if(!is.null(Test_EvaluationBoxPlot)) {
  eval(Test_EvaluationBoxPlot)
} else {
  print('Test_EvaluationBoxPlot is NULL or TestData is NULL')
}
if(!is.null(Train_EvaluationBoxPlot)) {
  eval(Train_EvaluationBoxPlot)
} else {
  print('Train_EvaluationBoxPlot is NULL or TrainData is NULL')
}
```

</details>
</p>





## <font size="5">Residuals ScatterPlots</font>
<p>

<details><summary>Expand</summary>
<p>

```{r EvaluationPlots_ResidualsScatterPlot, echo=FALSE}
if(!is.null(Test_ScatterPlot)) {
  eval(Test_ScatterPlot)
} else {
  print('Test_ScatterPlot is NULL or TestData is NULL')
}
if(!is.null(Train_ScatterPlot)) {
  eval(Train_ScatterPlot)
} else {
  print('Train_ScatterPlot is NULL or TrainData is NULL')
}
```

</details>
</p>



</details>
</p>




# <font size="6">Model Interpretation</font>
<p>

<details><summary>Expand</summary>
<p>



## <font size="5">Partial Dependence Plots: Numeric-Features</font>
<p>

<details><summary>Expand</summary>
<p>


### Partial Dependence Line Plots
<p>

<details><summary>Expand</summary>
<p>


#### **TestData**
<p>

<details><summary>Partital Dependence Line Plots</summary>
<p>

```{r Model_Evaluation_Metrics_NumericVariables, echo=FALSE}
options(warn = -1)
if(!is.null(Test_ParDepPlots) && length(Test_ParDepPlots) > 0) {
  echarts4r::e_arrange(Test_ParDepPlots)
} else {
  print('Test_ParDepPlots is NULL and TestData is NULL')
}
options(warn = 1)
```

</details>
</p>


#### **TrainData** + **ValidationData**
<p>

<details><summary>Partital Dependence Line Plots</summary>
<p>

```{r Model_Evaluation_Metrics_NumericVariables_Train, echo=FALSE}
options(warn = -1)
if(!is.null(Train_ParDepPlots) && length(Train_ParDepPlots) > 0) {
  echarts4r::e_arrange(Train_ParDepPlots)
} else {
  print('Train_ParDepPlots is NULL and TrainData is NULL')
}
options(warn = 1)
```

</details>
</p>



### Partial Dependence Box Plots
<p>

<details><summary>Expand</summary>
<p>


#### **TestData**
<p>

<details><summary>Partital Dependence Box Plots</summary>
<p>

```{r Model_Evaluation_Metrics_NumericVariables_Box, echo=FALSE}
options(warn = -1)
if(!is.null(Test_ParDepBoxPlots) && length(Test_ParDepBoxPlots) > 0) {
  echarts4r::e_arrange(Test_ParDepBoxPlots)
} else {
  print('Test_ParDepBoxPlots is NULL and TestData is NULL')
}
options(warn = 1)
```

</details>
</p>


#### **TrainData** + **ValidationData**
<p>

<details><summary>Partital Dependence Box Plots</summary>
<p>

```{r Model_Evaluation_Metrics_NumericVariables_Train_Box, echo=FALSE}
options(warn = -1)
if(!is.null(Train_ParDepBoxPlots) && length(Train_ParDepBoxPlots) > 0) {
  echarts4r::e_arrange(Train_ParDepBoxPlots)
} else {
  print('Train_ParDepBoxPlots is NULL and TestData is NULL')
}
options(warn = 1)
```

</details>
</p>



## <font size="5">Partial Partial Dependence Plots: Categorical-Features</font> 
<p>

<details><summary>Expand</summary>
<p>


### **TestData**
<p>

<details><summary>Partital Dependence Bar Plots</summary>
<p>

```{r Model_Evaluation_Metrics_CategoricalVariables, echo=FALSE}
options(warn = -1)
if(!is.null(Test_ParDepCatPlots) && length(Test_ParDepCatPlots) > 0) {
  echarts4r::e_arrange(Test_ParDepCatPlots)
} else {
  print('Test_ParDepCatPlots is NULL and TestData is NULL')
}
options(warn = 1)
```

</details>
</p>


### **TrainData** + **ValidationData**
<p>

<details><summary>Partital Dependence Bar Plots</summary>
<p>

```{r Model_Evaluation_Metrics_CategoricalVariables_Train, echo=FALSE}
options(warn = -1)
if(!is.null(Train_ParDepCatPlots) && length(Train_ParDepCatPlots) > 0) {
  echarts4r::e_arrange(Train_ParDepCatPlots)
} else {
  print('Train_ParDepCatPlots is NULL and TrainData is NULL')
}
options(warn = 1)
```

</details>
</p>


</details>
</p>



</details>
</p>




# <font size="6">Model MetaData</font>
<p>

<details><summary>Expand</summary>
<p>



## <font size="5">Parameters and Settings</font> 

<details><summary>Model Parameters</summary>
<p>

```{r Model_MetaData_Parameters, echo=FALSE}
if(!is.null(ArgsList)) {
  for(nam in names(ArgsList)) print(paste0(nam, ": ", ArgsList[[nam]]))
} else {
  txt <- paste0(ModelID, "_ArgsList.Rdata")
  print(paste0('ArgsList is NULL'))
}
```


## <font size="5">Grid Tuning Metrics</font>

<details><summary>Grid Tuning Metrics</summary>
<p>

```{r Model_MetaData_GridMetrics, echo=FALSE}
if(!is.null(GridMetrics)) {
  reactable::reactable(
    width = 1075,
    data = GridMetrics[order(-MetricValue)],
    compact = TRUE,
    defaultPageSize = 10,
    wrap = FALSE,
    filterable = TRUE,
    fullWidth = TRUE,
    highlight = TRUE,
    pagination = TRUE,
    resizable = TRUE,
    searchable = TRUE,
    selection = "multiple",
    showPagination = TRUE,
    showSortable = TRUE,
    showSortIcon = TRUE,
    sortable = TRUE,
    striped = TRUE,
    theme = reactable::reactableTheme(
      color = 'black',
      backgroundColor = "#4f4f4f26",
      borderColor = "#dfe2e5",
      stripedColor = "#4f4f4f8f",
      highlightColor = "#8989898f",
      cellPadding = "8px 12px",
      style = list(
        fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif"
      ),
      searchInputStyle = list(width = "100%")
    )
  )
  
} else {
  print("GridTuning was not conducted")
}
```

</details>
</p>



</details>
</p>



```{js, echo=FALSE}
setTimeout(function() {
  var codes = document.querySelectorAll('.dataTables_wrapper');
  var code, i, d, s, p;
  for (i = 0; i < codes.length; i++) {
    code = codes[i];
    p = code.parentNode;
    d = document.createElement('details');
    s = document.createElement('summary');
    s.innerText = 'Details';
    // <details><summary>Details</summary></details>
    d.appendChild(s);
    // move the code into <details>
    p.replaceChild(d, code);
    d.appendChild(code);
  }
});
```
