---
title: "Target Analysis Report"
author: "Provided by AutoQuant"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  prettydoc::html_pretty:
    theme: cayman
    toc: yes
    toc_depth: 2
    fig_caption: yes
    number_sections: no
classoption: landscape
params:
  artifacts: NULL
  DataName: "Target Analysis  Data"
  Theme: "dark"
---

```{css, echo=FALSE}
@import url('https://fonts.googleapis.com/css2?family=Yusei+Magic&display=swap');

:root{
  /* Core dark palette */
  --bg0: #070A14;
  --bg1: #0B1030;
  --bg2: #10183D;

  --panel: rgba(16, 24, 61, 0.72);
  --panel2: rgba(10, 14, 32, 0.72);

  --text: #E7ECFF;
  --muted: rgba(231, 236, 255, 0.72);

  --link: #9EC5FF;
  --linkHover: #CFE3FF;

  /* Neon glow */
  --glow: rgba(72, 145, 255, 0.40);
  --glowStrong: rgba(72, 145, 255, 0.70);
  --border: rgba(140, 170, 255, 0.30);

  --codeBg: rgba(255,255,255,0.06);
  --codeBorder: rgba(140, 170, 255, 0.22);

  --preBg: rgba(0,0,0,0.25);
  --preBorder: rgba(140, 170, 255, 0.28);

  --tableHeadBg: rgba(72, 145, 255, 0.22);
  --tableOdd: rgba(255,255,255,0.04);
  --tableEven: rgba(255,255,255,0.02);
  --tableGrid: rgba(231, 236, 255, 0.12);
}

* { box-sizing: border-box; }

html, body { height: 100%; }

body {
  padding: 0;
  margin: 0;
  font-family: "Open Sans", "Helvetica Neue", Helvetica, Arial, sans-serif;
  font-size: 16px;
  line-height: 1.55;
  color: #E7ECFF;

  background:
    radial-gradient(1200px 600px at 20% -10%, rgba(72,145,255,0.20), transparent 60%),
    radial-gradient(900px 500px at 90% 10%, rgba(168,80,255,0.14), transparent 55%),
    linear-gradient(180deg, #0B1030, #070A14);

  background-repeat: no-repeat;
  background-attachment: fixed;
  background-size: cover;
}

a {
  color: var(--link);
  text-decoration: none;
}
a:hover {
  color: var(--linkHover);
  text-decoration: underline;
}

/* Header */
.page-header {
  color: var(--text);
  text-align: center;
  background-color: #05071A;
  background-image: radial-gradient(900px 400px at 50% 0%, rgba(72,145,255,0.18), transparent 70%),
                    linear-gradient(120deg, #05071A, #0E1B4E);
  padding: 1.5rem 2rem;
  border-bottom: 1px solid rgba(140,170,255,0.15);
}
.page-header :last-child { margin-bottom: 0.5rem; }
@media screen and (max-width: 42em) {
  .page-header { padding: 1rem 1rem; }
}

.project-name {
  margin-top: 0;
  margin-bottom: 0.1rem;
  font-size: 2rem;
}
@media screen and (max-width: 42em) {
  .project-name { font-size: 1.75rem; }
}

.project-tagline {
  margin-bottom: 2rem;
  font-weight: normal;
  opacity: 0.8;
  font-size: 1.5rem;
  color: var(--muted);
}
@media screen and (max-width: 42em) {
  .project-tagline { font-size: 1.2rem; }
}

.project-author, .project-date {
  font-weight: normal;
  opacity: 0.85;
  font-size: 1.2rem;
  color: var(--muted);
}
@media screen and (max-width: 42em) {
  .project-author, .project-date { font-size: 1rem; }
}

/* Main layout */
.main-content, .toc {
  max-width: 95%;
  padding: 2rem 4rem;
  margin: 0 auto;
  font-size: 1.06rem;
}

@media screen and (min-width: 42em) and (max-width: 64em) {
  .main-content, .toc { padding: 2rem; }
}
@media screen and (max-width: 42em) {
  .main-content, .toc {
    padding: 2rem 1rem;
    font-size: 1rem;
  }
}

.main-content :first-child { margin-top: 0; }
.main-content img { max-width: 100%; }

/* TOC */
.toc { padding-bottom: 0; }

.toc .toc-box {
  padding: 48px;
  background: linear-gradient(90deg, rgba(5,7,26,0.90), rgba(16,24,61,0.70));
  border: 1px solid rgba(140,170,255,0.20);
  border-radius: 44px;
  color: var(--text);
  box-shadow:
    0 10px 30px rgba(0,0,0,0.35),
    0 0 24px var(--glow);
  backdrop-filter: blur(10px);
}
.toc .toc-box .toc-title {
  margin: 0 0 0.5rem;
  text-align: center;
}
.toc .toc-box > ul { margin: 0; padding-left: 1.5rem; }

/* Headings */
.main-content h1,
.main-content h2,
.main-content h3,
.main-content h4,
.main-content h5,
.main-content h6 {
  margin-top: 2rem;
  margin-bottom: 1rem;
  font-weight: 700;
  letter-spacing: 0.2px;
  color: var(--text);
}

.main-content h1 { font-size: 2.0rem; }
.main-content h2 { font-size: 1.6rem; opacity: 0.95; }
.main-content h3 { font-size: 1.35rem; opacity: 0.92; }
.main-content h4 { font-size: 1.15rem; opacity: 0.90; }
.main-content h5 { font-size: 1.05rem; opacity: 0.88; }
.main-content h6 { font-size: 1.0rem; opacity: 0.86; }

/* Paragraphs */
.main-content p { margin-bottom: 1em; color: var(--text); }

/* Inline code */
.main-content code {
  padding: 2px 6px;
  font-family: Consolas, "Liberation Mono", Menlo, Courier, monospace;
  color: var(--text);
  background-color: var(--codeBg);
  border: 1px solid var(--codeBorder);
  border-radius: 0.45rem;
}

/* Code blocks */
.main-content pre {
  padding: 0.9rem 1rem;
  margin-top: 0;
  margin-bottom: 1rem;

  font: 0.98rem Consolas, "Liberation Mono", Menlo, Courier, monospace;
  color: var(--text);

  background-color: var(--preBg);
  border: 1px solid var(--preBorder);
  border-radius: 0.75rem;
  line-height: 1.45;
  overflow: auto;

  box-shadow:
    0 10px 24px rgba(0,0,0,0.35),
    0 0 18px rgba(72,145,255,0.16);
}
@media screen and (max-width: 42em) {
  .main-content pre { font-size: 0.9rem; }
}

.main-content pre > code {
  padding: 0;
  margin: 0;
  color: var(--text);
  word-break: normal;
  white-space: pre;
  background: transparent;
  border: 0;
}

/* Lists */
.main-content ul, .main-content ol { margin-top: 0; }

/* Blockquotes */
.main-content blockquote {
  padding: 0.25rem 1rem;
  margin-left: 0;
  color: var(--muted);
  border-left: 0.3rem solid rgba(72,145,255,0.45);
  background: rgba(255,255,255,0.03);
  border-radius: 0.6rem;
}
@media screen and (max-width: 42em) {
  .main-content blockquote { font-size: 1.05rem; }
}

/* HR */
.main-content hr {
  height: 1px;
  padding: 0;
  margin: 1.25rem 0;
  background-color: rgba(231,236,255,0.12);
  border: 0;
}

/* ============================
   DETAILS: glow box + hover glow
   ============================ */
.main-content details {
  margin: 1rem 0;
  padding: 0.85rem 1rem;
  border-radius: 0.95rem;

  background: linear-gradient(180deg, var(--panel), var(--panel2));
  border: 1px solid var(--border);

  box-shadow:
    0 10px 26px rgba(0,0,0,0.35),
    0 0 18px var(--glow);

  transition: transform 140ms ease, box-shadow 140ms ease, border-color 140ms ease;
  backdrop-filter: blur(10px);
}

.main-content details:hover {
  transform: translateY(-1px);
  border-color: rgba(140,170,255,0.55);
  box-shadow:
    0 14px 34px rgba(0,0,0,0.45),
    0 0 26px var(--glowStrong);
}

.main-content details[open] {
  border-color: rgba(140,170,255,0.60);
  box-shadow:
    0 14px 34px rgba(0,0,0,0.45),
    0 0 28px var(--glowStrong);
}

.main-content details > summary {
  cursor: pointer;
  user-select: none;
  font-weight: 700;
  color: var(--text);
  list-style: none;
  display: flex;
  align-items: center;
  gap: 10px;
}

.main-content details > summary::-webkit-details-marker { display: none; }

.main-content details > summary::before {
  content: "▸";
  display: inline-block;
  transform: translateY(-1px);
  opacity: 0.85;
  transition: transform 140ms ease;
}

.main-content details[open] > summary::before {
  transform: rotate(90deg) translateY(-1px);
}

/* Inner content spacing inside details */
.main-content details > *:not(summary) {
  margin-top: 0.85rem;
}

/* ============================
   TABLES (dark) + wrapper hooks
   ============================ */
.main-content table {
  width: 100%;
  overflow: auto;
  word-break: normal;
  word-break: keep-all;
  -webkit-overflow-scrolling: touch;
  border-collapse: collapse;
  border-spacing: 0;
  margin: 0.75rem 0;
  color: var(--text);
}

.main-content table th {
  font-weight: 800;
  background-color: var(--tableHeadBg);
  color: var(--text);
  border-bottom: 1px solid var(--tableGrid);
}

.main-content table th,
.main-content table td {
  padding: 0.55rem 0.85rem;
  border-bottom: 1px solid var(--tableGrid);
  text-align: left;
}

.main-content table tr:nth-child(odd) { background-color: var(--tableOdd); }
.main-content table tr:nth-child(even) { background-color: var(--tableEven); }

/* Wrapper that JS will create around tables */
.table-wrap {
  margin: 1rem 0 1.25rem;
  padding: 0.75rem 0.9rem;
  border-radius: 0.95rem;
  background: linear-gradient(180deg, var(--panel), var(--panel2));
  border: 1px solid rgba(140,170,255,0.22);
  box-shadow:
    0 10px 26px rgba(0,0,0,0.30),
    0 0 18px rgba(72,145,255,0.18);
}

.table-toolbar {
  display: flex;
  justify-content: flex-end;
  gap: 10px;
  margin-bottom: 0.6rem;
}

.table-btn {
  appearance: none;
  border: 1px solid rgba(140,170,255,0.40);
  background: rgba(72,145,255,0.14);
  color: var(--text);
  padding: 7px 10px;
  border-radius: 0.7rem;
  cursor: pointer;
  font-weight: 700;
  letter-spacing: 0.2px;
  transition: transform 120ms ease, box-shadow 120ms ease, border-color 120ms ease, background 120ms ease;
}

.table-btn:hover {
  transform: translateY(-1px);
  border-color: rgba(140,170,255,0.70);
  background: rgba(72,145,255,0.22);
  box-shadow: 0 0 18px rgba(72,145,255,0.35);
}

.table-btn:active {
  transform: translateY(0px);
}

/* Definition lists */
.main-content dl { padding: 0; }
.main-content dl dt {
  padding: 0;
  margin-top: 1rem;
  font-size: 1rem;
  font-weight: 800;
  color: var(--text);
}
.main-content dl dd {
  padding: 0;
  margin-bottom: 1rem;
  color: var(--muted);
}

/* Reactable: focus glow + small polish */
.reactable .rt-search input:focus,
.reactable .rt-filter input:focus,
.reactable select:focus {
  border-color: rgba(140,170,255,0.70) !important;
  box-shadow: 0 0 0 3px rgba(72,145,255,0.18), 0 0 18px rgba(72,145,255,0.30) !important;
}

/* Reactable: soften grid + round the whole widget */
.reactable {
  border-radius: 14px;
  overflow: hidden; /* keeps rounded corners clean */
}

/* Scrollbar polish (Chrome/Edge) */
.reactable ::-webkit-scrollbar { height: 10px; width: 10px; }
.reactable ::-webkit-scrollbar-track { background: rgba(0,0,0,0.15); border-radius: 999px; }
.reactable ::-webkit-scrollbar-thumb { background: rgba(140,170,255,0.25); border-radius: 999px; }
.reactable ::-webkit-scrollbar-thumb:hover { background: rgba(140,170,255,0.40); }

.reactable {
  position: relative;
  border-radius: 16px;
  overflow: hidden;
}

.reactable::before {
  content: "";
  position: absolute;
  inset: 0;
  border-radius: 16px;
  padding: 1px;
  background: linear-gradient(
    135deg,
    rgba(72,145,255,0.7),
    rgba(168,80,255,0.5),
    rgba(72,145,255,0.7)
  );
  -webkit-mask:
    linear-gradient(#000 0 0) content-box,
    linear-gradient(#000 0 0);
  -webkit-mask-composite: xor;
  mask-composite: exclude;
  pointer-events: none;
}
.reactable .rt-tbody .rt-tr:hover {
  background: rgba(72,145,255,0.12) !important;
  box-shadow: inset 0 0 18px rgba(72,145,255,0.18);
}
.reactable .rt-tr {
  transition: background 120ms ease, box-shadow 120ms ease;
}

.reactable .rt-pagination button {
  transition: all 120ms ease;
}

```

## <font size="5">Target Analysis Report Descriptions</font>

<details><summary>Expand</summary>
<p>

This report is designed to provide a focused, structured, and user-friendly target-variable analysis workflow for evaluating a dataset from a modeling-readiness perspective. The goal is to summarize target behavior, identify feature relationships with the target, surface target distribution issues, evaluate temporal stability, detect potential drift, and flag variables that may require additional review before modeling.

The outputs are intended to help users understand how candidate features relate to the target variable through numeric association statistics, categorical target-rate or target-mean summaries, feature-level lift diagnostics, target trend analysis, feature drift diagnostics, concept drift diagnostics, and risk flags for potential leakage, collider effects, or post-treatment variables. These diagnostics are intended to highlight modeling-relevant patterns that may affect feature selection, validation strategy, model interpretation, and production stability.

The report should be treated as a pre-modeling investigation tool rather than a final modeling decision engine. Strong target associations, extreme categorical separation, drift signals, suspicious feature names, and leakage or collider-risk flags are heuristic indicators that require domain review. They can help identify promising predictors, unstable features, suspicious variables, and areas where additional validation is needed, but they do not prove causality, leakage, model suitability, or business relevance on their own.


</details>
</p>

# <font size="5">Describe Data</font>

<details><summary>Expand</summary>
<p>

```{r Model_Evaluation_Metrics, echo=FALSE}
if(!is.null(Describe_Data)) {
  eval(Describe_Data)
}
```

</details>
</p>





# <font size="5">Target Distribution Table</font>

<details><summary>Expand</summary>
<p>

```{r Target_Distribution, echo=FALSE}
if (exists("Target_Distribution")) {
  Target_Distribution
} else {
  print("Target distribution table was not created.")
}
```

</p>
</details>


# <font size="5">Target Distribution Plot</font>

<details><summary>Expand</summary>
<p>

```{r TargetDistributionPlot, echo=FALSE}
if (exists("TargetDistributionPlot") && !is.null(TargetDistributionPlot)) {
  TargetDistributionPlot
} else if (exists("TargetPlotList") && "Target Distribution" %in% names(TargetPlotList)) {
  TargetPlotList[["Target Distribution"]]
} else {
  print("Target distribution plot was not generated.")
}
```

</p>
</details>


# <font size="5">Target Association Plots</font>

<details><summary>Expand</summary>
<p>

```{r TargetAssociationPlotList, echo=FALSE}
if (exists("TargetAssociationPlotList") && length(TargetAssociationPlotList) > 0L) {
  AutoPlots::display_plots_grid(TargetAssociationPlotList, cols = 1)
} else {
  print("No target association plots were generated.")
}
```

</p>
</details>


# <font size="5">Target Overall Trend Plots</font>

<details><summary>Expand</summary>
<p>

```{r TargetTrendPlotList, echo=FALSE}
if (exists("TargetTrendPlotList") && length(TargetTrendPlotList) > 0L) {
  AutoPlots::display_plots_grid(TargetTrendPlotList, cols = 2)
} else {
  print("No target trend plots were generated. Provide a valid TargetVar and TrendDateVar to enable this section.")
}
```

</p>
</details>


# <font size="5">Target Grouped Trend Plots</font>

<details><summary>Expand</summary>
<p>

```{r TargetGroupedTrendPlotList, echo=FALSE}
if (exists("TargetGroupedTrendPlotList") && length(TargetGroupedTrendPlotList) > 0L) {
  AutoPlots::display_plots_grid(TargetGroupedTrendPlotList, cols = 2)
} else {
  print("No grouped target trend plots were generated. Provide a valid TargetVar, TrendDateVar, and TrendGroupVar to enable this section.")
}
```

</p>
</details>


# <font size="5">Target Drift Plots</font>

<details><summary>Expand</summary>
<p>

```{r TargetDriftPlotList, echo=FALSE}
if (exists("TargetDriftPlotList") && length(TargetDriftPlotList) > 0L) {
  AutoPlots::display_plots_grid(TargetDriftPlotList, cols = 1)
} else {
  print("No target drift plots were generated. Provide a valid TrendDateVar to enable drift diagnostics.")
}
```

</p>
</details>


# <font size="5">Target Risk Flag Plots</font>

<details><summary>Expand</summary>
<p>

```{r TargetRiskPlotList, echo=FALSE}
if (exists("TargetRiskPlotList") && length(TargetRiskPlotList) > 0L) {
  AutoPlots::display_plots_grid(TargetRiskPlotList, cols = 1)
} else {
  print("No target risk flag plots were generated.")
}
```

</p>
</details>


# <font size="5">All Target Plots</font>

<details><summary>Expand</summary>
<p>

```{r TargetPlotList, echo=FALSE}
if (exists("TargetPlotList") && length(TargetPlotList) > 0L) {
  AutoPlots::display_plots_grid(TargetPlotList, cols = 1)
} else {
  print("No target-oriented plots were generated.")
}
```

</p>
</details>


# <font size="5">Numeric Feature Association With Target</font>

<details><summary>Expand</summary>
<p>

```{r Target_Numeric_Association, echo=FALSE}
if (exists("Target_Numeric_Association")) {
  Target_Numeric_Association
} else {
  print("Numeric feature association table was not created.")
}
```

</p>
</details>


# <font size="5">Categorical Feature Association With Target</font>

<details><summary>Expand</summary>
<p>

```{r Target_Categorical_Association, echo=FALSE}
if (exists("Target_Categorical_Association")) {
  Target_Categorical_Association
} else {
  print("Categorical feature association table was not created.")
}
```

</p>
</details>


# <font size="5">Categorical Level Association With Target</font>

<details><summary>Expand</summary>
<p>

```{r Target_Categorical_Level_Association, echo=FALSE}
if (exists("Target_Categorical_Level_Association")) {
  Target_Categorical_Level_Association
} else {
  print("Categorical level association table was not created.")
}
```

</p>
</details>


# <font size="5">Target Trend Statistics</font>

<details><summary>Expand</summary>
<p>

```{r TargetTrendStats, echo=FALSE}
if (exists("TargetTrendStats") && nrow(TargetTrendStats) > 0L) {
  reactable::reactable(
    TargetTrendStats,
    compact = TRUE,
    defaultPageSize = 25,
    pageSizeOptions = c(10, 25, 50, 100),
    wrap = FALSE,
    filterable = TRUE,
    searchable = TRUE,
    fullWidth = TRUE,
    highlight = TRUE,
    pagination = TRUE,
    resizable = TRUE,
    sortable = TRUE,
    striped = FALSE,
    rowStyle = if (exists("target_dark_row_style")) target_dark_row_style else NULL,
    defaultColDef = reactable::colDef(
      headerStyle = if (exists("target_default_header_style")) target_default_header_style else NULL,
      style = if (exists("target_dark_cell_style")) target_dark_cell_style else NULL
    ),
    theme = if (exists("target_theme")) target_theme else reactable::reactableTheme()
  )
} else {
  print("Target trend statistics were not created.")
}
```

</p>
</details>


# <font size="5">Target Grouped Trend Statistics</font>

<details><summary>Expand</summary>
<p>

```{r TargetGroupedTrendStats, echo=FALSE}
if (exists("TargetGroupedTrendStats") && nrow(TargetGroupedTrendStats) > 0L) {
  reactable::reactable(
    TargetGroupedTrendStats,
    compact = TRUE,
    defaultPageSize = 25,
    pageSizeOptions = c(10, 25, 50, 100),
    wrap = FALSE,
    filterable = TRUE,
    searchable = TRUE,
    fullWidth = TRUE,
    highlight = TRUE,
    pagination = TRUE,
    resizable = TRUE,
    sortable = TRUE,
    striped = FALSE,
    rowStyle = if (exists("target_dark_row_style")) target_dark_row_style else NULL,
    defaultColDef = reactable::colDef(
      headerStyle = if (exists("target_default_header_style")) target_default_header_style else NULL,
      style = if (exists("target_dark_cell_style")) target_dark_cell_style else NULL
    ),
    theme = if (exists("target_theme")) target_theme else reactable::reactableTheme()
  )
} else {
  print("Grouped target trend statistics were not created.")
}
```

</p>
</details>


# <font size="5">Feature Drift Diagnostics</font>

<details><summary>Expand</summary>
<p>

```{r Target_Feature_Drift, echo=FALSE}
if (exists("Target_Feature_Drift")) {
  Target_Feature_Drift
} else {
  print("Feature drift diagnostics were not created.")
}
```

</p>
</details>


# <font size="5">Concept Drift Diagnostics</font>

<details><summary>Expand</summary>
<p>

```{r Target_Concept_Drift, echo=FALSE}
if (exists("Target_Concept_Drift")) {
  Target_Concept_Drift
} else {
  print("Concept drift diagnostics were not created.")
}
```

</p>
</details>


# <font size="5">Potential Leakage / Collider Risk Flags</font>

<details><summary>Expand</summary>
<p>

```{r Target_Risk_Flags, echo=FALSE}
if (exists("Target_Risk_Flags")) {
  Target_Risk_Flags
} else {
  print("Target risk flags were not created.")
}
```

</p>
</details>




```{js, echo=FALSE}
setTimeout(function() {
  var codes = document.querySelectorAll('.dataTables_wrapper');
  var code, i, d, s, p;
  for (i = 0; i < codes.length; i++) {
    code = codes[i];
    p = code.parentNode;
    d = document.createElement('details');
    s = document.createElement('summary');
    s.innerText = 'Details';
    // <details><summary>Details</summary></details>
    d.appendChild(s);
    // move the code into <details>
    p.replaceChild(d, code);
    d.appendChild(code);
  }
});
```
