---
title: "Target Analysis Report"
author: "Provided by AutoQuant"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  prettydoc::html_pretty:
    theme: cayman
    toc: yes
    toc_depth: 2
    fig_caption: yes
    number_sections: no
classoption: landscape
params:
  artifacts: NULL
  DataName: "Modeling Data"
  Theme: "dark"
---

```{css, echo=FALSE}
@import url('https://fonts.googleapis.com/css2?family=Yusei+Magic&display=swap');

:root{
  /* Core dark palette */
  --bg0: #070A14;
  --bg1: #0B1030;
  --bg2: #10183D;

  --panel: rgba(16, 24, 61, 0.72);
  --panel2: rgba(10, 14, 32, 0.72);

  --text: #E7ECFF;
  --muted: rgba(231, 236, 255, 0.72);

  --link: #9EC5FF;
  --linkHover: #CFE3FF;

  /* Neon glow */
  --glow: rgba(72, 145, 255, 0.40);
  --glowStrong: rgba(72, 145, 255, 0.70);
  --border: rgba(140, 170, 255, 0.30);

  --codeBg: rgba(255,255,255,0.06);
  --codeBorder: rgba(140, 170, 255, 0.22);

  --preBg: rgba(0,0,0,0.25);
  --preBorder: rgba(140, 170, 255, 0.28);

  --tableHeadBg: rgba(72, 145, 255, 0.22);
  --tableOdd: rgba(255,255,255,0.04);
  --tableEven: rgba(255,255,255,0.02);
  --tableGrid: rgba(231, 236, 255, 0.12);
}

* { box-sizing: border-box; }

html, body { height: 100%; }

body {
  padding: 0;
  margin: 0;
  font-family: "Open Sans", "Helvetica Neue", Helvetica, Arial, sans-serif;
  font-size: 16px;
  line-height: 1.55;
  color: #E7ECFF;

  background:
    radial-gradient(1200px 600px at 20% -10%, rgba(72,145,255,0.20), transparent 60%),
    radial-gradient(900px 500px at 90% 10%, rgba(168,80,255,0.14), transparent 55%),
    linear-gradient(180deg, #0B1030, #070A14);

  background-repeat: no-repeat;
  background-attachment: fixed;
  background-size: cover;
}

a {
  color: var(--link);
  text-decoration: none;
}
a:hover {
  color: var(--linkHover);
  text-decoration: underline;
}

/* Header */
.page-header {
  color: var(--text);
  text-align: center;
  background-color: #05071A;
  background-image: radial-gradient(900px 400px at 50% 0%, rgba(72,145,255,0.18), transparent 70%),
                    linear-gradient(120deg, #05071A, #0E1B4E);
  padding: 1.5rem 2rem;
  border-bottom: 1px solid rgba(140,170,255,0.15);
}
.page-header :last-child { margin-bottom: 0.5rem; }
@media screen and (max-width: 42em) {
  .page-header { padding: 1rem 1rem; }
}

.project-name {
  margin-top: 0;
  margin-bottom: 0.1rem;
  font-size: 2rem;
}
@media screen and (max-width: 42em) {
  .project-name { font-size: 1.75rem; }
}

.project-tagline {
  margin-bottom: 2rem;
  font-weight: normal;
  opacity: 0.8;
  font-size: 1.5rem;
  color: var(--muted);
}
@media screen and (max-width: 42em) {
  .project-tagline { font-size: 1.2rem; }
}

.project-author, .project-date {
  font-weight: normal;
  opacity: 0.85;
  font-size: 1.2rem;
  color: var(--muted);
}
@media screen and (max-width: 42em) {
  .project-author, .project-date { font-size: 1rem; }
}

/* Main layout */
.main-content, .toc {
  max-width: 95%;
  padding: 2rem 4rem;
  margin: 0 auto;
  font-size: 1.06rem;
}

@media screen and (min-width: 42em) and (max-width: 64em) {
  .main-content, .toc { padding: 2rem; }
}
@media screen and (max-width: 42em) {
  .main-content, .toc {
    padding: 2rem 1rem;
    font-size: 1rem;
  }
}

.main-content :first-child { margin-top: 0; }
.main-content img { max-width: 100%; }

/* TOC */
.toc { padding-bottom: 0; }

.toc .toc-box {
  padding: 48px;
  background: linear-gradient(90deg, rgba(5,7,26,0.90), rgba(16,24,61,0.70));
  border: 1px solid rgba(140,170,255,0.20);
  border-radius: 44px;
  color: var(--text);
  box-shadow:
    0 10px 30px rgba(0,0,0,0.35),
    0 0 24px var(--glow);
  backdrop-filter: blur(10px);
}
.toc .toc-box .toc-title {
  margin: 0 0 0.5rem;
  text-align: center;
}
.toc .toc-box > ul { margin: 0; padding-left: 1.5rem; }

/* Headings */
.main-content h1,
.main-content h2,
.main-content h3,
.main-content h4,
.main-content h5,
.main-content h6 {
  margin-top: 2rem;
  margin-bottom: 1rem;
  font-weight: 700;
  letter-spacing: 0.2px;
  color: var(--text);
}

.main-content h1 { font-size: 2.0rem; }
.main-content h2 { font-size: 1.6rem; opacity: 0.95; }
.main-content h3 { font-size: 1.35rem; opacity: 0.92; }
.main-content h4 { font-size: 1.15rem; opacity: 0.90; }
.main-content h5 { font-size: 1.05rem; opacity: 0.88; }
.main-content h6 { font-size: 1.0rem; opacity: 0.86; }

/* Paragraphs */
.main-content p { margin-bottom: 1em; color: var(--text); }

/* Inline code */
.main-content code {
  padding: 2px 6px;
  font-family: Consolas, "Liberation Mono", Menlo, Courier, monospace;
  color: var(--text);
  background-color: var(--codeBg);
  border: 1px solid var(--codeBorder);
  border-radius: 0.45rem;
}

/* Code blocks */
.main-content pre {
  padding: 0.9rem 1rem;
  margin-top: 0;
  margin-bottom: 1rem;

  font: 0.98rem Consolas, "Liberation Mono", Menlo, Courier, monospace;
  color: var(--text);

  background-color: var(--preBg);
  border: 1px solid var(--preBorder);
  border-radius: 0.75rem;
  line-height: 1.45;
  overflow: auto;

  box-shadow:
    0 10px 24px rgba(0,0,0,0.35),
    0 0 18px rgba(72,145,255,0.16);
}
@media screen and (max-width: 42em) {
  .main-content pre { font-size: 0.9rem; }
}

.main-content pre > code {
  padding: 0;
  margin: 0;
  color: var(--text);
  word-break: normal;
  white-space: pre;
  background: transparent;
  border: 0;
}

/* Lists */
.main-content ul, .main-content ol { margin-top: 0; }

/* Blockquotes */
.main-content blockquote {
  padding: 0.25rem 1rem;
  margin-left: 0;
  color: var(--muted);
  border-left: 0.3rem solid rgba(72,145,255,0.45);
  background: rgba(255,255,255,0.03);
  border-radius: 0.6rem;
}
@media screen and (max-width: 42em) {
  .main-content blockquote { font-size: 1.05rem; }
}

/* HR */
.main-content hr {
  height: 1px;
  padding: 0;
  margin: 1.25rem 0;
  background-color: rgba(231,236,255,0.12);
  border: 0;
}

/* ============================
   DETAILS: glow box + hover glow
   ============================ */
.main-content details {
  margin: 1rem 0;
  padding: 0.85rem 1rem;
  border-radius: 0.95rem;

  background: linear-gradient(180deg, var(--panel), var(--panel2));
  border: 1px solid var(--border);

  box-shadow:
    0 10px 26px rgba(0,0,0,0.35),
    0 0 18px var(--glow);

  transition: transform 140ms ease, box-shadow 140ms ease, border-color 140ms ease;
  backdrop-filter: blur(10px);
}

.main-content details:hover {
  transform: translateY(-1px);
  border-color: rgba(140,170,255,0.55);
  box-shadow:
    0 14px 34px rgba(0,0,0,0.45),
    0 0 26px var(--glowStrong);
}

.main-content details[open] {
  border-color: rgba(140,170,255,0.60);
  box-shadow:
    0 14px 34px rgba(0,0,0,0.45),
    0 0 28px var(--glowStrong);
}

.main-content details > summary {
  cursor: pointer;
  user-select: none;
  font-weight: 700;
  color: var(--text);
  list-style: none;
  display: flex;
  align-items: center;
  gap: 10px;
}

.main-content details > summary::-webkit-details-marker { display: none; }

.main-content details > summary::before {
  content: "▸";
  display: inline-block;
  transform: translateY(-1px);
  opacity: 0.85;
  transition: transform 140ms ease;
}

.main-content details[open] > summary::before {
  transform: rotate(90deg) translateY(-1px);
}

/* Inner content spacing inside details */
.main-content details > *:not(summary) {
  margin-top: 0.85rem;
}

/* ============================
   TABLES (dark) + wrapper hooks
   ============================ */
.main-content table {
  width: 100%;
  overflow: auto;
  word-break: normal;
  word-break: keep-all;
  -webkit-overflow-scrolling: touch;
  border-collapse: collapse;
  border-spacing: 0;
  margin: 0.75rem 0;
  color: var(--text);
}

.main-content table th {
  font-weight: 800;
  background-color: var(--tableHeadBg);
  color: var(--text);
  border-bottom: 1px solid var(--tableGrid);
}

.main-content table th,
.main-content table td {
  padding: 0.55rem 0.85rem;
  border-bottom: 1px solid var(--tableGrid);
  text-align: left;
}

.main-content table tr:nth-child(odd) { background-color: var(--tableOdd); }
.main-content table tr:nth-child(even) { background-color: var(--tableEven); }

/* Wrapper that JS will create around tables */
.table-wrap {
  margin: 1rem 0 1.25rem;
  padding: 0.75rem 0.9rem;
  border-radius: 0.95rem;
  background: linear-gradient(180deg, var(--panel), var(--panel2));
  border: 1px solid rgba(140,170,255,0.22);
  box-shadow:
    0 10px 26px rgba(0,0,0,0.30),
    0 0 18px rgba(72,145,255,0.18);
}

.table-toolbar {
  display: flex;
  justify-content: flex-end;
  gap: 10px;
  margin-bottom: 0.6rem;
}

.table-btn {
  appearance: none;
  border: 1px solid rgba(140,170,255,0.40);
  background: rgba(72,145,255,0.14);
  color: var(--text);
  padding: 7px 10px;
  border-radius: 0.7rem;
  cursor: pointer;
  font-weight: 700;
  letter-spacing: 0.2px;
  transition: transform 120ms ease, box-shadow 120ms ease, border-color 120ms ease, background 120ms ease;
}

.table-btn:hover {
  transform: translateY(-1px);
  border-color: rgba(140,170,255,0.70);
  background: rgba(72,145,255,0.22);
  box-shadow: 0 0 18px rgba(72,145,255,0.35);
}

.table-btn:active {
  transform: translateY(0px);
}

/* Definition lists */
.main-content dl { padding: 0; }
.main-content dl dt {
  padding: 0;
  margin-top: 1rem;
  font-size: 1rem;
  font-weight: 800;
  color: var(--text);
}
.main-content dl dd {
  padding: 0;
  margin-bottom: 1rem;
  color: var(--muted);
}

/* Reactable: focus glow + small polish */
.reactable .rt-search input:focus,
.reactable .rt-filter input:focus,
.reactable select:focus {
  border-color: rgba(140,170,255,0.70) !important;
  box-shadow: 0 0 0 3px rgba(72,145,255,0.18), 0 0 18px rgba(72,145,255,0.30) !important;
}

/* Reactable: soften grid + round the whole widget */
.reactable {
  border-radius: 14px;
  overflow: hidden; /* keeps rounded corners clean */
}

/* Scrollbar polish (Chrome/Edge) */
.reactable ::-webkit-scrollbar { height: 10px; width: 10px; }
.reactable ::-webkit-scrollbar-track { background: rgba(0,0,0,0.15); border-radius: 999px; }
.reactable ::-webkit-scrollbar-thumb { background: rgba(140,170,255,0.25); border-radius: 999px; }
.reactable ::-webkit-scrollbar-thumb:hover { background: rgba(140,170,255,0.40); }

.reactable {
  position: relative;
  border-radius: 16px;
  overflow: hidden;
}

.reactable::before {
  content: "";
  position: absolute;
  inset: 0;
  border-radius: 16px;
  padding: 1px;
  background: linear-gradient(
    135deg,
    rgba(72,145,255,0.7),
    rgba(168,80,255,0.5),
    rgba(72,145,255,0.7)
  );
  -webkit-mask:
    linear-gradient(#000 0 0) content-box,
    linear-gradient(#000 0 0);
  -webkit-mask-composite: xor;
  mask-composite: exclude;
  pointer-events: none;
}
.reactable .rt-tbody .rt-tr:hover {
  background: rgba(72,145,255,0.12) !important;
  box-shadow: inset 0 0 18px rgba(72,145,255,0.18);
}
.reactable .rt-tr {
  transition: background 120ms ease, box-shadow 120ms ease;
}

.reactable .rt-pagination button {
  transition: all 120ms ease;
}

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)

artifacts <- params$artifacts
DataName <- params$DataName
Theme <- params$Theme

if (is.null(artifacts)) {
  stop("`params$artifacts` is NULL. Pass an artifact object into the report renderer.")
}
```

## <font size="5">Target Analysis Report Descriptions</font>

<details><summary>Expand</summary>
<p>

This report is designed to provide a comprehensive model-readiness assessment by exhaustively evaluating the target variable, candidate predictor variables, temporal characteristics, and potential production considerations before any model is trained. The objective is to characterize the modeling problem as completely as possible so that feature engineering, model development, validation, deployment, and long-term monitoring decisions can be made using evidence rather than intuition.

The report examines the target variable from multiple perspectives, including target quality, target distribution, target associations, temporal behavior, feature drift, concept drift, and potential risks such as data leakage, collider variables, post-treatment variables, proxy variables, and production instability. Numeric, categorical, and calendar variables are evaluated independently to identify nonlinear relationships, categorical separation, encoding opportunities, feature engineering candidates, seasonality, trend behavior, and other modeling-relevant characteristics that may influence both predictive performance and explanatory validity.

Rather than recommending a single modeling algorithm, the report focuses on generating exhaustive evidence that supports informed modeling decisions. The diagnostics are intended to identify variables that are well suited for explanatory modeling, variables that may be more appropriate for predictive modeling, variables that require additional engineering or validation, and variables that should be reviewed or excluded due to instability or potential bias. The report also provides guidance for feature engineering opportunities, validation strategy considerations, production monitoring priorities, and expected retraining considerations.

The report should be viewed as a model design and readiness assessment rather than a model evaluation report. The diagnostics are heuristic and evidence-based rather than definitive. Strong target associations, nonlinear relationships, categorical separation, drift signals, suspicious variable names, and other risk indicators do not prove causality, leakage, instability, or production risk on their own. Instead, they provide a structured framework for prioritizing further investigation and supporting statistically sound, interpretable, and production-ready modeling workflows.

The long-term philosophy of this report is exhaustive evidence generation. Every statistic, visualization, diagnostic, and recommendation is intended to contribute an independent piece of evidence describing the modeling problem. These artifacts can be consumed directly by analysts, incorporated into interactive reports and dashboards, or synthesized by large language models to produce comprehensive modeling narratives, feature engineering recommendations, model design guidance, and production monitoring strategies.


</details>
</p>


## <font size="5">Describe Data</font>
<details><summary>Expand</summary>
<p>

```{r Describe_Data, echo=FALSE}
if (!is.null(artifacts$widgets$describe_data)) {
artifacts$widgets$describe_data
} else {
  cat("Describe Data was not created.")
}
```

</details>
</p>


## <font size="5">Target QA</font>

<details><summary>Expand</summary>
<p>

```{r Target_QA, echo=FALSE}
if (!is.null(artifacts$widgets$target_qa)) {
  artifacts$widgets$target_qa
} else {
  cat("Target QA was not created.")
}
```

</details>
</p>


## <font size="5">Target Distribution</font>

<details><summary>Expand</summary>
<p>

```{r Target_Distribution, echo=FALSE}
if (!is.null(artifacts$widgets$target_distribution)) {
  artifacts$widgets$target_distribution
} else {
  cat("Target Distribution was not created.")
}
```

</details>
</p>


## <font size="5">Numeric Association</font>

<details><summary>Expand</summary>
<p>

```{r Numeric_Association, echo=FALSE}
if (!is.null(artifacts$widgets$numeric_association)) {
  artifacts$widgets$numeric_association
} else {
  cat("Numeric Association was not created.")
}
```

</details>
</p>


## <font size="5">Categorical Association</font>

<details><summary>Expand</summary>
<p>

```{r Categorical_Association, echo=FALSE}
if (!is.null(artifacts$widgets$categorical_association)) {
  artifacts$widgets$categorical_association
} else {
  cat("Categorical Association was not created.")
}
```

</details>
</p>


## <font size="5">Categorical Level Association</font>

<details><summary>Expand</summary>
<p>

```{r Categorical_Level_Association, echo=FALSE}
if (!is.null(artifacts$widgets$categorical_level_association)) {
  artifacts$widgets$categorical_level_association
} else {
  cat("Categorical Level Association was not created.")
}
```

</details>
</p>


## <font size="5">Feature Drift</font>

<details><summary>Expand</summary>
<p>

```{r Feature_Drift, echo=FALSE}
if (!is.null(artifacts$widgets$feature_drift)) {
  artifacts$widgets$feature_drift
} else {
  cat("Feature Drift was not created.")
}
```

</details>
</p>


## <font size="5">Concept Drift</font>

<details><summary>Expand</summary>
<p>

```{r Concept_Drift, echo=FALSE}
if (!is.null(artifacts$widgets$concept_drift)) {
  artifacts$widgets$concept_drift
} else {
  cat("Concept Drift was not created.")
}
```

</details>
</p>



## <font size="5">Risk Flags</font>

<details><summary>Expand</summary>
<p>

```{r Risk_Flags, echo=FALSE}
if (!is.null(artifacts$widgets$risk_flags)) {
  artifacts$widgets$risk_flags
} else {
  cat("Risk Flags was not created.")
}
```

</details>
</p>


## <font size="5">Target Suitability Assessment</font>

<details><summary>Expand</summary>
<p>

```{r Target_Suitability_Assessment, echo=FALSE}
if (!is.null(artifacts$widgets$target_suitability_assessment)) {
  artifacts$widgets$target_suitability_assessment
} else {
  cat("Target Suitability Assessment was not created.")
}
```

</details>
</p>


## <font size="5">Feature Risk Registry</font>

<details><summary>Expand</summary>
<p>

```{r Feature_Risk_Registry, echo=FALSE}
if (!is.null(artifacts$widgets$feature_risk_registry)) {
  artifacts$widgets$feature_risk_registry
} else {
  cat("Feature Risk Registry was not created.")
}
```

</details>
</p>


## <font size="5">Numeric Feature Diagnostics</font>

<details><summary>Expand</summary>
<p>

```{r Numeric_Feature_Diagnostics, echo=FALSE}
if (!is.null(artifacts$widgets$numeric_feature_diagnostics)) {
  artifacts$widgets$numeric_feature_diagnostics
} else {
  cat("Numeric Feature Diagnostics was not created.")
}
```

</details>
</p>


## <font size="5">Numeric Shape Diagnostics</font>

<details><summary>Expand</summary>
<p>

```{r Numeric_Shape_Diagnostics, echo=FALSE}
if (!is.null(artifacts$widgets$numeric_shape_diagnostics)) {
  artifacts$widgets$numeric_shape_diagnostics
} else {
  cat("Numeric Shape Diagnostics was not created.")
}
```

</details>
</p>


## <font size="5">Numeric Engineering Recommendations</font>

<details><summary>Expand</summary>
<p>

```{r Numeric_Engineering_Recommendations, echo=FALSE}
if (!is.null(artifacts$widgets$numeric_engineering_recommendations)) {
  artifacts$widgets$numeric_engineering_recommendations
} else {
  cat("Numeric Engineering Recommendations was not created.")
}
```

</details>
</p>


## <font size="5">Categorical Feature Diagnostics</font>

<details><summary>Expand</summary>
<p>

```{r Categorical_Feature_Diagnostics, echo=FALSE}
if (!is.null(artifacts$widgets$categorical_feature_diagnostics)) {
  artifacts$widgets$categorical_feature_diagnostics
} else {
  cat("Categorical Feature Diagnostics was not created.")
}
```

</details>
</p>


## <font size="5">Categorical Encoding Recommendations</font>

<details><summary>Expand</summary>
<p>

```{r Categorical_Encoding_Recommendations, echo=FALSE}
if (!is.null(artifacts$widgets$categorical_encoding_recommendations)) {
  artifacts$widgets$categorical_encoding_recommendations
} else {
  cat("Categorical Encoding Recommendations was not created.")
}
```

</details>
</p>


## <font size="5">Calendar Feature Diagnostics</font>

<details><summary>Expand</summary>
<p>

```{r Calendar_Feature_Diagnostics, echo=FALSE}
if (!is.null(artifacts$widgets$calendar_feature_diagnostics)) {
  artifacts$widgets$calendar_feature_diagnostics
} else {
  cat("Calendar Feature Diagnostics was not created.")
}
```

</details>
</p>


## <font size="5">Calendar Engineering Recommendations</font>

<details><summary>Expand</summary>
<p>

```{r Calendar_Engineering_Recommendations, echo=FALSE}
if (!is.null(artifacts$widgets$calendar_engineering_recommendations)) {
  artifacts$widgets$calendar_engineering_recommendations
} else {
  cat("Calendar Engineering Recommendations was not created.")
}
```

</details>
</p>


## <font size="5">Validation Recommendations</font>

<details><summary>Expand</summary>
<p>

```{r Validation_Recommendations, echo=FALSE}
if (!is.null(artifacts$widgets$validation_recommendations)) {
  artifacts$widgets$validation_recommendations
} else {
  cat("Validation Recommendations was not created.")
}
```

</details>
</p>


## <font size="5">Monitoring Recommendations</font>

<details><summary>Expand</summary>
<p>

```{r Monitoring_Recommendations, echo=FALSE}
if (!is.null(artifacts$widgets$monitoring_recommendations)) {
  artifacts$widgets$monitoring_recommendations
} else {
  cat("Monitoring Recommendations was not created.")
}
```

</details>
</p>


## <font size="5">Modeling Strategy Recommendations</font>

<details><summary>Expand</summary>
<p>

```{r Modeling_Strategy_Recommendations, echo=FALSE}
if (!is.null(artifacts$widgets$modeling_strategy_recommendations)) {
  artifacts$widgets$modeling_strategy_recommendations
} else {
  cat("Modeling Strategy Recommendations was not created.")
}
```

</details>
</p>


## <font size="5">Retraining Cadence Recommendation</font>

<details><summary>Expand</summary>
<p>

```{r Retraining_Cadence_Recommendation, echo=FALSE}
if (!is.null(artifacts$widgets$retraining_cadence_recommendation)) {
  artifacts$widgets$retraining_cadence_recommendation
} else {
  cat("Retraining Cadence Recommendation was not created.")
}
```

</details>
</p>


## <font size="5">Model Readiness Summary</font>

<details><summary>Expand</summary>
<p>

```{r Model_Readiness_Summary, echo=FALSE}
if (!is.null(artifacts$widgets$model_readiness_summary)) {
  artifacts$widgets$model_readiness_summary
} else {
  cat("Model Readiness Summary was not created.")
}
```

</details>
</p>


## <font size="5">Schema Issues</font>

<details><summary>Expand</summary>
<p>

```{r Schema_Issues, echo=FALSE}
if (!is.null(artifacts$widgets$schema_issues)) {
  artifacts$widgets$schema_issues
} else {
  cat("Schema Issues was not created.")
}
```

</details>
</p>




```{js, echo=FALSE}
setTimeout(function() {
  var codes = document.querySelectorAll('.dataTables_wrapper');
  var code, i, d, s, p;
  for (i = 0; i < codes.length; i++) {
    code = codes[i];
    p = code.parentNode;
    d = document.createElement('details');
    s = document.createElement('summary');
    s.innerText = 'Details';
    // <details><summary>Details</summary></details>
    d.appendChild(s);
    // move the code into <details>
    p.replaceChild(d, code);
    d.appendChild(code);
  }
});
```
