---
title: "Target Analysis Report"
author: "Provided by AutoQuant"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  prettydoc::html_pretty:
    theme: cayman
    toc: yes
    toc_depth: 2
    fig_caption: yes
    number_sections: no
classoption: landscape
---

```{css, echo=FALSE}
@import url('https://fonts.googleapis.com/css2?family=Yusei+Magic&display=swap');

:root{
  /* Core dark palette */
  --bg0: #070A14;
  --bg1: #0B1030;
  --bg2: #10183D;

  --panel: rgba(16, 24, 61, 0.72);
  --panel2: rgba(10, 14, 32, 0.72);

  --text: #E7ECFF;
  --muted: rgba(231, 236, 255, 0.72);

  --link: #9EC5FF;
  --linkHover: #CFE3FF;

  /* Neon glow */
  --glow: rgba(72, 145, 255, 0.40);
  --glowStrong: rgba(72, 145, 255, 0.70);
  --border: rgba(140, 170, 255, 0.30);

  --codeBg: rgba(255,255,255,0.06);
  --codeBorder: rgba(140, 170, 255, 0.22);

  --preBg: rgba(0,0,0,0.25);
  --preBorder: rgba(140, 170, 255, 0.28);

  --tableHeadBg: rgba(72, 145, 255, 0.22);
  --tableOdd: rgba(255,255,255,0.04);
  --tableEven: rgba(255,255,255,0.02);
  --tableGrid: rgba(231, 236, 255, 0.12);
}

* { box-sizing: border-box; }

html, body { height: 100%; }

body {
  padding: 0;
  margin: 0;
  font-family: "Open Sans", "Helvetica Neue", Helvetica, Arial, sans-serif;
  font-size: 16px;
  line-height: 1.55;
  color: #E7ECFF;

  background:
    radial-gradient(1200px 600px at 20% -10%, rgba(72,145,255,0.20), transparent 60%),
    radial-gradient(900px 500px at 90% 10%, rgba(168,80,255,0.14), transparent 55%),
    linear-gradient(180deg, #0B1030, #070A14);

  background-repeat: no-repeat;
  background-attachment: fixed;
  background-size: cover;
}

a {
  color: var(--link);
  text-decoration: none;
}
a:hover {
  color: var(--linkHover);
  text-decoration: underline;
}

/* Header */
.page-header {
  color: var(--text);
  text-align: center;
  background-color: #05071A;
  background-image: radial-gradient(900px 400px at 50% 0%, rgba(72,145,255,0.18), transparent 70%),
                    linear-gradient(120deg, #05071A, #0E1B4E);
  padding: 1.5rem 2rem;
  border-bottom: 1px solid rgba(140,170,255,0.15);
}
.page-header :last-child { margin-bottom: 0.5rem; }
@media screen and (max-width: 42em) {
  .page-header { padding: 1rem 1rem; }
}

.project-name {
  margin-top: 0;
  margin-bottom: 0.1rem;
  font-size: 2rem;
}
@media screen and (max-width: 42em) {
  .project-name { font-size: 1.75rem; }
}

.project-tagline {
  margin-bottom: 2rem;
  font-weight: normal;
  opacity: 0.8;
  font-size: 1.5rem;
  color: var(--muted);
}
@media screen and (max-width: 42em) {
  .project-tagline { font-size: 1.2rem; }
}

.project-author, .project-date {
  font-weight: normal;
  opacity: 0.85;
  font-size: 1.2rem;
  color: var(--muted);
}
@media screen and (max-width: 42em) {
  .project-author, .project-date { font-size: 1rem; }
}

/* Main layout */
.main-content, .toc {
  max-width: 95%;
  padding: 2rem 4rem;
  margin: 0 auto;
  font-size: 1.06rem;
}

@media screen and (min-width: 42em) and (max-width: 64em) {
  .main-content, .toc { padding: 2rem; }
}
@media screen and (max-width: 42em) {
  .main-content, .toc {
    padding: 2rem 1rem;
    font-size: 1rem;
  }
}

.main-content :first-child { margin-top: 0; }
.main-content img { max-width: 100%; }

/* TOC */
.toc { padding-bottom: 0; }

.toc .toc-box {
  padding: 48px;
  background: linear-gradient(90deg, rgba(5,7,26,0.90), rgba(16,24,61,0.70));
  border: 1px solid rgba(140,170,255,0.20);
  border-radius: 44px;
  color: var(--text);
  box-shadow:
    0 10px 30px rgba(0,0,0,0.35),
    0 0 24px var(--glow);
  backdrop-filter: blur(10px);
}
.toc .toc-box .toc-title {
  margin: 0 0 0.5rem;
  text-align: center;
}
.toc .toc-box > ul { margin: 0; padding-left: 1.5rem; }

/* Headings */
.main-content h1,
.main-content h2,
.main-content h3,
.main-content h4,
.main-content h5,
.main-content h6 {
  margin-top: 2rem;
  margin-bottom: 1rem;
  font-weight: 700;
  letter-spacing: 0.2px;
  color: var(--text);
}

.main-content h1 { font-size: 2.0rem; }
.main-content h2 { font-size: 1.6rem; opacity: 0.95; }
.main-content h3 { font-size: 1.35rem; opacity: 0.92; }
.main-content h4 { font-size: 1.15rem; opacity: 0.90; }
.main-content h5 { font-size: 1.05rem; opacity: 0.88; }
.main-content h6 { font-size: 1.0rem; opacity: 0.86; }

/* Paragraphs */
.main-content p { margin-bottom: 1em; color: var(--text); }

/* Inline code */
.main-content code {
  padding: 2px 6px;
  font-family: Consolas, "Liberation Mono", Menlo, Courier, monospace;
  color: var(--text);
  background-color: var(--codeBg);
  border: 1px solid var(--codeBorder);
  border-radius: 0.45rem;
}

/* Code blocks */
.main-content pre {
  padding: 0.9rem 1rem;
  margin-top: 0;
  margin-bottom: 1rem;

  font: 0.98rem Consolas, "Liberation Mono", Menlo, Courier, monospace;
  color: var(--text);

  background-color: var(--preBg);
  border: 1px solid var(--preBorder);
  border-radius: 0.75rem;
  line-height: 1.45;
  overflow: auto;

  box-shadow:
    0 10px 24px rgba(0,0,0,0.35),
    0 0 18px rgba(72,145,255,0.16);
}
@media screen and (max-width: 42em) {
  .main-content pre { font-size: 0.9rem; }
}

.main-content pre > code {
  padding: 0;
  margin: 0;
  color: var(--text);
  word-break: normal;
  white-space: pre;
  background: transparent;
  border: 0;
}

/* Lists */
.main-content ul, .main-content ol { margin-top: 0; }

/* Blockquotes */
.main-content blockquote {
  padding: 0.25rem 1rem;
  margin-left: 0;
  color: var(--muted);
  border-left: 0.3rem solid rgba(72,145,255,0.45);
  background: rgba(255,255,255,0.03);
  border-radius: 0.6rem;
}
@media screen and (max-width: 42em) {
  .main-content blockquote { font-size: 1.05rem; }
}

/* HR */
.main-content hr {
  height: 1px;
  padding: 0;
  margin: 1.25rem 0;
  background-color: rgba(231,236,255,0.12);
  border: 0;
}

/* ============================
   DETAILS: glow box + hover glow
   ============================ */
.main-content details {
  margin: 1rem 0;
  padding: 0.85rem 1rem;
  border-radius: 0.95rem;

  background: linear-gradient(180deg, var(--panel), var(--panel2));
  border: 1px solid var(--border);

  box-shadow:
    0 10px 26px rgba(0,0,0,0.35),
    0 0 18px var(--glow);

  transition: transform 140ms ease, box-shadow 140ms ease, border-color 140ms ease;
  backdrop-filter: blur(10px);
}

.main-content details:hover {
  transform: translateY(-1px);
  border-color: rgba(140,170,255,0.55);
  box-shadow:
    0 14px 34px rgba(0,0,0,0.45),
    0 0 26px var(--glowStrong);
}

.main-content details[open] {
  border-color: rgba(140,170,255,0.60);
  box-shadow:
    0 14px 34px rgba(0,0,0,0.45),
    0 0 28px var(--glowStrong);
}

.main-content details > summary {
  cursor: pointer;
  user-select: none;
  font-weight: 700;
  color: var(--text);
  list-style: none;
  display: flex;
  align-items: center;
  gap: 10px;
}

.main-content details > summary::-webkit-details-marker { display: none; }

.main-content details > summary::before {
  content: "▸";
  display: inline-block;
  transform: translateY(-1px);
  opacity: 0.85;
  transition: transform 140ms ease;
}

.main-content details[open] > summary::before {
  transform: rotate(90deg) translateY(-1px);
}

/* Inner content spacing inside details */
.main-content details > *:not(summary) {
  margin-top: 0.85rem;
}

/* ============================
   TABLES (dark) + wrapper hooks
   ============================ */
.main-content table {
  width: 100%;
  overflow: auto;
  word-break: normal;
  word-break: keep-all;
  -webkit-overflow-scrolling: touch;
  border-collapse: collapse;
  border-spacing: 0;
  margin: 0.75rem 0;
  color: var(--text);
}

.main-content table th {
  font-weight: 800;
  background-color: var(--tableHeadBg);
  color: var(--text);
  border-bottom: 1px solid var(--tableGrid);
}

.main-content table th,
.main-content table td {
  padding: 0.55rem 0.85rem;
  border-bottom: 1px solid var(--tableGrid);
  text-align: left;
}

.main-content table tr:nth-child(odd) { background-color: var(--tableOdd); }
.main-content table tr:nth-child(even) { background-color: var(--tableEven); }

/* Wrapper that JS will create around tables */
.table-wrap {
  margin: 1rem 0 1.25rem;
  padding: 0.75rem 0.9rem;
  border-radius: 0.95rem;
  background: linear-gradient(180deg, var(--panel), var(--panel2));
  border: 1px solid rgba(140,170,255,0.22);
  box-shadow:
    0 10px 26px rgba(0,0,0,0.30),
    0 0 18px rgba(72,145,255,0.18);
}

.table-toolbar {
  display: flex;
  justify-content: flex-end;
  gap: 10px;
  margin-bottom: 0.6rem;
}

.table-btn {
  appearance: none;
  border: 1px solid rgba(140,170,255,0.40);
  background: rgba(72,145,255,0.14);
  color: var(--text);
  padding: 7px 10px;
  border-radius: 0.7rem;
  cursor: pointer;
  font-weight: 700;
  letter-spacing: 0.2px;
  transition: transform 120ms ease, box-shadow 120ms ease, border-color 120ms ease, background 120ms ease;
}

.table-btn:hover {
  transform: translateY(-1px);
  border-color: rgba(140,170,255,0.70);
  background: rgba(72,145,255,0.22);
  box-shadow: 0 0 18px rgba(72,145,255,0.35);
}

.table-btn:active {
  transform: translateY(0px);
}

/* Definition lists */
.main-content dl { padding: 0; }
.main-content dl dt {
  padding: 0;
  margin-top: 1rem;
  font-size: 1rem;
  font-weight: 800;
  color: var(--text);
}
.main-content dl dd {
  padding: 0;
  margin-bottom: 1rem;
  color: var(--muted);
}

/* Reactable: focus glow + small polish */
.reactable .rt-search input:focus,
.reactable .rt-filter input:focus,
.reactable select:focus {
  border-color: rgba(140,170,255,0.70) !important;
  box-shadow: 0 0 0 3px rgba(72,145,255,0.18), 0 0 18px rgba(72,145,255,0.30) !important;
}

/* Reactable: soften grid + round the whole widget */
.reactable {
  border-radius: 14px;
  overflow: hidden; /* keeps rounded corners clean */
}

/* Scrollbar polish (Chrome/Edge) */
.reactable ::-webkit-scrollbar { height: 10px; width: 10px; }
.reactable ::-webkit-scrollbar-track { background: rgba(0,0,0,0.15); border-radius: 999px; }
.reactable ::-webkit-scrollbar-thumb { background: rgba(140,170,255,0.25); border-radius: 999px; }
.reactable ::-webkit-scrollbar-thumb:hover { background: rgba(140,170,255,0.40); }

.reactable {
  position: relative;
  border-radius: 16px;
  overflow: hidden;
}

.reactable::before {
  content: "";
  position: absolute;
  inset: 0;
  border-radius: 16px;
  padding: 1px;
  background: linear-gradient(
    135deg,
    rgba(72,145,255,0.7),
    rgba(168,80,255,0.5),
    rgba(72,145,255,0.7)
  );
  -webkit-mask:
    linear-gradient(#000 0 0) content-box,
    linear-gradient(#000 0 0);
  -webkit-mask-composite: xor;
  mask-composite: exclude;
  pointer-events: none;
}
.reactable .rt-tbody .rt-tr:hover {
  background: rgba(72,145,255,0.12) !important;
  box-shadow: inset 0 0 18px rgba(72,145,255,0.18);
}
.reactable .rt-tr {
  transition: background 120ms ease, box-shadow 120ms ease;
}

.reactable .rt-pagination button {
  transition: all 120ms ease;
}

```

```{r Environment, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
temp <- globalenv()
TempNames <- names(temp)
for(nam in TempNames) {
  assign(x = nam, value = eval(temp[[nam]]), envir = .GlobalEnv)
}
```

```{r Describe Data and Table Creation, echo = FALSE}
# ============================================================
# Shared Formatting Safety Helper
# ============================================================

safe_format_digits <- function(digits = NULL, default = 3L, max_digits = 8L) {

  if (is.null(digits) || length(digits) == 0L) {
    return(as.integer(default))
  }

  digits <- suppressWarnings(as.integer(digits[1L]))

  if (is.na(digits) || digits < 0L) {
    return(as.integer(default))
  }

  as.integer(min(digits, max_digits))
}

# ============================================================
# Data Description / Column Audit
# ============================================================

null_count <- function(x) {
  # Atomic data.frame/data.table columns cannot contain row-level NULLs.
  # List columns can.
  if (is.list(x)) {
    return(sum(vapply(x, is.null, logical(1L))))
  }

  0L
}

empty_count <- function(x) {
  # Empty strings for character/factor-like fields.
  # Empty elements for list columns.
  if (is.character(x)) {
    return(sum(!is.na(x) & trimws(x) == ""))
  }

  if (is.factor(x)) {
    y <- as.character(x)
    return(sum(!is.na(y) & trimws(y) == ""))
  }

  if (is.list(x)) {
    return(sum(vapply(x, function(z) length(z) == 0L, logical(1L))))
  }

  0L
}

infinite_count <- function(x) {
  if (is.numeric(x) || is.integer(x)) {
    return(sum(is.infinite(x)))
  }

  0L
}

nan_count <- function(x) {
  if (is.numeric(x) || is.integer(x)) {
    return(sum(is.nan(x)))
  }

  0L
}

unique_count <- function(x) {
  if (is.list(x)) {
    # uniqueN() can be awkward on arbitrary list columns.
    return(NA_integer_)
  }

  data.table::uniqueN(x, na.rm = FALSE)
}

non_missing_unique_count <- function(x) {
  if (is.list(x)) {
    return(NA_integer_)
  }

  data.table::uniqueN(x, na.rm = TRUE)
}

mode_value <- function(x) {
  if (is.list(x)) {
    return(NA_character_)
  }

  y <- x[!is.na(x)]

  if (!length(y)) {
    return(NA_character_)
  }

  tab <- sort(table(y), decreasing = TRUE)
  as.character(names(tab)[1L])
}

mode_count <- function(x) {
  if (is.list(x)) {
    return(NA_integer_)
  }

  y <- x[!is.na(x)]

  if (!length(y)) {
    return(NA_integer_)
  }

  max(as.integer(table(y)))
}

first_values <- function(x, n = 5L) {
  y <- utils::head(x, n)

  if (is.list(y)) {
    y <- vapply(
      y,
      function(z) {
        if (is.null(z)) {
          "<NULL>"
        } else if (length(z) == 0L) {
          "<EMPTY>"
        } else {
          paste(as.character(z), collapse = "|")
        }
      },
      character(1L)
    )
  } else {
    y <- as.character(y)
    y[is.na(y)] <- "<NA>"
    y[trimws(y) == ""] <- "<EMPTY STRING>"
  }

  paste(y, collapse = ", ")
}

is_numeric_like_character <- function(x) {
  if (!is.character(x) && !is.factor(x)) {
    return(FALSE)
  }

  y <- trimws(as.character(x))
  y <- y[!is.na(y) & y != ""]

  if (!length(y)) {
    return(FALSE)
  }

  mean(!is.na(suppressWarnings(as.numeric(y)))) >= 0.95
}

is_date_like_character <- function(x) {
  if (!is.character(x) && !is.factor(x)) {
    return(FALSE)
  }

  y <- trimws(as.character(x))
  y <- y[!is.na(y) & y != ""]

  if (!length(y)) {
    return(FALSE)
  }

  if (length(y) > 1000L) {
    y <- sample(y, 1000L)
  }

  # Only check highly standard formats.
  # Do not use loose as.Date(y), because it can error and is too magical.
  formats <- c(
    "%Y-%m-%d",
    "%Y/%m/%d",
    "%m/%d/%Y",
    "%m-%d-%Y",
    "%d-%b-%Y",
    "%d %b %Y"
  )

  rates <- vapply(
    formats,
    function(fmt) {
      parsed <- tryCatch(
        suppressWarnings(as.Date(y, format = fmt)),
        error = function(e) rep(as.Date(NA), length(y))
      )

      mean(!is.na(parsed))
    },
    numeric(1L)
  )

  max(rates, na.rm = TRUE) >= 0.95
}

column_role_guess <- function(x, var_name = NULL, n_rows = NULL) {

  cls <- class(x)[1L]
  unique_n <- unique_count(x)
  non_missing_n <- sum(!is.na(x))

  if (is.list(x)) {
    return("List Column")
  }

  if (!is.null(var_name) && grepl("(^id$|_id$|id$|uuid|guid)", var_name, ignore.case = TRUE)) {
    return("Possible ID")
  }

  if (inherits(x, c("Date", "POSIXct", "POSIXlt", "IDate", "ITime"))) {
    return("Date/Time")
  }

  if (cls %in% c("character", "factor")) {
    if (!is.na(unique_n) && unique_n <= 2L) {
      return("Binary Categorical")
    }

    if (is_numeric_like_character(x)) {
      return("Numeric-like Text")
    }

    if (is_date_like_character(x)) {
      return("Date-like Text")
    }

    if (!is.na(unique_n) && !is.null(n_rows) && unique_n > 0.9 * n_rows) {
      return("High-Cardinality Text")
    }

    return("Categorical")
  }

  if (cls %in% c("logical")) {
    return("Logical")
  }

  if (cls %in% c("numeric", "integer")) {
    if (!is.na(unique_n) && unique_n <= 2L) {
      return("Binary Numeric")
    }

    if (!is.na(unique_n) && !is.null(n_rows) && unique_n > 0.9 * n_rows) {
      return("Continuous / Possible ID")
    }

    return("Numeric")
  }

  cls
}

n_rows <- nrow(data)

DescribeData <- data.table::data.table(
  `Variable Name` = names(data)
)

DescribeData[, `Variable Type` := vapply(
  data,
  function(x) class(x)[1L],
  character(1L)
)]

DescribeData[, `Column Role Guess` := vapply(
  names(data),
  function(nm) column_role_guess(data[[nm]], var_name = nm, n_rows = n_rows),
  character(1L)
)]

DescribeData[, `Rows` := n_rows]

DescribeData[, `NULL Counts` := vapply(
  data,
  null_count,
  integer(1L)
)]

DescribeData[, `NA Counts` := vapply(
  data,
  function(x) sum(is.na(x)),
  integer(1L)
)]

DescribeData[, `NA Percent` := round(
  vapply(data, function(x) mean(is.na(x)) * 100, numeric(1L)),
  2
)]

DescribeData[, `NaN Counts` := vapply(
  data,
  nan_count,
  integer(1L)
)]

DescribeData[, `Infinite Counts` := vapply(
  data,
  infinite_count,
  integer(1L)
)]

DescribeData[, `Empty Counts` := vapply(
  data,
  empty_count,
  integer(1L)
)]

DescribeData[, `Unique Values` := vapply(
  data,
  unique_count,
  integer(1L)
)]

DescribeData[, `Non-Missing Unique Values` := vapply(
  data,
  non_missing_unique_count,
  integer(1L)
)]

DescribeData[, `Unique Percent` := round(
  `Unique Values` / pmax(`Rows`, 1L) * 100,
  2
)]

DescribeData[, `Mode` := vapply(
  data,
  mode_value,
  character(1L)
)]

DescribeData[, `Mode Count` := vapply(
  data,
  mode_count,
  integer(1L)
)]

DescribeData[, `Mode Percent` := round(
  `Mode Count` / pmax(`Rows` - `NA Counts`, 1L) * 100,
  2
)]

DescribeData[, `Is Constant` := fifelse(
  !is.na(`Non-Missing Unique Values`) & `Non-Missing Unique Values` <= 1L,
  TRUE,
  FALSE
)]

DescribeData[, `Has Missing` := `NA Counts` > 0L | `NULL Counts` > 0L | `NaN Counts` > 0L]

DescribeData[, `Has Infinite` := `Infinite Counts` > 0L]

DescribeData[, `First 5 Values` := vapply(
  data,
  first_values,
  character(1L)
)]

# ============================================================
# Describe Data Reactable Theme Helpers
# ============================================================

audit_badge <- function(value, type = c("neutral", "good", "warning", "danger", "info")) {

  type <- match.arg(type)

  colors <- list(
    neutral = list(bg = "#263247", fg = "#CBD5E1", border = "#475569"),
    good    = list(bg = "#064E3B", fg = "#A7F3D0", border = "#10B981"),
    warning = list(bg = "#78350F", fg = "#FDE68A", border = "#F59E0B"),
    danger  = list(bg = "#7F1D1D", fg = "#FECACA", border = "#EF4444"),
    info    = list(bg = "#1E3A8A", fg = "#BFDBFE", border = "#3B82F6")
  )

  htmltools::tags$span(
    style = paste0(
      "display:inline-block;",
      "padding:2px 8px;",
      "border-radius:999px;",
      "font-size:11px;",
      "font-weight:700;",
      "letter-spacing:0.02em;",
      "background:", colors[[type]]$bg, ";",
      "color:", colors[[type]]$fg, ";",
      "border:1px solid ", colors[[type]]$border, ";"
    ),
    as.character(value)
  )
}

fmt_num <- function(x, digits = 0L) {
  ifelse(
    is.na(x),
    NA_character_,
    formatC(x, format = "f", big.mark = ",", digits = digits)
  )
}

fmt_pct <- function(x, digits = 2L) {
  ifelse(
    is.na(x),
    NA_character_,
    paste0(formatC(x, format = "f", big.mark = ",", digits = digits), "%")
  )
}

numeric_cell_style <- function(value) {
  list(
    textAlign = "right",
    fontVariantNumeric = "tabular-nums",
    color = if (length(value) == 0 || is.na(value)) "#64748B" else "#E2E8F0"
  )
}

problem_count_cell <- function(value) {
  if (is.na(value)) {
    return(htmltools::tags$span(style = "color:#64748B;", "—"))
  }

  if (value > 0) {
    audit_badge(fmt_num(value, 0L), "danger")
  } else {
    htmltools::tags$span(style = "color:#64748B;", "0")
  }
}

percent_cell <- function(value, danger_cutoff = 25, warning_cutoff = 5) {
  if (is.na(value)) {
    return(htmltools::tags$span(style = "color:#64748B;", "—"))
  }

  type <- if (value >= danger_cutoff) {
    "danger"
  } else if (value >= warning_cutoff) {
    "warning"
  } else if (value > 0) {
    "info"
  } else {
    "neutral"
  }

  audit_badge(fmt_pct(value, 2L), type)
}

bool_cell <- function(value) {
  if (is.na(value)) {
    return(htmltools::tags$span(style = "color:#64748B;", "—"))
  }

  if (isTRUE(value)) {
    audit_badge("Yes", "danger")
  } else {
    audit_badge("No", "good")
  }
}

role_cell <- function(value) {
  type <- switch(
    as.character(value),
    "Possible ID" = "warning",
    "Continuous / Possible ID" = "warning",
    "High-Cardinality Text" = "warning",
    "Numeric-like Text" = "info",
    "Date-like Text" = "info",
    "Date/Time" = "info",
    "List Column" = "warning",
    "Binary Numeric" = "neutral",
    "Binary Categorical" = "neutral",
    "Numeric" = "good",
    "Categorical" = "good",
    "Logical" = "neutral",
    "neutral"
  )

  audit_badge(value, type)
}

type_cell <- function(value) {
  type <- switch(
    as.character(value),
    "numeric" = "good",
    "integer" = "good",
    "character" = "info",
    "factor" = "info",
    "Date" = "info",
    "IDate" = "info",
    "POSIXct" = "info",
    "logical" = "neutral",
    "list" = "warning",
    "neutral"
  )

  audit_badge(value, type)
}

sample_values_cell <- function(value) {
  htmltools::tags$span(
    title = as.character(value),
    style = paste0(
      "display:block;",
      "max-width:420px;",
      "overflow:hidden;",
      "text-overflow:ellipsis;",
      "white-space:nowrap;",
      "color:#CBD5E1;",
      "font-family:ui-monospace, SFMono-Regular, Menlo, Monaco, Consolas, monospace;",
      "font-size:12px;"
    ),
    as.character(value)
  )
}

# ============================================================
# Describe Data Table
# ============================================================

Describe_Data <- reactable::reactable(
  data = DescribeData,

  # Core functionality
  compact = TRUE,
  defaultPageSize = 15,
  pageSizeOptions = c(10, 15, 25, 50, 100),
  wrap = FALSE,
  filterable = TRUE,
  fullWidth = TRUE,
  highlight = TRUE,
  pagination = TRUE,
  resizable = TRUE,
  searchable = TRUE,
  selection = "multiple",
  showPagination = TRUE,
  showPageSizeOptions = TRUE,
  showSortable = TRUE,
  showSortIcon = TRUE,
  sortable = TRUE,
  striped = TRUE,
  bordered = FALSE,
  outlined = FALSE,

  # Quality of life
  defaultColDef = reactable::colDef(
    minWidth = 110,
    headerStyle = list(
      background = "#0F1B33",
      color = "#E5E7EB",
      fontWeight = "800",
      borderBottom = "1px solid #334155",
      textTransform = "uppercase",
      letterSpacing = "0.045em",
      fontSize = "11px"
    ),
    style = list(
      borderBottom = "1px solid rgba(148, 163, 184, 0.14)"
    )
  ),

  columns = list(

    `Variable Name` = reactable::colDef(
      name = "Variable",
      sticky = "left",
      minWidth = 220,
      filterable = TRUE,
      style = list(
        position = "sticky",
        left = 0,
        zIndex = 1,
        background = "#101B2F",
        color = "#F8FAFC",
        fontWeight = "800",
        fontFamily = "ui-monospace, SFMono-Regular, Menlo, Monaco, Consolas, monospace"
      ),
      headerStyle = list(
        position = "sticky",
        left = 0,
        zIndex = 2,
        background = "#0B1326",
        color = "#F8FAFC",
        fontWeight = "900",
        borderBottom = "1px solid #334155"
      )
    ),

    `Variable Type` = reactable::colDef(
      name = "Type",
      minWidth = 125,
      cell = type_cell,
      align = "center"
    ),

    `Column Role Guess` = reactable::colDef(
      name = "Role Guess",
      minWidth = 185,
      cell = role_cell,
      align = "center"
    ),

    Rows = reactable::colDef(
      minWidth = 95,
      align = "right",
      cell = function(value) fmt_num(value, 0L),
      style = numeric_cell_style
    ),

    `NULL Counts` = reactable::colDef(
      name = "NULL",
      minWidth = 95,
      align = "center",
      cell = problem_count_cell
    ),

    `NA Counts` = reactable::colDef(
      name = "NA",
      minWidth = 95,
      align = "center",
      cell = problem_count_cell
    ),

    `NA Percent` = reactable::colDef(
      name = "NA %",
      minWidth = 105,
      align = "center",
      cell = function(value) percent_cell(value, danger_cutoff = 25, warning_cutoff = 5)
    ),

    `NaN Counts` = reactable::colDef(
      name = "NaN",
      minWidth = 95,
      align = "center",
      cell = problem_count_cell
    ),

    `Infinite Counts` = reactable::colDef(
      name = "Inf",
      minWidth = 95,
      align = "center",
      cell = problem_count_cell
    ),

    `Empty Counts` = reactable::colDef(
      name = "Empty",
      minWidth = 95,
      align = "center",
      cell = problem_count_cell
    ),

    `Unique Values` = reactable::colDef(
      name = "Unique",
      minWidth = 105,
      align = "right",
      cell = function(value) fmt_num(value, 0L),
      style = numeric_cell_style
    ),

    `Non-Missing Unique Values` = reactable::colDef(
      name = "Unique Non-NA",
      minWidth = 135,
      align = "right",
      cell = function(value) fmt_num(value, 0L),
      style = numeric_cell_style
    ),

    `Unique Percent` = reactable::colDef(
      name = "Unique %",
      minWidth = 115,
      align = "center",
      cell = function(value) {
        if (is.na(value)) {
          return(htmltools::tags$span(style = "color:#64748B;", "—"))
        }

        type <- if (value >= 90) {
          "warning"
        } else if (value <= 1) {
          "warning"
        } else {
          "neutral"
        }

        audit_badge(fmt_pct(value, 2L), type)
      }
    ),

    Mode = reactable::colDef(
      minWidth = 160,
      cell = function(value) {
        htmltools::tags$span(
          title = as.character(value),
          style = paste0(
            "display:block;",
            "max-width:150px;",
            "overflow:hidden;",
            "text-overflow:ellipsis;",
            "white-space:nowrap;",
            "color:#CBD5E1;",
            "font-family:ui-monospace, SFMono-Regular, Menlo, Monaco, Consolas, monospace;",
            "font-size:12px;"
          ),
          ifelse(is.na(value), "—", as.character(value))
        )
      }
    ),

    `Mode Count` = reactable::colDef(
      name = "Mode N",
      minWidth = 105,
      align = "right",
      cell = function(value) fmt_num(value, 0L),
      style = numeric_cell_style
    ),

    `Mode Percent` = reactable::colDef(
      name = "Mode %",
      minWidth = 115,
      align = "center",
      cell = function(value) {
        if (is.na(value)) {
          return(htmltools::tags$span(style = "color:#64748B;", "—"))
        }

        type <- if (value >= 95) {
          "danger"
        } else if (value >= 75) {
          "warning"
        } else {
          "neutral"
        }

        audit_badge(fmt_pct(value, 2L), type)
      }
    ),

    `Is Constant` = reactable::colDef(
      name = "Constant",
      minWidth = 105,
      align = "center",
      cell = bool_cell
    ),

    `Has Missing` = reactable::colDef(
      name = "Missing",
      minWidth = 105,
      align = "center",
      cell = bool_cell
    ),

    `Has Infinite` = reactable::colDef(
      name = "Infinite",
      minWidth = 105,
      align = "center",
      cell = bool_cell
    ),

    `First 5 Values` = reactable::colDef(
      name = "Sample Values",
      minWidth = 430,
      cell = sample_values_cell
    )
  ),

  theme = reactable::reactableTheme(
    color = "#E2E8F0",
    backgroundColor = "#0B1326",
    borderColor = "rgba(148, 163, 184, 0.22)",

    stripedColor = "rgba(30, 41, 59, 0.78)",
    highlightColor = "rgba(59, 130, 246, 0.18)",

    rowSelectedStyle = list(
      backgroundColor = "rgba(37, 99, 235, 0.28)",
      boxShadow = "inset 3px 0 0 #60A5FA"
    ),

    cellPadding = "9px 12px",

    style = list(
      fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Inter, Helvetica, Arial, sans-serif",
      fontSize = "13px",
      border = "1px solid rgba(148, 163, 184, 0.22)",
      borderRadius = "14px",
      overflow = "hidden",
      boxShadow = "0 18px 45px rgba(0, 0, 0, 0.28)"
    ),

    tableStyle = list(
      borderCollapse = "separate",
      borderSpacing = "0"
    ),

    headerStyle = list(
      background = "#0F1B33",
      color = "#F8FAFC",
      borderBottom = "1px solid rgba(148, 163, 184, 0.28)"
    ),

    rowStyle = list(
      backgroundColor = "#0B1326"
    ),

    searchInputStyle = list(
      width = "100%",
      backgroundColor = "#111C33",
      color = "#E2E8F0",
      border = "1px solid #334155",
      borderRadius = "10px",
      padding = "8px 12px",
      outline = "none"
    ),

    filterInputStyle = list(
      backgroundColor = "#111C33",
      color = "#E2E8F0",
      border = "1px solid #334155",
      borderRadius = "8px",
      padding = "5px 8px",
      outline = "none"
    ),

    selectStyle = list(
      backgroundColor = "#111C33",
      color = "#E2E8F0",
      border = "1px solid #60A5FA",
      borderRadius = "10px",
      padding = "6px 10px",
      minWidth = "76px",
      height = "34px",
      fontSize = "13px",
      fontWeight = "800",
      lineHeight = "1.2",
      cursor = "pointer",
      outline = "none",
      boxShadow = paste(
        "inset 0 1px 0 rgba(255, 255, 255, 0.06),",
        "0 0 0 1px rgba(96, 165, 250, 0.14),",
        "0 8px 18px rgba(0, 0, 0, 0.24)"
      )
    )
  )
)

```

```{r Target Variable Analysis, echo=FALSE}
# ============================================================
# Target-Oriented Analysis
# ============================================================

# ----------------------------
# Target settings
# ----------------------------

TargetMaxCategoricalLevels <- 25L
TargetMaxAssociationRows <- 25L
TargetMaxPlotRows <- 25L
MaxCorrelationPairsToPlot <- 25L

TargetHighLiftThreshold <- 2.00
TargetLowLiftThreshold <- 0.50
TargetExtremeRateThreshold <- 0.90
TargetMinLevelN <- 20L
TargetMinTimePeriods <- 4L
TargetDriftRecentShare <- 0.25
TargetConceptDriftMinN <- 20L
TargetConceptDriftMinPeriods <- 4L

# ----------------------------
# Target settings
# ----------------------------

TargetMaxCategoricalLevels <- 25L
TargetHighLiftThreshold <- 2.00
TargetLowLiftThreshold <- 0.50
TargetExtremeRateThreshold <- 0.90
TargetMinLevelN <- 20L
TargetMinTimePeriods <- 4L
TargetDriftRecentShare <- 0.25
TargetConceptDriftMinN <- 20L
TargetConceptDriftMinPeriods <- 4L


# ============================================================
# Target Safe Helpers
# ============================================================
target_safe_mean <- function(x) {
  out <- suppressWarnings(mean(x, na.rm = TRUE))
  as.numeric(out)
}

target_safe_median <- function(x) {
  out <- suppressWarnings(stats::median(x, na.rm = TRUE))
  as.numeric(out)
}

target_safe_sd <- function(x) {
  out <- suppressWarnings(stats::sd(x, na.rm = TRUE))
  as.numeric(out)
}

target_safe_min <- function(x) {
  out <- suppressWarnings(min(x, na.rm = TRUE))
  as.numeric(out)
}

target_safe_max <- function(x) {
  out <- suppressWarnings(max(x, na.rm = TRUE))
  as.numeric(out)
}

target_is_empty <- function(value) {
  is.null(value) ||
    length(value) == 0L ||
    all(is.na(value))
}

target_safe_chr <- function(value, empty_value = "—") {
  if (target_is_empty(value)) {
    empty_value
  } else {
    as.character(value)
  }
}

target_safe_num <- function(value) {
  if (target_is_empty(value)) {
    return(NA_real_)
  }

  suppressWarnings(as.numeric(value)[1L])
}

target_clean_var_vector <- function(x) {
  if (is.null(x)) {
    return(character(0L))
  }

  x <- as.character(x)
  x <- trimws(x)
  x <- x[!is.na(x) & nzchar(x)]
  unique(x)
}

target_is_numeric_col <- function(x) {
  is.numeric(x) &&
    !inherits(x, c("Date", "POSIXct", "POSIXlt", "IDate", "ITime"))
}

target_is_categorical_col <- function(x) {
  is.character(x) ||
    is.factor(x) ||
    is.logical(x)
}

target_is_date_col <- function(x) {
  inherits(x, c("Date", "POSIXct", "POSIXlt", "IDate", "IDateTime"))
}

target_is_binary_numeric <- function(x) {
  if (!target_is_numeric_col(x)) {
    return(FALSE)
  }

  y <- x[!is.na(x) & is.finite(x)]

  if (!length(y)) {
    return(FALSE)
  }

  vals <- sort(unique(y))

  length(vals) == 2L && all(vals %in% c(0, 1))
}

target_mode_value <- function(x) {
  if (!length(x)) {
    return(NA_character_)
  }

  x <- x[!is.na(x)]

  if (!length(x)) {
    return(NA_character_)
  }

  tab <- sort(table(x), decreasing = TRUE)

  names(tab)[1L]
}

target_fmt_int <- function(x) {
  if (target_is_empty(x)) {
    return(NA_character_)
  }

  x <- suppressWarnings(as.numeric(x))

  if (!length(x) || is.na(x[1L])) {
    return(NA_character_)
  }

  formatC(round(x[1L]), format = "f", digits = 0L, big.mark = ",")
}

target_fmt_pct <- function(x, digits = 2L) {
  if (target_is_empty(x)) {
    return(NA_character_)
  }

  x <- suppressWarnings(as.numeric(x))

  if (!length(x) || is.na(x[1L])) {
    return(NA_character_)
  }

  paste0(formatC(x[1L], format = "f", big.mark = ",", digits = digits), "%")
}

target_safe_cor <- function(x, y, method = "spearman") {
  keep <- !is.na(x) & !is.na(y) & is.finite(x) & is.finite(y)

  x <- x[keep]
  y <- y[keep]

  if (length(x) < 3L) {
    return(NA_real_)
  }

  if (data.table::uniqueN(x) <= 1L || data.table::uniqueN(y) <= 1L) {
    return(NA_real_)
  }

  suppressWarnings(stats::cor(x, y, method = method, use = "complete.obs"))
}

target_safe_cor_p_value <- function(x, y, method = "spearman") {
  keep <- !is.na(x) & !is.na(y) & is.finite(x) & is.finite(y)

  x <- x[keep]
  y <- y[keep]

  if (length(x) < 4L) {
    return(NA_real_)
  }

  if (data.table::uniqueN(x) <= 1L || data.table::uniqueN(y) <= 1L) {
    return(NA_real_)
  }

  out <- tryCatch(
    suppressWarnings(
      stats::cor.test(
        x = x,
        y = y,
        method = method,
        exact = FALSE
      )$p.value
    ),
    error = function(e) NA_real_
  )

  as.numeric(out)
}

target_strength_label <- function(x) {
  if (is.na(x)) {
    return("Not available")
  }

  ax <- abs(x)

  if (ax >= 0.90) {
    "Very Strong"
  } else if (ax >= 0.70) {
    "Strong"
  } else if (ax >= 0.50) {
    "Moderate"
  } else if (ax >= 0.30) {
    "Weak"
  } else {
    "Very Weak"
  }
}

target_direction_label <- function(x) {
  if (is.na(x)) {
    return("Not available")
  }

  if (x > 0) {
    "Positive"
  } else if (x < 0) {
    "Negative"
  } else {
    "Zero"
  }
}

target_risk_word_match <- function(x) {
  x <- tolower(x)

  patterns <- c(
    "target",
    "outcome",
    "result",
    "status",
    "converted",
    "conversion",
    "complete",
    "completed",
    "approved",
    "accepted",
    "rejected",
    "enrolled",
    "enrollment",
    "churn",
    "churned",
    "cancel",
    "cancelled",
    "retained",
    "retention",
    "response",
    "label",
    "score",
    "decision",
    "final",
    "post",
    "after"
  )

  any(vapply(patterns, function(p) grepl(p, x, fixed = TRUE), logical(1L)))
}

target_feature_role <- function(v, x) {
  if (v == TargetVar) {
    return("Target")
  }

  if (target_is_numeric_col(x)) {
    return("Numeric Feature")
  }

  if (target_is_categorical_col(x)) {
    return("Categorical Feature")
  }

  if (target_is_date_col(x)) {
    return("Date/Time")
  }

  "Skipped / Unsupported"
}


# ============================================================
# Target Reactable Styling Helpers
# ============================================================

target_safe_index <- function(index) {
  if (is.null(index) || length(index) == 0L || is.na(index)) {
    return(1L)
  }

  as.integer(index[1L])
}

target_row_bg <- function(index) {
  index <- target_safe_index(index)

  if (index %% 2L == 0L) {
    "#0B1326"
  } else {
    "#111C33"
  }
}

target_sticky_row_bg <- function(index) {
  index <- target_safe_index(index)

  if (index %% 2L == 0L) {
    "#101B2F"
  } else {
    "#13203A"
  }
}

target_dark_row_style <- function(index) {
  list(
    backgroundColor = target_row_bg(index),
    color = "#E2E8F0"
  )
}

target_dark_cell_style <- function(value, index = NULL) {
  list(
    backgroundColor = target_row_bg(index),
    color = if (target_is_empty(value)) "#64748B" else "#E2E8F0",
    borderBottom = "1px solid rgba(148, 163, 184, 0.14)"
  )
}

target_dark_numeric_cell_style <- function(value, index = NULL) {
  list(
    backgroundColor = target_row_bg(index),
    color = if (target_is_empty(value)) "#64748B" else "#E2E8F0",
    textAlign = "right",
    fontVariantNumeric = "tabular-nums",
    borderBottom = "1px solid rgba(148, 163, 184, 0.14)"
  )
}

target_dark_center_cell_style <- function(value, index = NULL) {
  list(
    backgroundColor = target_row_bg(index),
    color = if (target_is_empty(value)) "#64748B" else "#E2E8F0",
    textAlign = "center",
    borderBottom = "1px solid rgba(148, 163, 184, 0.14)"
  )
}

target_dark_sticky_cell_style <- function(value, index = NULL) {
  list(
    position = "sticky",
    left = 0,
    zIndex = 1,
    backgroundColor = target_sticky_row_bg(index),
    color = "#F8FAFC",
    fontWeight = "800",
    fontFamily = "ui-monospace, SFMono-Regular, Menlo, Monaco, Consolas, monospace",
    borderBottom = "1px solid rgba(148, 163, 184, 0.14)",
    boxShadow = "6px 0 10px rgba(0, 0, 0, 0.18)"
  )
}

target_numeric_cell <- function(value, index = NULL, name = NULL, digits = 3L) {

  digits <- safe_format_digits(
    digits = digits,
    default = 3L,
    max_digits = 8L
  )

  if (target_is_empty(value)) {
    htmltools::tags$span(style = "color:#64748B;", "—")
  } else {
    htmltools::tags$span(
      style = "font-variant-numeric:tabular-nums;color:#E2E8F0;",
      target_fmt_num(value, digits = digits)
    )
  }
}

target_pct_cell <- function(value, index = NULL, name = NULL, digits = 2L) {

  digits <- safe_format_digits(
    digits = digits,
    default = 2L,
    max_digits = 8L
  )

  if (target_is_empty(value)) {
    htmltools::tags$span(style = "color:#64748B;", "—")
  } else {
    htmltools::tags$span(
      style = "font-variant-numeric:tabular-nums;color:#E2E8F0;",
      target_fmt_pct(value, digits = digits)
    )
  }
}

target_default_header_style <- list(
  background = "#0F1B33",
  color = "#E5E7EB",
  fontWeight = "800",
  borderBottom = "1px solid #334155",
  textTransform = "uppercase",
  letterSpacing = "0.045em",
  fontSize = "11px"
)

target_theme <- reactable::reactableTheme(
  color = "#E2E8F0",
  backgroundColor = "#0B1326",
  borderColor = "rgba(148, 163, 184, 0.22)",
  highlightColor = "rgba(59, 130, 246, 0.18)",
  rowSelectedStyle = list(
    backgroundColor = "rgba(37, 99, 235, 0.28)",
    boxShadow = "inset 3px 0 0 #60A5FA"
  ),
  cellPadding = "9px 12px",
  style = list(
    fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Inter, Helvetica, Arial, sans-serif",
    fontSize = "13px",
    border = "1px solid rgba(148, 163, 184, 0.22)",
    borderRadius = "14px",
    overflow = "hidden",
    boxShadow = "0 18px 45px rgba(0, 0, 0, 0.28)"
  ),
  tableStyle = list(
    borderCollapse = "separate",
    borderSpacing = "0"
  ),
  headerStyle = list(
    background = "#0F1B33",
    color = "#F8FAFC",
    borderBottom = "1px solid rgba(148, 163, 184, 0.28)"
  ),
  searchInputStyle = list(
    width = "100%",
    backgroundColor = "#111C33",
    color = "#E2E8F0",
    border = "1px solid #334155",
    borderRadius = "10px",
    padding = "8px 12px",
    outline = "none"
  ),
  filterInputStyle = list(
    backgroundColor = "#111C33",
    color = "#E2E8F0",
    border = "1px solid #334155",
    borderRadius = "8px",
    padding = "5px 8px",
    outline = "none"
  ),
  selectStyle = list(
    backgroundColor = "#111C33",
    color = "#E2E8F0",
    border = "1px solid #60A5FA",
    borderRadius = "10px",
    padding = "6px 10px",
    minWidth = "76px",
    height = "34px",
    fontSize = "13px",
    fontWeight = "800",
    lineHeight = "1.2",
    cursor = "pointer",
    outline = "none"
  )
)

target_badge <- function(value, type = c("neutral", "good", "warning", "danger", "info")) {

  type <- match.arg(type)

  colors <- list(
    neutral = list(bg = "#263247", fg = "#CBD5E1", border = "#475569"),
    good    = list(bg = "#064E3B", fg = "#A7F3D0", border = "#10B981"),
    warning = list(bg = "#78350F", fg = "#FDE68A", border = "#F59E0B"),
    danger  = list(bg = "#7F1D1D", fg = "#FECACA", border = "#EF4444"),
    info    = list(bg = "#1E3A8A", fg = "#BFDBFE", border = "#3B82F6")
  )

  htmltools::tags$span(
    style = paste0(
      "display:inline-block;",
      "padding:2px 8px;",
      "border-radius:999px;",
      "font-size:11px;",
      "font-weight:700;",
      "letter-spacing:0.02em;",
      "background:", colors[[type]]$bg, ";",
      "color:", colors[[type]]$fg, ";",
      "border:1px solid ", colors[[type]]$border, ";"
    ),
    target_safe_chr(value)
  )
}

target_integer_cell <- function(value) {
  if (target_is_empty(value)) {
    htmltools::tags$span(style = "color:#64748B;", "—")
  } else {
    htmltools::tags$span(
      style = "font-variant-numeric:tabular-nums;color:#E2E8F0;",
      target_fmt_int(value)
    )
  }
}

target_numeric_cell <- function(value, digits = 3L) {
  if (target_is_empty(value)) {
    htmltools::tags$span(style = "color:#64748B;", "—")
  } else {
    htmltools::tags$span(
      style = "font-variant-numeric:tabular-nums;color:#E2E8F0;",
      safe_format_digits(value, digits)
    )
  }
}

target_pct_cell <- function(value, digits = 2L) {
  if (target_is_empty(value)) {
    htmltools::tags$span(style = "color:#64748B;", "—")
  } else {
    htmltools::tags$span(
      style = "font-variant-numeric:tabular-nums;color:#E2E8F0;",
      target_fmt_pct(value, digits)
    )
  }
}

target_corr_cell <- function(value) {
  value <- target_safe_num(value)

  if (is.na(value)) {
    return(htmltools::tags$span(style = "color:#64748B;", "—"))
  }

  av <- abs(value)

  type <- if (av >= 0.90) {
    "danger"
  } else if (av >= 0.70) {
    "warning"
  } else if (av >= 0.50) {
    "info"
  } else {
    "neutral"
  }

  target_badge(safe_format_digits(value, 3L), type)
}

target_abs_corr_cell <- function(value) {
  value <- target_safe_num(value)

  if (is.na(value)) {
    return(htmltools::tags$span(style = "color:#64748B;", "—"))
  }

  type <- if (value >= 0.90) {
    "danger"
  } else if (value >= 0.70) {
    "warning"
  } else if (value >= 0.50) {
    "info"
  } else {
    "neutral"
  }

  target_badge(safe_format_digits(value, 3L), type)
}

target_lift_cell <- function(value) {
  value <- target_safe_num(value)

  if (is.na(value)) {
    return(htmltools::tags$span(style = "color:#64748B;", "—"))
  }

  type <- if (value >= TargetHighLiftThreshold) {
    "danger"
  } else if (value <= TargetLowLiftThreshold) {
    "warning"
  } else {
    "neutral"
  }

  target_badge(safe_format_digits(value, 3L), type)
}

target_flag_cell <- function(value) {
  value <- target_safe_chr(value)

  type <- switch(
    value,
    "High" = "danger",
    "Medium" = "warning",
    "Low" = "info",
    "Yes" = "danger",
    "No" = "good",
    "Not available" = "neutral",
    "neutral"
  )

  target_badge(value, type)
}

target_text_cell <- function(value) {
  htmltools::tags$span(
    style = "color:#CBD5E1;",
    target_safe_chr(value)
  )
}

target_truncated_mono_cell <- function(value) {
  htmltools::tags$span(
    title = target_safe_chr(value, empty_value = ""),
    style = paste0(
      "display:block;",
      "max-width:720px;",
      "overflow:hidden;",
      "text-overflow:ellipsis;",
      "white-space:nowrap;",
      "color:#CBD5E1;",
      "font-family:ui-monospace, SFMono-Regular, Menlo, Monaco, Consolas, monospace;",
      "font-size:12px;"
    ),
    target_safe_chr(value)
  )
}


# ============================================================
# Target Object Initialization
# ============================================================

TargetVar_Clean <- target_clean_var_vector(TargetVar)

TargetVar_Provided <- length(TargetVar_Clean) > 0L
TargetVar_Name <- if (TargetVar_Provided) TargetVar_Clean[1L] else NA_character_
TargetVar_Valid <- TargetVar_Provided && TargetVar_Name %in% names(data)

TargetVar_Type <- NA_character_
TargetVar_Class <- NA_character_
TargetVar_Usable <- FALSE
TargetProblemType <- "Not provided"

TargetQA <- data.table::data.table()
TargetDistributionTable <- data.table::data.table()
TargetNumericAssociationStats <- data.table::data.table()
TargetCategoricalLevelStats <- data.table::data.table()
TargetCategoricalAssociationStats <- data.table::data.table()
TargetTrendStats <- data.table::data.table()
TargetGroupedTrendStats <- data.table::data.table()
TargetFeatureDriftStats <- data.table::data.table()
TargetConceptDriftStats <- data.table::data.table()
TargetRiskFlags <- data.table::data.table()
TargetPlotList <- list()
TargetTrendPlotList <- list()
TargetGroupedTrendPlotList <- list()
TargetDistributionPlot <- NULL
TargetAssociationPlotList <- list()
TargetDriftPlotList <- list()
TargetRiskPlotList <- list()


# ============================================================
# Target Validation / QA
# ============================================================

if (TargetVar_Valid) {

  target_y <- data[[TargetVar_Name]]

  TargetVar_Class <- class(target_y)[1L]

  TargetVar_Type <- if (target_is_binary_numeric(target_y)) {
    "Binary Numeric"
  } else if (target_is_numeric_col(target_y)) {
    "Continuous Numeric"
  } else if (target_is_categorical_col(target_y)) {
    if (data.table::uniqueN(target_y, na.rm = TRUE) == 2L) {
      "Binary Categorical"
    } else {
      "Multiclass Categorical"
    }
  } else {
    "Unsupported"
  }

  TargetProblemType <- if (TargetVar_Type %in% c("Binary Numeric", "Binary Categorical")) {
    "Binary"
  } else if (TargetVar_Type == "Continuous Numeric") {
    "Regression"
  } else if (TargetVar_Type == "Multiclass Categorical") {
    "Multiclass"
  } else {
    "Unsupported"
  }

  TargetVar_Usable <- TargetProblemType %in% c("Binary", "Regression", "Multiclass")

  TargetQA <- data.table::data.table(
    Metric = c(
      "TargetVar Provided",
      "TargetVar Valid",
      "Target Variable",
      "Target Class",
      "Target Type",
      "Target Problem Type",
      "Target Usable",
      "Rows",
      "Target NA N",
      "Target NA %",
      "Target Unique N",
      "Target Mode"
    ),
    Count = c(
      as.integer(TargetVar_Provided),
      as.integer(TargetVar_Valid),
      NA_integer_,
      NA_integer_,
      NA_integer_,
      NA_integer_,
      as.integer(TargetVar_Usable),
      length(target_y),
      sum(is.na(target_y)),
      NA_integer_,
      data.table::uniqueN(target_y, na.rm = TRUE),
      NA_integer_
    ),
    Value = c(
      as.character(TargetVar_Provided),
      as.character(TargetVar_Valid),
      TargetVar_Name,
      TargetVar_Class,
      TargetVar_Type,
      TargetProblemType,
      as.character(TargetVar_Usable),
      as.character(length(target_y)),
      as.character(sum(is.na(target_y))),
      target_fmt_pct(mean(is.na(target_y)) * 100, 2L),
      as.character(data.table::uniqueN(target_y, na.rm = TRUE)),
      target_mode_value(target_y)
    )
  )

} else {

  TargetQA <- data.table::data.table(
    Metric = c(
      "TargetVar Provided",
      "TargetVar Valid",
      "Target Variable",
      "Target Class",
      "Target Type",
      "Target Problem Type",
      "Target Usable",
      "Rows",
      "Target NA N",
      "Target NA %",
      "Target Unique N",
      "Target Mode"
    ),
    Count = c(
      as.integer(TargetVar_Provided),
      as.integer(TargetVar_Valid),
      NA_integer_,
      NA_integer_,
      NA_integer_,
      NA_integer_,
      0L,
      nrow(data),
      NA_integer_,
      NA_integer_,
      NA_integer_,
      NA_integer_
    ),
    Value = c(
      as.character(TargetVar_Provided),
      as.character(TargetVar_Valid),
      ifelse(TargetVar_Provided, TargetVar_Name, ""),
      "",
      "",
      "Not provided",
      "FALSE",
      as.character(nrow(data)),
      "",
      "",
      "",
      ""
    )
  )
}


# ============================================================
# Target Distribution
# ============================================================

if (TargetVar_Valid && TargetVar_Usable) {

  target_y <- data[[TargetVar_Name]]

  if (TargetProblemType %in% c("Binary", "Multiclass")) {

    target_dist_dt <- data.table::data.table(
      TargetValue = as.character(target_y)
    )

    target_dist_dt[is.na(TargetValue), TargetValue := "<NA>"]
    target_dist_dt[trimws(TargetValue) == "", TargetValue := "<EMPTY STRING>"]

    TargetDistributionTable <- target_dist_dt[
      ,
      .(N = .N),
      by = TargetValue
    ]

    data.table::setorderv(TargetDistributionTable, "N", order = -1L)

    TargetDistributionTable[, Percent := N / sum(N) * 100]

    TargetDistributionPlot <- AutoPlots::Bar(
      dt = TargetDistributionTable,
      XVar = "TargetValue",
      YVar = "N",
      title.text = paste0(TargetVar_Name, " Distribution"),
      yAxis.title = "Count",
      xAxis.title = TargetVar_Name,
      Theme = Theme
    )

    TargetPlotList[["Target Distribution"]] <- TargetDistributionPlot

  } else if (TargetProblemType == "Regression") {

    TargetDistributionTable <- data.table::data.table(
      Metric = c(
        "N",
        "NA N",
        "Mean",
        "Median",
        "Standard Deviation",
        "Min",
        "Q25",
        "Q75",
        "Max"
      ),
      Value = as.numeric(c(
        sum(!is.na(target_y) & is.finite(target_y)),
        sum(is.na(target_y)),
        target_safe_mean(target_y),
        target_safe_median(target_y),
        target_safe_sd(target_y),
        target_safe_min(target_y),
        suppressWarnings(as.numeric(stats::quantile(target_y, probs = 0.25, na.rm = TRUE, names = FALSE))),
        suppressWarnings(as.numeric(stats::quantile(target_y, probs = 0.75, na.rm = TRUE, names = FALSE))),
        target_safe_max(target_y)
      ))
    )

    TargetDistributionPlot <- AutoPlots::Histogram(
      dt = data[!is.na(get(TargetVar_Name)) & is.finite(get(TargetVar_Name))],
      XVar = TargetVar_Name,
      title.text = paste0(TargetVar_Name, " Distribution"),
      xAxis.title = TargetVar_Name,
      yAxis.title = "Count",
      Theme = Theme
    )

    TargetPlotList[["Target Distribution"]] <- TargetDistributionPlot
  }
}


# ============================================================
# Feature Set for Target Analysis
# ============================================================

TargetCandidateVars <- setdiff(names(data), TargetVar_Name)

TargetNumericFeatureVars <- TargetCandidateVars[
  vapply(
    TargetCandidateVars,
    function(v) target_is_numeric_col(data[[v]]),
    logical(1L)
  )
]

TargetCategoricalFeatureVars <- TargetCandidateVars[
  vapply(
    TargetCandidateVars,
    function(v) target_is_categorical_col(data[[v]]),
    logical(1L)
  )
]

TargetSkippedFeatureVars <- setdiff(
  TargetCandidateVars,
  c(TargetNumericFeatureVars, TargetCategoricalFeatureVars)
)


# ============================================================
# Numeric Feature Association With Target
# ============================================================

if (TargetVar_Valid && TargetVar_Usable && TargetProblemType %in% c("Binary", "Regression") && length(TargetNumericFeatureVars) > 0L) {

  target_y <- data[[TargetVar_Name]]

  if (TargetProblemType == "Binary" && !target_is_numeric_col(target_y)) {
    target_levels <- sort(unique(as.character(target_y[!is.na(target_y)])))
    target_y_num <- as.integer(as.character(target_y) == target_levels[length(target_levels)])
  } else {
    target_y_num <- target_y
  }

  TargetNumericAssociationStats <- data.table::rbindlist(
    lapply(TargetNumericFeatureVars, function(v) {

      x <- data[[v]]

      keep <- !is.na(x) &
        !is.na(target_y_num) &
        is.finite(x) &
        is.finite(target_y_num)

      n_valid <- sum(keep)

      r <- target_safe_cor(x, target_y_num, method = "spearman")
      p <- target_safe_cor_p_value(x, target_y_num, method = "spearman")

      data.table::data.table(
        Feature = v,
        FeatureType = class(x)[1L],
        N = n_valid,
        `Feature NA N` = sum(is.na(x)),
        `Feature NA %` = mean(is.na(x)) * 100,
        `Target NA N` = sum(is.na(target_y_num)),
        `Correlation` = r,
        `Abs Correlation` = abs(r),
        Direction = target_direction_label(r),
        Strength = target_strength_label(r),
        `P Value` = p,
        `Suspicious Name` = target_risk_word_match(v)
      )
    }),
    fill = TRUE
  )

  data.table::setorderv(
    TargetNumericAssociationStats,
    cols = c("Abs Correlation", "N"),
    order = c(-1L, -1L),
    na.last = TRUE
  )
}


# ============================================================
# Categorical Feature Association With Target
# ============================================================

if (TargetVar_Valid && TargetVar_Usable && TargetProblemType %in% c("Binary", "Regression") && length(TargetCategoricalFeatureVars) > 0L) {

  target_y <- data[[TargetVar_Name]]

  if (TargetProblemType == "Binary" && !target_is_numeric_col(target_y)) {
    target_levels <- sort(unique(as.character(target_y[!is.na(target_y)])))
    target_y_num <- as.integer(as.character(target_y) == target_levels[length(target_levels)])
  } else {
    target_y_num <- target_y
  }

  global_target_mean <- mean(target_y_num, na.rm = TRUE)

  TargetCategoricalLevelStats <- data.table::rbindlist(
    lapply(TargetCategoricalFeatureVars, function(v) {

      x <- as.character(data[[v]])
      x[is.na(x)] <- "<NA>"
      x[trimws(x) == ""] <- "<EMPTY STRING>"

      data2 <- data.table::data.table(
        Feature = v,
        Level = x,
        TargetValue = target_y_num
      )

      out <- data2[
        ,
        .(
          N = as.integer(.N),
          `Target NonMissing N` = as.integer(sum(!is.na(TargetValue))),
          `Target Mean` = target_safe_mean(TargetValue),
          `Target Median` = target_safe_median(TargetValue),
          `Target SD` = target_safe_sd(TargetValue)
        ),
        by = .(Feature, Level)
      ]

      out[, `Level N %` := N / sum(N) * 100]
      out[, `Global Target Mean` := global_target_mean]
      out[, Lift := `Target Mean` / global_target_mean]
      out[, `Abs Lift From 1` := abs(Lift - 1)]
      out[, `Suspicious Name` := target_risk_word_match(v)]
      out[, `Low N Flag` := N < TargetMinLevelN]

      data.table::setorderv(out, c("Feature", "N"), order = c(1L, -1L))

      if (nrow(out) > TargetMaxCategoricalLevels) {
        out <- out[seq_len(TargetMaxCategoricalLevels)]
      }

      out
    }),
    fill = TRUE
  )

  TargetCategoricalAssociationStats <- TargetCategoricalLevelStats[
    ,
    .(
      Levels = data.table::uniqueN(Level),
      N = sum(N),
      `Max Target Mean` = max(`Target Mean`, na.rm = TRUE),
      `Min Target Mean` = min(`Target Mean`, na.rm = TRUE),
      `Target Mean Range` = max(`Target Mean`, na.rm = TRUE) - min(`Target Mean`, na.rm = TRUE),
      `Max Lift` = max(Lift, na.rm = TRUE),
      `Min Lift` = min(Lift, na.rm = TRUE),
      `Max Abs Lift From 1` = max(`Abs Lift From 1`, na.rm = TRUE),
      `Extreme Level Count` = sum(
        !is.na(`Target Mean`) &
          (`Target Mean` >= TargetExtremeRateThreshold | `Target Mean` <= (1 - TargetExtremeRateThreshold))
      ),
      `Low N Level Count` = sum(`Low N Flag`, na.rm = TRUE),
      `Suspicious Name` = any(`Suspicious Name`, na.rm = TRUE)
    ),
    by = Feature
  ]

  TargetCategoricalAssociationStats[, RiskLevel := fifelse(
    `Suspicious Name` & `Max Abs Lift From 1` >= 1,
    "High",
    fifelse(
      `Max Abs Lift From 1` >= 1 | `Extreme Level Count` > 0,
      "Medium",
      fifelse(`Max Abs Lift From 1` >= 0.5, "Low", "None")
    )
  )]

  data.table::setorderv(
    TargetCategoricalAssociationStats,
    cols = c("RiskLevel", "Max Abs Lift From 1"),
    order = c(1L, -1L)
  )
}


# ============================================================
# Target Trend / Target Grouped Trend
# ============================================================

TargetTrendDateVar_Valid <- !is.null(TrendDateVar) &&
  length(TrendDateVar) == 1L &&
  !is.na(TrendDateVar) &&
  nzchar(TrendDateVar) &&
  TrendDateVar %in% names(data) &&
  target_is_date_col(data[[TrendDateVar]])

TargetTrendGroupVars_Requested <- target_clean_var_vector(TrendGroupVar)
TargetTrendGroupVars_Valid <- TargetTrendGroupVars_Requested[
  TargetTrendGroupVars_Requested %in% names(data)
]
TargetTrendGroupVars_Missing <- setdiff(
  TargetTrendGroupVars_Requested,
  TargetTrendGroupVars_Valid
)

TargetTrendGroupVar_Valid <- length(TargetTrendGroupVars_Valid) > 0L

TargetGroupedTrendStatsList <- list()

if (TargetVar_Valid && TargetVar_Usable && TargetProblemType %in% c("Binary", "Regression") && TargetTrendDateVar_Valid) {

  target_y <- data[[TargetVar_Name]]

  if (TargetProblemType == "Binary" && !target_is_numeric_col(target_y)) {

    target_levels <- sort(unique(as.character(target_y[!is.na(target_y)])))

    if (length(target_levels) >= 2L) {
      target_y_num <- as.integer(as.character(target_y) == target_levels[length(target_levels)])
    } else {
      target_y_num <- rep(NA_integer_, length(target_y))
    }

  } else {
    target_y_num <- target_y
  }

  data_target_trend <- data.table::copy(data)
  data_target_trend[, `.TargetValue` := target_y_num]

  # ----------------------------
  # Overall target trend
  # ----------------------------

  TargetTrendStats <- data_target_trend[
    !is.na(get(TrendDateVar)) &
      !is.na(`.TargetValue`) &
      is.finite(`.TargetValue`),
    .(
      N = as.integer(.N),
      TargetMean = target_safe_mean(`.TargetValue`),
      TargetMedian = target_safe_median(`.TargetValue`),
      TargetSD = target_safe_sd(`.TargetValue`)
    ),
    by = TrendDateVar
  ]

  data.table::setorderv(TargetTrendStats, TrendDateVar)

  if (nrow(TargetTrendStats) > 0L) {

    TargetTrendPlotList[["Target Overall Trend"]] <- AutoPlots::Area(
      dt = TargetTrendStats,
      XVar = TrendDateVar,
      YVar = "TargetMean",
      title.text = paste0(TargetVar_Name, " Overall Trend"),
      yAxis.title = ifelse(TargetProblemType == "Binary", "Target Rate", "Target Mean"),
      xAxis.title = TrendDateVar,
      Theme = Theme
    )
  }

  # ----------------------------
  # Grouped target trends
  # one plot per valid TrendGroupVar
  # ----------------------------

  if (TargetTrendGroupVar_Valid) {

    for (g in TargetTrendGroupVars_Valid) {

      data2 <- data_target_trend[
        !is.na(get(TrendDateVar)) &
          !is.na(get(g)) &
          !is.na(`.TargetValue`) &
          is.finite(`.TargetValue`),
        .(
          N = as.integer(.N),
          TargetMean = target_safe_mean(`.TargetValue`),
          TargetMedian = target_safe_median(`.TargetValue`),
          TargetSD = target_safe_sd(`.TargetValue`)
        ),
        by = c(TrendDateVar, g)
      ]

      if (nrow(data2) > 0L) {

        data.table::setorderv(
          data2,
          cols = c(g, TrendDateVar)
        )

        # Standardize grouped stats columns so multiple group variables
        # can be combined into one output table.
        data2[, TrendGroupVar := g]
        data.table::setnames(data2, old = g, new = "TrendGroupValue")

        data.table::setcolorder(
          data2,
          c(
            "TrendGroupVar",
            "TrendGroupValue",
            TrendDateVar,
            "N",
            "TargetMean",
            "TargetMedian",
            "TargetSD"
          )
        )

        TargetGroupedTrendStatsList[[g]] <- data2

        TargetGroupedTrendPlotList[[paste0("Target Trend by ", g)]] <- AutoPlots::Line(
          dt = data2,
          XVar = TrendDateVar,
          YVar = "TargetMean",
          GroupVar = "TrendGroupValue",
          title.text = paste0(TargetVar_Name, " Trend by ", g),
          yAxis.title = ifelse(TargetProblemType == "Binary", "Target Rate", "Target Mean"),
          xAxis.title = TrendDateVar,
          Theme = Theme
        )
      }
    }

    if (length(TargetGroupedTrendStatsList) > 0L) {
      TargetGroupedTrendStats <- data.table::rbindlist(
        TargetGroupedTrendStatsList,
        fill = TRUE
      )

      data.table::setorderv(
        TargetGroupedTrendStats,
        cols = c("TrendGroupVar", "TrendGroupValue", TrendDateVar)
      )
    }
  }
}


# ============================================================
# Feature Drift Diagnostics
# ============================================================

if (TargetTrendDateVar_Valid && length(TargetCandidateVars) > 0L) {

  data_drift <- data.table::copy(data)
  data.table::setorderv(data_drift, TrendDateVar)

  n_rows_drift <- nrow(data_drift)
  recent_n <- max(1L, floor(n_rows_drift * TargetDriftRecentShare))
  early_n <- max(1L, recent_n)

  early_dt <- data_drift[seq_len(min(early_n, .N))]
  recent_dt <- data_drift[(.N - min(recent_n, .N) + 1L):.N]

  numeric_drift <- data.table::data.table()

  if (length(TargetNumericFeatureVars) > 0L) {

    numeric_drift <- data.table::rbindlist(
      lapply(TargetNumericFeatureVars, function(v) {

        early_x <- early_dt[[v]]
        recent_x <- recent_dt[[v]]

        early_mean <- mean(early_x, na.rm = TRUE)
        recent_mean <- mean(recent_x, na.rm = TRUE)

        data.table::data.table(
          Feature = v,
          FeatureType = "Numeric",
          `Early N` = sum(!is.na(early_x) & is.finite(early_x)),
          `Recent N` = sum(!is.na(recent_x) & is.finite(recent_x)),
          `Early Mean` = early_mean,
          `Recent Mean` = recent_mean,
          `Absolute Change` = recent_mean - early_mean,
          `Percent Change` = ifelse(is.na(early_mean) || early_mean == 0, NA_real_, (recent_mean - early_mean) / abs(early_mean) * 100),
          `Early Missing %` = mean(is.na(early_x)) * 100,
          `Recent Missing %` = mean(is.na(recent_x)) * 100,
          `Missing % Change` = (mean(is.na(recent_x)) - mean(is.na(early_x))) * 100
        )
      }),
      fill = TRUE
    )
  }

  categorical_drift <- data.table::data.table()

  if (length(TargetCategoricalFeatureVars) > 0L) {

    categorical_drift <- data.table::rbindlist(
      lapply(TargetCategoricalFeatureVars, function(v) {

        early_x <- as.character(early_dt[[v]])
        recent_x <- as.character(recent_dt[[v]])

        early_x[is.na(early_x)] <- "<NA>"
        recent_x[is.na(recent_x)] <- "<NA>"

        early_tab <- data.table::data.table(Level = early_x)[, .(EarlyN = .N), by = Level]
        recent_tab <- data.table::data.table(Level = recent_x)[, .(RecentN = .N), by = Level]

        out <- merge(early_tab, recent_tab, by = "Level", all = TRUE)
        out[is.na(EarlyN), EarlyN := 0L]
        out[is.na(RecentN), RecentN := 0L]

        out[, Feature := v]
        out[, FeatureType := "Categorical"]
        out[, `Early Share` := EarlyN / sum(EarlyN) * 100]
        out[, `Recent Share` := RecentN / sum(RecentN) * 100]
        out[, `Share Change` := `Recent Share` - `Early Share`]

        data.table::setorderv(out, "Share Change", order = -1L)

        if (nrow(out) > TargetMaxCategoricalLevels) {
          out <- out[seq_len(TargetMaxCategoricalLevels)]
        }

        out
      }),
      fill = TRUE
    )
  }

  TargetFeatureDriftStats <- data.table::rbindlist(
    list(numeric_drift, categorical_drift),
    fill = TRUE
  )
}


# ============================================================
# Concept Drift Diagnostics
# ============================================================

if (TargetVar_Valid && TargetVar_Usable && TargetProblemType %in% c("Binary", "Regression") && TargetTrendDateVar_Valid && length(TargetNumericFeatureVars) > 0L) {

  target_y <- data[[TargetVar_Name]]

  if (TargetProblemType == "Binary" && !target_is_numeric_col(target_y)) {
    target_levels <- sort(unique(as.character(target_y[!is.na(target_y)])))
    target_y_num <- as.integer(as.character(target_y) == target_levels[length(target_levels)])
  } else {
    target_y_num <- target_y
  }

  data_concept <- data.table::copy(data)
  data_concept[, `.TargetValue` := target_y_num]

  date_values <- sort(unique(data_concept[[TrendDateVar]][!is.na(data_concept[[TrendDateVar]])]))

  if (length(date_values) >= TargetConceptDriftMinPeriods) {

    midpoint <- floor(length(date_values) / 2L)
    early_dates <- date_values[seq_len(midpoint)]
    recent_dates <- date_values[(midpoint + 1L):length(date_values)]

    early_concept <- data_concept[get(TrendDateVar) %in% early_dates]
    recent_concept <- data_concept[get(TrendDateVar) %in% recent_dates]

    TargetConceptDriftStats <- data.table::rbindlist(
      lapply(TargetNumericFeatureVars, function(v) {

        early_r <- target_safe_cor(early_concept[[v]], early_concept[[".TargetValue"]], method = "spearman")
        recent_r <- target_safe_cor(recent_concept[[v]], recent_concept[[".TargetValue"]], method = "spearman")

        early_n <- sum(
          !is.na(early_concept[[v]]) &
            !is.na(early_concept[[".TargetValue"]]) &
            is.finite(early_concept[[v]]) &
            is.finite(early_concept[[".TargetValue"]])
        )

        recent_n <- sum(
          !is.na(recent_concept[[v]]) &
            !is.na(recent_concept[[".TargetValue"]]) &
            is.finite(recent_concept[[v]]) &
            is.finite(recent_concept[[".TargetValue"]])
        )

        data.table::data.table(
          Feature = v,
          `Early N` = early_n,
          `Recent N` = recent_n,
          `Early Correlation` = early_r,
          `Recent Correlation` = recent_r,
          `Correlation Change` = recent_r - early_r,
          `Abs Correlation Change` = abs(recent_r - early_r),
          `Direction Changed` = ifelse(is.na(early_r) | is.na(recent_r), FALSE, sign(early_r) != sign(recent_r))
        )
      }),
      fill = TRUE
    )

    data.table::setorderv(
      TargetConceptDriftStats,
      cols = "Abs Correlation Change",
      order = -1L,
      na.last = TRUE
    )
  }
}


# ============================================================
# Target Risk Flags
# ============================================================

TargetRiskFlags <- data.table::data.table(
  Feature = character(),
  RiskType = character(),
  RiskLevel = character(),
  Reason = character(),
  Evidence = character()
)

if (TargetVar_Valid && TargetVar_Usable) {

  suspicious_name_flags <- data.table::data.table(
    Feature = names(data)[vapply(names(data), target_risk_word_match, logical(1L))]
  )

  suspicious_name_flags <- suspicious_name_flags[Feature != TargetVar_Name]

  if (nrow(suspicious_name_flags) > 0L) {
    suspicious_name_flags[, `:=`(
      RiskType = "Name-based leakage risk",
      RiskLevel = "Medium",
      Reason = "Feature name contains a word commonly associated with outcome, status, decision, post-treatment, or label information.",
      Evidence = Feature
    )]

    TargetRiskFlags <- data.table::rbindlist(
      list(TargetRiskFlags, suspicious_name_flags),
      fill = TRUE
    )
  }

  if (nrow(TargetNumericAssociationStats) > 0L) {

    numeric_high_assoc <- TargetNumericAssociationStats[
      !is.na(`Abs Correlation`) & `Abs Correlation` >= 0.90
    ]

    if (nrow(numeric_high_assoc) > 0L) {
      numeric_high_assoc <- numeric_high_assoc[
        ,
        .(
          Feature,
          RiskType = "Extreme numeric target association",
          RiskLevel = "High",
          Reason = "Numeric feature has extremely high absolute association with the target.",
          Evidence = paste0("Abs correlation = ", safe_format_digits(`Abs Correlation`, 3L))
        )
      ]

      TargetRiskFlags <- data.table::rbindlist(
        list(TargetRiskFlags, numeric_high_assoc),
        fill = TRUE
      )
    }
  }

  if (nrow(TargetCategoricalAssociationStats) > 0L) {

    categorical_high_assoc <- TargetCategoricalAssociationStats[
      RiskLevel %in% c("High", "Medium")
    ]

    if (nrow(categorical_high_assoc) > 0L) {
      categorical_high_assoc <- categorical_high_assoc[
        ,
        .(
          Feature,
          RiskType = "Categorical target separation",
          RiskLevel,
          Reason = "Categorical feature has levels with unusually large target-rate or target-mean separation.",
          Evidence = paste0(
            "Max lift = ", safe_format_digits(`Max Lift`, 3L),
            "; min lift = ", safe_format_digits(`Min Lift`, 3L),
            "; target mean range = ", safe_format_digits(`Target Mean Range`, 3L)
          )
        )
      ]

      TargetRiskFlags <- data.table::rbindlist(
        list(TargetRiskFlags, categorical_high_assoc),
        fill = TRUE
      )
    }
  }

  if (nrow(TargetConceptDriftStats) > 0L) {

    concept_flags <- TargetConceptDriftStats[
      !is.na(`Abs Correlation Change`) & `Abs Correlation Change` >= 0.30
    ]

    if (nrow(concept_flags) > 0L) {
      concept_flags <- concept_flags[
        ,
        .(
          Feature,
          RiskType = "Potential concept drift",
          RiskLevel = ifelse(`Abs Correlation Change` >= 0.50, "High", "Medium"),
          Reason = "Feature-target relationship changed materially between early and recent periods.",
          Evidence = paste0(
            "Early corr = ", safe_format_digits(`Early Correlation`, 3L),
            "; recent corr = ", safe_format_digits(`Recent Correlation`, 3L),
            "; change = ", safe_format_digits(`Correlation Change`, 3L)
          )
        )
      ]

      TargetRiskFlags <- data.table::rbindlist(
        list(TargetRiskFlags, concept_flags),
        fill = TRUE
      )
    }
  }

  if (nrow(TargetRiskFlags) > 0L) {
    data.table::setorderv(
      TargetRiskFlags,
      cols = c("RiskLevel", "RiskType", "Feature"),
      order = c(1L, 1L, 1L)
    )
  }
}


# ============================================================
# Target Reactable Artifacts
# ============================================================

Target_QA <- reactable::reactable(
  data = TargetQA,
  compact = TRUE,
  defaultPageSize = 25,
  wrap = TRUE,
  filterable = TRUE,
  fullWidth = TRUE,
  highlight = TRUE,
  pagination = FALSE,
  resizable = TRUE,
  searchable = TRUE,
  sortable = TRUE,
  striped = FALSE,
  rowStyle = target_dark_row_style,
  bordered = FALSE,
  outlined = FALSE,
  defaultColDef = reactable::colDef(
    headerStyle = target_default_header_style,
    style = target_dark_cell_style
  ),
  columns = list(
    Metric = reactable::colDef(
      minWidth = 260,
      style = function(value, index) {
        out <- target_dark_cell_style(value, index)
        out$color <- "#F8FAFC"
        out$fontWeight <- "800"
        out
      }
    ),
    Count = reactable::colDef(
      minWidth = 100,
      align = "right",
      cell = target_integer_cell,
      style = target_dark_numeric_cell_style
    ),
    Value = reactable::colDef(
      minWidth = 500,
      cell = target_truncated_mono_cell,
      style = target_dark_cell_style
    )
  ),
  theme = target_theme
)

Target_Distribution <- reactable::reactable(
  data = TargetDistributionTable,
  compact = TRUE,
  defaultPageSize = 25,
  pageSizeOptions = c(10, 25, 50, 100),
  wrap = FALSE,
  filterable = TRUE,
  fullWidth = TRUE,
  highlight = TRUE,
  pagination = TRUE,
  resizable = TRUE,
  searchable = TRUE,
  sortable = TRUE,
  striped = FALSE,
  rowStyle = target_dark_row_style,
  bordered = FALSE,
  outlined = FALSE,
  defaultColDef = reactable::colDef(
    headerStyle = target_default_header_style,
    style = target_dark_cell_style
  ),
  theme = target_theme
)

Target_Numeric_Association <- reactable::reactable(
  data = TargetNumericAssociationStats,
  compact = TRUE,
  defaultPageSize = 15,
  pageSizeOptions = c(10, 15, 25, 50, 100),
  wrap = FALSE,
  filterable = TRUE,
  fullWidth = TRUE,
  highlight = TRUE,
  pagination = TRUE,
  resizable = TRUE,
  searchable = TRUE,
  selection = "multiple",
  showPagination = TRUE,
  showPageSizeOptions = TRUE,
  sortable = TRUE,
  striped = FALSE,
  rowStyle = target_dark_row_style,
  bordered = FALSE,
  outlined = FALSE,
  defaultColDef = reactable::colDef(
    minWidth = 105,
    headerStyle = target_default_header_style,
    style = target_dark_cell_style
  ),
  columns = list(
    Feature = reactable::colDef(
      sticky = "left",
      minWidth = 260,
      filterable = TRUE,
      style = target_dark_sticky_cell_style,
      headerStyle = list(
        position = "sticky",
        left = 0,
        zIndex = 2,
        background = "#0B1326",
        color = "#F8FAFC",
        fontWeight = "900",
        borderBottom = "1px solid #334155",
        boxShadow = "6px 0 10px rgba(0, 0, 0, 0.22)"
      )
    ),
    N = reactable::colDef(align = "right", cell = target_integer_cell, style = target_dark_numeric_cell_style),
    `Feature NA N` = reactable::colDef(align = "right", cell = target_integer_cell, style = target_dark_numeric_cell_style),
    `Feature NA %` = reactable::colDef(align = "right", cell = target_pct_cell, style = target_dark_numeric_cell_style),
    `Target NA N` = reactable::colDef(align = "right", cell = target_integer_cell, style = target_dark_numeric_cell_style),
    Correlation = reactable::colDef(align = "center", cell = target_corr_cell, style = target_dark_center_cell_style),
    `Abs Correlation` = reactable::colDef(name = "|Corr|", align = "center", cell = target_abs_corr_cell, style = target_dark_center_cell_style),
    Direction = reactable::colDef(align = "center", cell = function(value) target_badge(value, ifelse(value == "Positive", "good", ifelse(value == "Negative", "warning", "neutral"))), style = target_dark_center_cell_style),
    Strength = reactable::colDef(align = "center", cell = function(value) target_badge(value, ifelse(value %in% c("Very Strong", "Strong"), "danger", ifelse(value == "Moderate", "warning", "neutral"))), style = target_dark_center_cell_style),
    `P Value` = reactable::colDef(align = "center", cell = function(value) target_numeric_cell(value, 4L), style = target_dark_center_cell_style),
    `Suspicious Name` = reactable::colDef(align = "center", cell = function(value) if (isTRUE(value)) target_badge("Yes", "danger") else target_badge("No", "good"), style = target_dark_center_cell_style)
  ),
  theme = target_theme
)

Target_Categorical_Association <- reactable::reactable(
  data = TargetCategoricalAssociationStats,
  compact = TRUE,
  defaultPageSize = 15,
  pageSizeOptions = c(10, 15, 25, 50, 100),
  wrap = FALSE,
  filterable = TRUE,
  fullWidth = TRUE,
  highlight = TRUE,
  pagination = TRUE,
  resizable = TRUE,
  searchable = TRUE,
  selection = "multiple",
  showPagination = TRUE,
  showPageSizeOptions = TRUE,
  sortable = TRUE,
  striped = FALSE,
  rowStyle = target_dark_row_style,
  bordered = FALSE,
  outlined = FALSE,
  defaultColDef = reactable::colDef(
    minWidth = 105,
    headerStyle = target_default_header_style,
    style = target_dark_cell_style
  ),
  columns = list(
    Feature = reactable::colDef(
      sticky = "left",
      minWidth = 260,
      filterable = TRUE,
      style = target_dark_sticky_cell_style,
      headerStyle = list(
        position = "sticky",
        left = 0,
        zIndex = 2,
        background = "#0B1326",
        color = "#F8FAFC",
        fontWeight = "900",
        borderBottom = "1px solid #334155",
        boxShadow = "6px 0 10px rgba(0, 0, 0, 0.22)"
      )
    ),
    Levels = reactable::colDef(align = "right", cell = target_integer_cell, style = target_dark_numeric_cell_style),
    N = reactable::colDef(align = "right", cell = target_integer_cell, style = target_dark_numeric_cell_style),
    `Max Target Mean` = reactable::colDef(align = "right", cell = target_numeric_cell, style = target_dark_numeric_cell_style),
    `Min Target Mean` = reactable::colDef(align = "right", cell = target_numeric_cell, style = target_dark_numeric_cell_style),
    `Target Mean Range` = reactable::colDef(align = "right", cell = target_numeric_cell, style = target_dark_numeric_cell_style),
    `Max Lift` = reactable::colDef(align = "center", cell = target_lift_cell, style = target_dark_center_cell_style),
    `Min Lift` = reactable::colDef(align = "center", cell = target_lift_cell, style = target_dark_center_cell_style),
    `Max Abs Lift From 1` = reactable::colDef(align = "right", cell = target_numeric_cell, style = target_dark_numeric_cell_style),
    `Extreme Level Count` = reactable::colDef(align = "right", cell = target_integer_cell, style = target_dark_numeric_cell_style),
    `Low N Level Count` = reactable::colDef(align = "right", cell = target_integer_cell, style = target_dark_numeric_cell_style),
    `Suspicious Name` = reactable::colDef(align = "center", cell = function(value) if (isTRUE(value)) target_badge("Yes", "danger") else target_badge("No", "good"), style = target_dark_center_cell_style),
    RiskLevel = reactable::colDef(align = "center", cell = target_flag_cell, style = target_dark_center_cell_style)
  ),
  theme = target_theme
)

Target_Categorical_Level_Association <- reactable::reactable(
  data = TargetCategoricalLevelStats,
  compact = TRUE,
  defaultPageSize = 25,
  pageSizeOptions = c(10, 25, 50, 100),
  wrap = FALSE,
  filterable = TRUE,
  fullWidth = TRUE,
  highlight = TRUE,
  pagination = TRUE,
  resizable = TRUE,
  searchable = TRUE,
  sortable = TRUE,
  striped = FALSE,
  rowStyle = target_dark_row_style,
  bordered = FALSE,
  outlined = FALSE,
  defaultColDef = reactable::colDef(
    minWidth = 105,
    headerStyle = target_default_header_style,
    style = target_dark_cell_style
  ),
  columns = list(
    Feature = reactable::colDef(sticky = "left", minWidth = 240, style = target_dark_sticky_cell_style),
    Level = reactable::colDef(minWidth = 240, cell = target_truncated_mono_cell, style = target_dark_cell_style),
    N = reactable::colDef(align = "right", cell = target_integer_cell, style = target_dark_numeric_cell_style),
    `Level N %` = reactable::colDef(align = "right", cell = target_pct_cell, style = target_dark_numeric_cell_style),
    `Target Mean` = reactable::colDef(align = "right", cell = target_numeric_cell, style = target_dark_numeric_cell_style),
    Lift = reactable::colDef(align = "center", cell = target_lift_cell, style = target_dark_center_cell_style),
    `Abs Lift From 1` = reactable::colDef(align = "right", cell = target_numeric_cell, style = target_dark_numeric_cell_style),
    `Low N Flag` = reactable::colDef(align = "center", cell = function(value) if (isTRUE(value)) target_badge("Yes", "warning") else target_badge("No", "good"), style = target_dark_center_cell_style)
  ),
  theme = target_theme
)

Target_Feature_Drift <- reactable::reactable(
  data = TargetFeatureDriftStats,
  compact = TRUE,
  defaultPageSize = 25,
  pageSizeOptions = c(10, 25, 50, 100),
  wrap = FALSE,
  filterable = TRUE,
  fullWidth = TRUE,
  highlight = TRUE,
  pagination = TRUE,
  resizable = TRUE,
  searchable = TRUE,
  sortable = TRUE,
  striped = FALSE,
  rowStyle = target_dark_row_style,
  bordered = FALSE,
  outlined = FALSE,
  defaultColDef = reactable::colDef(
    minWidth = 105,
    headerStyle = target_default_header_style,
    style = target_dark_cell_style
  ),
  theme = target_theme
)

Target_Concept_Drift <- reactable::reactable(
  data = TargetConceptDriftStats,
  compact = TRUE,
  defaultPageSize = 25,
  pageSizeOptions = c(10, 25, 50, 100),
  wrap = FALSE,
  filterable = TRUE,
  fullWidth = TRUE,
  highlight = TRUE,
  pagination = TRUE,
  resizable = TRUE,
  searchable = TRUE,
  sortable = TRUE,
  striped = FALSE,
  rowStyle = target_dark_row_style,
  bordered = FALSE,
  outlined = FALSE,
  defaultColDef = reactable::colDef(
    minWidth = 105,
    headerStyle = target_default_header_style,
    style = target_dark_cell_style
  ),
  columns = list(
    Feature = reactable::colDef(sticky = "left", minWidth = 240, style = target_dark_sticky_cell_style),
    `Early N` = reactable::colDef(align = "right", cell = target_integer_cell, style = target_dark_numeric_cell_style),
    `Recent N` = reactable::colDef(align = "right", cell = target_integer_cell, style = target_dark_numeric_cell_style),
    `Early Correlation` = reactable::colDef(align = "center", cell = target_corr_cell, style = target_dark_center_cell_style),
    `Recent Correlation` = reactable::colDef(align = "center", cell = target_corr_cell, style = target_dark_center_cell_style),
    `Correlation Change` = reactable::colDef(align = "right", cell = target_numeric_cell, style = target_dark_numeric_cell_style),
    `Abs Correlation Change` = reactable::colDef(align = "right", cell = target_numeric_cell, style = target_dark_numeric_cell_style),
    `Direction Changed` = reactable::colDef(align = "center", cell = function(value) if (isTRUE(value)) target_badge("Yes", "warning") else target_badge("No", "good"), style = target_dark_center_cell_style)
  ),
  theme = target_theme
)

Target_Risk_Flags <- reactable::reactable(
  data = TargetRiskFlags,
  compact = TRUE,
  defaultPageSize = 25,
  pageSizeOptions = c(10, 25, 50, 100),
  wrap = TRUE,
  filterable = TRUE,
  fullWidth = TRUE,
  highlight = TRUE,
  pagination = TRUE,
  resizable = TRUE,
  searchable = TRUE,
  sortable = TRUE,
  striped = FALSE,
  rowStyle = target_dark_row_style,
  bordered = FALSE,
  outlined = FALSE,
  defaultColDef = reactable::colDef(
    minWidth = 130,
    headerStyle = target_default_header_style,
    style = target_dark_cell_style
  ),
  columns = list(
    Feature = reactable::colDef(sticky = "left", minWidth = 240, style = target_dark_sticky_cell_style),
    RiskType = reactable::colDef(minWidth = 240, cell = target_text_cell, style = target_dark_cell_style),
    RiskLevel = reactable::colDef(align = "center", cell = target_flag_cell, style = target_dark_center_cell_style),
    Reason = reactable::colDef(minWidth = 500, cell = target_text_cell, style = target_dark_cell_style),
    Evidence = reactable::colDef(minWidth = 500, cell = target_text_cell, style = target_dark_cell_style)
  ),
  theme = target_theme
)


# ============================================================
# Target-Oriented Plots
# ============================================================

# ----------------------------
# Target distribution plot is already created above and stored in:
# TargetDistributionPlot
# TargetPlotList[["Target Distribution"]]
# ----------------------------


# ----------------------------
# Numeric association plots
# ----------------------------

if (exists("TargetNumericAssociationStats") && nrow(TargetNumericAssociationStats) > 0L) {

  TargetNumericAssociationPlotData <- data.table::copy(
    TargetNumericAssociationStats[
      !is.na(`Abs Correlation`)
    ]
  )

  data.table::setorderv(
    TargetNumericAssociationPlotData,
    cols = c("Abs Correlation", "N"),
    order = c(-1L, -1L),
    na.last = TRUE
  )

  if (nrow(TargetNumericAssociationPlotData) > MaxCorrelationPairsToPlot) {
    TargetNumericAssociationPlotData <- TargetNumericAssociationPlotData[seq_len(MaxCorrelationPairsToPlot)]
  }

  if (nrow(TargetNumericAssociationPlotData) > 0L) {

    TargetAssociationPlotList[["Top Numeric Target Associations"]] <- AutoPlots::Bar(
      dt = TargetNumericAssociationPlotData,
      XVar = "Feature",
      YVar = "Abs Correlation",
      title.text = paste0("Top Numeric Associations with ", TargetVar_Name),
      yAxis.title = "|Spearman Correlation|",
      xAxis.title = NULL,
      Theme = Theme
    ) |> echarts4r::e_flip_coords()
  }
}


# ----------------------------
# Categorical association plots
# ----------------------------

if (exists("TargetCategoricalAssociationStats") && nrow(TargetCategoricalAssociationStats) > 0L) {

  TargetCategoricalAssociationPlotData <- data.table::copy(
    TargetCategoricalAssociationStats[
      !is.na(`Max Abs Lift From 1`)
    ]
  )

  data.table::setorderv(
    TargetCategoricalAssociationPlotData,
    cols = c("Max Abs Lift From 1", "Target Mean Range"),
    order = c(-1L, -1L),
    na.last = TRUE
  )

  if (nrow(TargetCategoricalAssociationPlotData) > MaxCorrelationPairsToPlot) {
    TargetCategoricalAssociationPlotData <- TargetCategoricalAssociationPlotData[seq_len(MaxCorrelationPairsToPlot)]
  }

  if (nrow(TargetCategoricalAssociationPlotData) > 0L) {

    TargetAssociationPlotList[["Top Categorical Target Associations"]] <- AutoPlots::Bar(
      dt = TargetCategoricalAssociationPlotData,
      XVar = "Feature",
      YVar = "Max Abs Lift From 1",
      title.text = paste0("Top Categorical Associations with ", TargetVar_Name),
      yAxis.title = "Max |Lift - 1|",
      xAxis.title = NULL,
      Theme = Theme
    ) |> echarts4r::e_flip_coords()
  }
}


# ----------------------------
# Categorical level lift plot
# ----------------------------

if (exists("TargetCategoricalLevelStats") && nrow(TargetCategoricalLevelStats) > 0L) {

  TargetCategoricalLevelPlotData <- data.table::copy(
    TargetCategoricalLevelStats[
      !is.na(`Abs Lift From 1`)
    ]
  )

  TargetCategoricalLevelPlotData[
    ,
    FeatureLevel := paste0(Feature, " = ", Level)
  ]

  data.table::setorderv(
    TargetCategoricalLevelPlotData,
    cols = c("Abs Lift From 1", "N"),
    order = c(-1L, -1L),
    na.last = TRUE
  )

  if (nrow(TargetCategoricalLevelPlotData) > MaxCorrelationPairsToPlot) {
    TargetCategoricalLevelPlotData <- TargetCategoricalLevelPlotData[seq_len(MaxCorrelationPairsToPlot)]
  }

  if (nrow(TargetCategoricalLevelPlotData) > 0L) {

    TargetAssociationPlotList[["Top Categorical Level Lifts"]] <- AutoPlots::Bar(
      dt = TargetCategoricalLevelPlotData,
      XVar = "FeatureLevel",
      YVar = "Abs Lift From 1",
      title.text = paste0("Top Categorical Level Lifts for ", TargetVar_Name),
      yAxis.title = "|Lift - 1|",
      xAxis.title = NULL,
      Theme = Theme
    ) |> echarts4r::e_flip_coords()
  }
}


# ----------------------------
# Target overall trend plots already created above and stored in:
# TargetTrendPlotList
# ----------------------------


# ----------------------------
# Target grouped trend plots already created above and stored in:
# TargetGroupedTrendPlotList
# ----------------------------


# ----------------------------
# Numeric feature drift plots
# ----------------------------

if (exists("TargetFeatureDriftStats") && nrow(TargetFeatureDriftStats) > 0L) {

  TargetNumericFeatureDriftPlotData <- data.table::copy(
    TargetFeatureDriftStats[
      FeatureType == "Numeric" &
        !is.na(`Percent Change`)
    ]
  )

  if (nrow(TargetNumericFeatureDriftPlotData) > 0L) {

    TargetNumericFeatureDriftPlotData[
      ,
      `Abs Percent Change` := abs(`Percent Change`)
    ]

    data.table::setorderv(
      TargetNumericFeatureDriftPlotData,
      cols = "Abs Percent Change",
      order = -1L,
      na.last = TRUE
    )

    if (nrow(TargetNumericFeatureDriftPlotData) > MaxCorrelationPairsToPlot) {
      TargetNumericFeatureDriftPlotData <- TargetNumericFeatureDriftPlotData[seq_len(MaxCorrelationPairsToPlot)]
    }

    TargetDriftPlotList[["Top Numeric Feature Drift"]] <- AutoPlots::Bar(
      dt = TargetNumericFeatureDriftPlotData,
      XVar = "Feature",
      YVar = "Abs Percent Change",
      title.text = "Top Numeric Feature Drift",
      yAxis.title = "|Recent Mean % Change|",
      xAxis.title = NULL,
      Theme = Theme
    )
  }
}


# ----------------------------
# Numeric missingness drift plot
# ----------------------------

if (exists("TargetFeatureDriftStats") && nrow(TargetFeatureDriftStats) > 0L) {

  TargetMissingDriftPlotData <- data.table::copy(
    TargetFeatureDriftStats[
      FeatureType == "Numeric" &
        !is.na(`Missing % Change`)
    ]
  )

  if (nrow(TargetMissingDriftPlotData) > 0L) {

    TargetMissingDriftPlotData[
      ,
      `Abs Missing % Change` := abs(`Missing % Change`)
    ]

    data.table::setorderv(
      TargetMissingDriftPlotData,
      cols = "Abs Missing % Change",
      order = -1L,
      na.last = TRUE
    )

    if (nrow(TargetMissingDriftPlotData) > MaxCorrelationPairsToPlot) {
      TargetMissingDriftPlotData <- TargetMissingDriftPlotData[seq_len(MaxCorrelationPairsToPlot)]
    }

    TargetDriftPlotList[["Top Missingness Drift"]] <- AutoPlots::Bar(
      dt = TargetMissingDriftPlotData,
      XVar = "Feature",
      YVar = "Abs Missing % Change",
      title.text = "Top Feature Missingness Drift",
      yAxis.title = "|Recent Missing % - Early Missing %|",
      xAxis.title = NULL,
      Theme = Theme
    )
  }
}


# ----------------------------
# Categorical feature share drift plot
# ----------------------------

if (exists("TargetFeatureDriftStats") && nrow(TargetFeatureDriftStats) > 0L) {

  TargetCategoricalDriftPlotData <- data.table::copy(
    TargetFeatureDriftStats[
      FeatureType == "Categorical" &
        !is.na(`Share Change`)
    ]
  )

  if (nrow(TargetCategoricalDriftPlotData) > 0L) {

    TargetCategoricalDriftPlotData[
      ,
      FeatureLevel := paste0(Feature, " = ", Level)
    ]

    TargetCategoricalDriftPlotData[
      ,
      `Abs Share Change` := abs(`Share Change`)
    ]

    data.table::setorderv(
      TargetCategoricalDriftPlotData,
      cols = "Abs Share Change",
      order = -1L,
      na.last = TRUE
    )

    if (nrow(TargetCategoricalDriftPlotData) > MaxCorrelationPairsToPlot) {
      TargetCategoricalDriftPlotData <- TargetCategoricalDriftPlotData[seq_len(MaxCorrelationPairsToPlot)]
    }

    TargetDriftPlotList[["Top Categorical Share Drift"]] <- AutoPlots::Bar(
      dt = TargetCategoricalDriftPlotData,
      XVar = "FeatureLevel",
      YVar = "Abs Share Change",
      title.text = "Top Categorical Level Share Drift",
      yAxis.title = "|Recent Share - Early Share|",
      xAxis.title = NULL,
      Theme = Theme
    )
  }
}


# ----------------------------
# Concept drift plot
# ----------------------------

if (exists("TargetConceptDriftStats") && nrow(TargetConceptDriftStats) > 0L) {

  TargetConceptDriftPlotData <- data.table::copy(
    TargetConceptDriftStats[
      !is.na(`Abs Correlation Change`)
    ]
  )

  data.table::setorderv(
    TargetConceptDriftPlotData,
    cols = "Abs Correlation Change",
    order = -1L,
    na.last = TRUE
  )

  if (nrow(TargetConceptDriftPlotData) > MaxCorrelationPairsToPlot) {
    TargetConceptDriftPlotData <- TargetConceptDriftPlotData[seq_len(MaxCorrelationPairsToPlot)]
  }

  if (nrow(TargetConceptDriftPlotData) > 0L) {

    TargetDriftPlotList[["Top Concept Drift"]] <- AutoPlots::Bar(
      dt = TargetConceptDriftPlotData,
      XVar = "Feature",
      YVar = "Abs Correlation Change",
      title.text = paste0("Top Concept Drift Against ", TargetVar_Name),
      yAxis.title = "|Recent Corr - Early Corr|",
      xAxis.title = NULL,
      Theme = Theme
    )
  }
}


# ----------------------------
# Risk flag plots
# ----------------------------

if (exists("TargetRiskFlags") && nrow(TargetRiskFlags) > 0L) {

  TargetRiskLevelPlotData <- TargetRiskFlags[
    ,
    .(N = .N),
    by = RiskLevel
  ]

  data.table::setorderv(
    TargetRiskLevelPlotData,
    cols = "N",
    order = -1L
  )

  TargetRiskPlotList[["Risk Flags by Severity"]] <- AutoPlots::Bar(
    dt = TargetRiskLevelPlotData,
    XVar = "RiskLevel",
    YVar = "N",
    title.text = "Target Risk Flags by Severity",
    yAxis.title = "Flag Count",
    xAxis.title = NULL,
    Theme = Theme
  )

  TargetRiskTypePlotData <- TargetRiskFlags[
    ,
    .(N = .N),
    by = RiskType
  ]

  data.table::setorderv(
    TargetRiskTypePlotData,
    cols = "N",
    order = -1L
  )

  TargetRiskPlotList[["Risk Flags by Type"]] <- AutoPlots::Bar(
    dt = TargetRiskTypePlotData,
    XVar = "RiskType",
    YVar = "N",
    title.text = "Target Risk Flags by Type",
    yAxis.title = "Flag Count",
    xAxis.title = NULL,
    Theme = Theme
  )
}


# ----------------------------
# Master target plot list
# ----------------------------

TargetPlotList <- c(
  TargetPlotList,
  TargetAssociationPlotList,
  TargetTrendPlotList,
  TargetGroupedTrendPlotList,
  TargetDriftPlotList,
  TargetRiskPlotList
)

# ----------------------------
# Target plot QA
# ----------------------------

TargetPlotQA <- data.table::data.table(
  PlotSection = c(
    "Target Distribution Plots",
    "Target Association Plots",
    "Target Trend Plots",
    "Target Grouped Trend Plots",
    "Target Drift Plots",
    "Target Risk Plots",
    "Total Target Plots"
  ),
  Count = c(
    as.integer(!is.null(TargetDistributionPlot)),
    length(TargetAssociationPlotList),
    length(TargetTrendPlotList),
    length(TargetGroupedTrendPlotList),
    length(TargetDriftPlotList),
    length(TargetRiskPlotList),
    length(TargetPlotList)
  ),
  Values = c(
    ifelse(!is.null(TargetDistributionPlot), "Target Distribution", ""),
    paste(names(TargetAssociationPlotList), collapse = ", "),
    paste(names(TargetTrendPlotList), collapse = ", "),
    paste(names(TargetGroupedTrendPlotList), collapse = ", "),
    paste(names(TargetDriftPlotList), collapse = ", "),
    paste(names(TargetRiskPlotList), collapse = ", "),
    paste(names(TargetPlotList), collapse = ", ")
  )
)
```


## <font size="5">Target Analysis Report Descriptions</font>

<details><summary>Expand</summary>
<p>

This report is designed to provide a focused, structured, and user-friendly target-variable analysis workflow for evaluating a dataset from a modeling-readiness perspective. The goal is to summarize target behavior, identify feature relationships with the target, surface target distribution issues, evaluate temporal stability, detect potential drift, and flag variables that may require additional review before modeling.

The outputs are intended to help users understand how candidate features relate to the target variable through numeric association statistics, categorical target-rate or target-mean summaries, feature-level lift diagnostics, target trend analysis, feature drift diagnostics, concept drift diagnostics, and risk flags for potential leakage, collider effects, or post-treatment variables. These diagnostics are intended to highlight modeling-relevant patterns that may affect feature selection, validation strategy, model interpretation, and production stability.

The report should be treated as a pre-modeling investigation tool rather than a final modeling decision engine. Strong target associations, extreme categorical separation, drift signals, suspicious feature names, and leakage or collider-risk flags are heuristic indicators that require domain review. They can help identify promising predictors, unstable features, suspicious variables, and areas where additional validation is needed, but they do not prove causality, leakage, model suitability, or business relevance on their own.


</details>
</p>

# <font size="5">Describe Data</font>

<details><summary>Expand</summary>
<p>

```{r Model_Evaluation_Metrics, echo=FALSE}
if(!is.null(Describe_Data)) {
  eval(Describe_Data)
}
```

</details>
</p>





# <font size="5">Target Distribution Table</font>

<details><summary>Expand</summary>
<p>

```{r Target_Distribution, echo=FALSE}
if (exists("Target_Distribution")) {
  Target_Distribution
} else {
  print("Target distribution table was not created.")
}
```

</p>
</details>


# <font size="5">Target Distribution Plot</font>

<details><summary>Expand</summary>
<p>

```{r TargetDistributionPlot, echo=FALSE}
if (exists("TargetDistributionPlot") && !is.null(TargetDistributionPlot)) {
  TargetDistributionPlot
} else if (exists("TargetPlotList") && "Target Distribution" %in% names(TargetPlotList)) {
  TargetPlotList[["Target Distribution"]]
} else {
  print("Target distribution plot was not generated.")
}
```

</p>
</details>


# <font size="5">Target Association Plots</font>

<details><summary>Expand</summary>
<p>

```{r TargetAssociationPlotList, echo=FALSE}
if (exists("TargetAssociationPlotList") && length(TargetAssociationPlotList) > 0L) {
  AutoPlots::display_plots_grid(TargetAssociationPlotList, cols = 1)
} else {
  print("No target association plots were generated.")
}
```

</p>
</details>


# <font size="5">Target Overall Trend Plots</font>

<details><summary>Expand</summary>
<p>

```{r TargetTrendPlotList, echo=FALSE}
if (exists("TargetTrendPlotList") && length(TargetTrendPlotList) > 0L) {
  AutoPlots::display_plots_grid(TargetTrendPlotList, cols = 2)
} else {
  print("No target trend plots were generated. Provide a valid TargetVar and TrendDateVar to enable this section.")
}
```

</p>
</details>


# <font size="5">Target Grouped Trend Plots</font>

<details><summary>Expand</summary>
<p>

```{r TargetGroupedTrendPlotList, echo=FALSE}
if (exists("TargetGroupedTrendPlotList") && length(TargetGroupedTrendPlotList) > 0L) {
  AutoPlots::display_plots_grid(TargetGroupedTrendPlotList, cols = 2)
} else {
  print("No grouped target trend plots were generated. Provide a valid TargetVar, TrendDateVar, and TrendGroupVar to enable this section.")
}
```

</p>
</details>


# <font size="5">Target Drift Plots</font>

<details><summary>Expand</summary>
<p>

```{r TargetDriftPlotList, echo=FALSE}
if (exists("TargetDriftPlotList") && length(TargetDriftPlotList) > 0L) {
  AutoPlots::display_plots_grid(TargetDriftPlotList, cols = 1)
} else {
  print("No target drift plots were generated. Provide a valid TrendDateVar to enable drift diagnostics.")
}
```

</p>
</details>


# <font size="5">Target Risk Flag Plots</font>

<details><summary>Expand</summary>
<p>

```{r TargetRiskPlotList, echo=FALSE}
if (exists("TargetRiskPlotList") && length(TargetRiskPlotList) > 0L) {
  AutoPlots::display_plots_grid(TargetRiskPlotList, cols = 1)
} else {
  print("No target risk flag plots were generated.")
}
```

</p>
</details>


# <font size="5">All Target Plots</font>

<details><summary>Expand</summary>
<p>

```{r TargetPlotList, echo=FALSE}
if (exists("TargetPlotList") && length(TargetPlotList) > 0L) {
  AutoPlots::display_plots_grid(TargetPlotList, cols = 1)
} else {
  print("No target-oriented plots were generated.")
}
```

</p>
</details>


# <font size="5">Numeric Feature Association With Target</font>

<details><summary>Expand</summary>
<p>

```{r Target_Numeric_Association, echo=FALSE}
if (exists("Target_Numeric_Association")) {
  Target_Numeric_Association
} else {
  print("Numeric feature association table was not created.")
}
```

</p>
</details>


# <font size="5">Categorical Feature Association With Target</font>

<details><summary>Expand</summary>
<p>

```{r Target_Categorical_Association, echo=FALSE}
if (exists("Target_Categorical_Association")) {
  Target_Categorical_Association
} else {
  print("Categorical feature association table was not created.")
}
```

</p>
</details>


# <font size="5">Categorical Level Association With Target</font>

<details><summary>Expand</summary>
<p>

```{r Target_Categorical_Level_Association, echo=FALSE}
if (exists("Target_Categorical_Level_Association")) {
  Target_Categorical_Level_Association
} else {
  print("Categorical level association table was not created.")
}
```

</p>
</details>


# <font size="5">Target Trend Statistics</font>

<details><summary>Expand</summary>
<p>

```{r TargetTrendStats, echo=FALSE}
if (exists("TargetTrendStats") && nrow(TargetTrendStats) > 0L) {
  reactable::reactable(
    TargetTrendStats,
    compact = TRUE,
    defaultPageSize = 25,
    pageSizeOptions = c(10, 25, 50, 100),
    wrap = FALSE,
    filterable = TRUE,
    searchable = TRUE,
    fullWidth = TRUE,
    highlight = TRUE,
    pagination = TRUE,
    resizable = TRUE,
    sortable = TRUE,
    striped = FALSE,
    rowStyle = if (exists("target_dark_row_style")) target_dark_row_style else NULL,
    defaultColDef = reactable::colDef(
      headerStyle = if (exists("target_default_header_style")) target_default_header_style else NULL,
      style = if (exists("target_dark_cell_style")) target_dark_cell_style else NULL
    ),
    theme = if (exists("target_theme")) target_theme else reactable::reactableTheme()
  )
} else {
  print("Target trend statistics were not created.")
}
```

</p>
</details>


# <font size="5">Target Grouped Trend Statistics</font>

<details><summary>Expand</summary>
<p>

```{r TargetGroupedTrendStats, echo=FALSE}
if (exists("TargetGroupedTrendStats") && nrow(TargetGroupedTrendStats) > 0L) {
  reactable::reactable(
    TargetGroupedTrendStats,
    compact = TRUE,
    defaultPageSize = 25,
    pageSizeOptions = c(10, 25, 50, 100),
    wrap = FALSE,
    filterable = TRUE,
    searchable = TRUE,
    fullWidth = TRUE,
    highlight = TRUE,
    pagination = TRUE,
    resizable = TRUE,
    sortable = TRUE,
    striped = FALSE,
    rowStyle = if (exists("target_dark_row_style")) target_dark_row_style else NULL,
    defaultColDef = reactable::colDef(
      headerStyle = if (exists("target_default_header_style")) target_default_header_style else NULL,
      style = if (exists("target_dark_cell_style")) target_dark_cell_style else NULL
    ),
    theme = if (exists("target_theme")) target_theme else reactable::reactableTheme()
  )
} else {
  print("Grouped target trend statistics were not created.")
}
```

</p>
</details>


# <font size="5">Feature Drift Diagnostics</font>

<details><summary>Expand</summary>
<p>

```{r Target_Feature_Drift, echo=FALSE}
if (exists("Target_Feature_Drift")) {
  Target_Feature_Drift
} else {
  print("Feature drift diagnostics were not created.")
}
```

</p>
</details>


# <font size="5">Concept Drift Diagnostics</font>

<details><summary>Expand</summary>
<p>

```{r Target_Concept_Drift, echo=FALSE}
if (exists("Target_Concept_Drift")) {
  Target_Concept_Drift
} else {
  print("Concept drift diagnostics were not created.")
}
```

</p>
</details>


# <font size="5">Potential Leakage / Collider Risk Flags</font>

<details><summary>Expand</summary>
<p>

```{r Target_Risk_Flags, echo=FALSE}
if (exists("Target_Risk_Flags")) {
  Target_Risk_Flags
} else {
  print("Target risk flags were not created.")
}
```

</p>
</details>




```{js, echo=FALSE}
setTimeout(function() {
  var codes = document.querySelectorAll('.dataTables_wrapper');
  var code, i, d, s, p;
  for (i = 0; i < codes.length; i++) {
    code = codes[i];
    p = code.parentNode;
    d = document.createElement('details');
    s = document.createElement('summary');
    s.innerText = 'Details';
    // <details><summary>Details</summary></details>
    d.appendChild(s);
    // move the code into <details>
    p.replaceChild(d, code);
    d.appendChild(code);
  }
});
```
